### 2021-08-18 docs/manuscript/manuscript.Rmd
init

---
title             : "Data irregularities across five implicit learning articles by the same researchers"
# title             : "Data irregularities across five implicit learning: Comments on @lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015"
shorttitle        : "Data irregularities"

author: 
  - name          : "Brad McKay"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1280 Main Street West, Ivor Wynne Centre Room AB-131 A1, McMaster University, Hamilton ON Canada, L8S 4K1"
    email         : "bradmckay8@gmail.com"
  - name          : "Michael J. Carter"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Kinesiology, McMaster University"

authornote: |
  \addORCIDlink{Brad McKay}{0000-0002-7408-2323}

  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

abstract: |
  We present a critical re-analysis of five implicit learning papers published by the same authors between 2010 and 2021. We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article. We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations. We found the pairwise effect sizes were implausible in all five articles in question, with Cohen’s d values often exceeding 100 and sometimes exceeding 1000. Impossible statistics were reported in 4 out of the 5 articles. Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects. The results reported in the five articles in question are unreliable. Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.

keywords          : "Meta-science; GRIMMER; Effect sizes; Perceptual motor learning"
wordcount         : "X"

bibliography      : ["../references.bib", "../r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "../apa.csl"
documentclass     : "apa7"
classoption       : "man" # use "doc" for 1-column preprint or "jou" for 2-column preprint
output            : papaja::apa6_pdf
header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{xcolor}
  - \raggedbottom
  #- \leftheader{\textbf{THIS PREPRINT IS CURRENTLY UNDER REVIEW}}
  #- \rightheader{\textbf{THIS PREPRINT IS CURRENTLY UNDER REVIEW}}
  - \pagewiselinenumbers
  #- \hypersetup{draft}
---

```{r setup, include = FALSE}
library("papaja")
library(kableExtra)
library(tidyverse)
# r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Statistical reporting errors may commonly occur in psychology articles [@brown2017; @nuijten2016] and such errors are often consistent with hypothesized results [@bakker2011]. When the primary conclusions in research articles depend on reporting errors, replicability is unlikely and future research may be wasted if researchers attempt to build on the erroneously reported results [@munafo2017]. In this paper, we scrutinize five papers published by the same two authors[^1], where the authors report a high number of erroneous or implausible data on which their primary conclusions depend. We first became aware of the @lola2021 paper when the paper was highlighted in a social media post [@gray2021]. During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed. The paper also referenced past research published by these authors, and given our cause for concern over the issues found in the @lola2021 paper, we deemed it necessary to examine these other papers. We remain agnostic to the sources of error in each of these papers. Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., $F$-statistics) across multiple papers. Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions. Below, we outline our causes for concern and the overarching issues we found across the five articles in question.

[^1]: One of the five papers had a third author.

## The articles in question

We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague [@lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015]. All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. The five articles will be referred to throughout this paper using the following numbering system:

1.  Lola, A.C., & Tzetzis, G.C. (2021). The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress. *International Journal of Sport and Exercise Psychology*, 1-21. <https://doi.org/10.1080/1612197X.2021.1877325>

2.  Lola, A.C., & Tzetzis, G.C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. *Journal of Physical Education and Sport*, 20(5), 2478-2486. <https://doi.org/10.7752/jpes.2020.05339>

3.  Tzetzis, G.C., & Lola, A.C. (2015). The effect of analogy, implicit, and explicit learning on anticipation in volleyball serving. *International Journal of Sport Psychology*, 46(2), 152-166. <https://doi.org/10.7352/IJSP.2015.46.152>

4.  Lola, A.C., & Tzetzis, G.C., & Zetou, H. (2012). The effect of implicit and explicit practice in the development of decision making in volleyball serving. *Perceptual and Motor Skills*, 114(2), 665-678. <https://doi.org/10.2466/05.23.25.PMS.114.2.665-678>

5.  Tzetzis, G.C., & Lola, C.A. (2010). The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions. *International Journal of Sport Sciences and Physical Education*, 1, 54-59.[^2]

[^2]: This article is in a journal of a publishing group that has been identified as a potential predatory journal. Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (<https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS>). In fact, the earliest available issue on the journal's webpage in from 2016.

```{r table1, echo = FALSE, results = "asis"}

table_1 <- tibble(
  c1 = c("Lola \\& Tzetzis (2021)",
         "Lola \\& Tzetzis (2020)",
         "Tzetzis \\& Lola (2015)",
         "Lola et al (2012)",
         "Tzetzis \\& Lola (2010)"),
  c2 = c("60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
         "80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
         "60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\\textsuperscript{a}",
         "60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)",
         "48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)")
)

kbl(table_1,
    booktabs = TRUE,
    escape = FALSE,
    caption = "Participant demographics in each of the target articles.",
    col.names = c("Target article",
                  "Sample size and participant details"),
    align = c("l", "l")) %>%
  kable_styling(position = "left",
                font_size = 11) %>%
  pack_rows("Article 1", 1, 1) %>%
  pack_rows("Article 2", 2, 2) %>%
  pack_rows("Article 3", 3, 3) %>%
  pack_rows("Article 4", 4, 4) %>%
  pack_rows("Article 5", 5, 5) %>%
  footnote(alphabet = c("Articles 1-3 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2."),
           alphabet_title = "Note.",
           threeparttable = TRUE)

```

Although there were some differences between the reported experiments in the target articles, there were many methodological commonalities that can be summarized. All five articles involved female children learning a volleyball skill as part of a volleyball camp. In each case, the participants were reported to have minimal experience (i.e., were described as novices) with the task at hand. The purpose of all five experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice. Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test. The authors also included a high stress test in Articles 1 and 5.

In Articles 1-3, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy. In Articles 4 and 5, a sequential group (see below for description) replaced the analogy group. All five experiments also included a control group that did not practice the task. Implicit instruction did not contain any explicit information for how to perform the task and the learners were asked to perform a distracting task like counting backwards while practicing to prevent them from acquiring declarative rules for performance. In contrast, explicit instruction consisted of direct verbal instructions for performing the task. Analogy instruction was considered a type of implicit instruction wherein an analogy or metaphor was provided to the learner. For example, "Imagine that the opponents' surface is covered with water. Send the ball where there is more water and no opponents at the court." [@lola2021, p. 9]. Sequential instruction involved receiving explicit instruction for the first half of training followed by implicit instruction for the second half of training. Across experiments, the authors predicted that implicit forms of instruction---implicit, analogy, and sequential---would be more effective than explicit instruction for motor and perceptual learning. This advantage was also predicted to be greater when testing was conducted in a high stress situation. In @lola2021 for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team. Further, it was often predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.

The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2). In addition, Articles 1 and 5 included a measure of state anxiety with the Competitive State Anxiety Inventory-2 (CSAI-2) [@tsorbatzoudis1998], and Article 2 had a measure of self-efficacy using a Likert scale. Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.

# Methods

None of the five articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 11 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analysis and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2 through 5 as these articles were less recent and presumably, all planned analyses had been completed. After a 2 week period with no response, we followed up on with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication that we were concerned about irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 1 and provided some more general responses to our concerns; however, elements of their responses were inaccurate relative to the target articles. <!-- [MAYBE AN APPENDIX TO HIGHLIGHT SOME LIKE THE MENTION OF BONFERRONI YET NON USED BONFERONNI]. --> The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data *and* analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: **[LINK]**.

## Effect size calculations and simulations

Means and standard deviations were extracted from each article for all measures and time points that were reported. Cohen's $d$ was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}. To provide context, we simulated data with true effect sizes of $d$ = .80 and $d$ = 3.0 one million times each and report the range of effect sizes observed in those simulations. <!-- SHOULD WE NEED TO MENTION SAMPLE SIZE FOR SIMS AND WHY THAT VALUE WAS PICKED? -->

## Mathematically impossible data and granularity analysis

In two of the articles in question, it was clear that the some of the reported results were not mathematically possible based on the scale of measurement that was used. When outcomes were single item integers, such as the number of explicit rules recalled, we used a web application (<http://www.prepubmed.org/grimmer_sd/>) to conduct a granularity analysis called GRIMMER [@anaya2016]. Using GRIMMER it is possible to determine if specific means and standard deviations are possible for a given sample size. To be conservative, we specified that we did not know whether the standard deviation was calculated for the sample or population, nor whether ambiguous values were rounded up or down. Mean and standard deviation pairs that are mathematically possible are considered GRIMMER consistent, while mean and standard deviation pairs that are not mathematically possible are GRIMMER inconsistent. <!-- THIS IS THE SECTION I THINK WE MAY NEED TO ADD SOME EXPLANATIONS TO REGARDING THESE TESTS SO THE READER HAS AN UNDERSTANDING OF IT. I THINK WE COULD MODEL THIS OFF THE VAN DER ZEE ET AL PAPER AND THEIR GRANULARITY ERRORS SECTION -->

## Test statistics and $\eta^{2}$

Each of the articles reported only omnibus test statistics and then reported post-hoc analyses with symbols demarcating significant and non-significant differences. In response to our expressions of concern, the authors suggested that many of the issues were due to misprints in the articles. Specifically, they indicated that the reported means and standard deviations in their tables were incorrect and the root of the errors had to be from them outsourcing the formatting of their tables. The authors then insisted that despite these typographic errors, their discussion of the results and corresponding conclusions were still accurate (A. Lola, personal communication, April 22, 2021). However, the test statistics reported for many analyses were implausibly large and the authors often reported $\eta^{2}$ values associated with the omnibus test. Our examination of the reported $\eta^{2}$ values revealed that many were not only implausibly large, but also consistent with the reported pairwise effects.

# Results

## Implausible effect sizes

Cohen's $d$ is used to describe the standardized mean difference of an effect and values can range between 0 and infinity. Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion]. Conventional benchmarks for small, medium and large effects are $d$ = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [@thompson2007; @lakens2013; @field2016; @correll2020]. Recently, an analysis of 6447 Cohen's $d$ statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's $d$ values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].

To evaluate the maximum range of plausible Cohen's $d$ statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of 1,000,000 experiments. For the first simulation we set the true effect size at $d$ = .80, the conventional benchmark for a "large" treatment effect. The largest effect size observed from the 1,000,000 simulated experiments was $d$ = 2.97 (see Figure \@ref(fig:fig1)). In the second simulation, we set the true effect size at $d$ = 3.0, an unrealistically large effect size that might rarely be encountered in the psychology literature. The maximum effect size observed in the 1,000,000 simulated experiments was $d$ = 6.6.

(ref:fig1-caption) Absolute Cohen's d estimates from Articles 1-4 plotted on a logarithmic scale. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = .80 is illustrated by light blue and dark blue regions of the figure, reaching a maximum value of $d$ = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3.0 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of $d$ = 6.86.

```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", out.width = "100%", out.height = "100%", fig.align = "center"}
#fig.env = "figure*"
knitr::include_graphics("../../figs/fig1.pdf")
```

<!-- PROBABLY NEED TO DO SOME MINOR TWEAKS TO FIG TO MAKE AXIS TEXT A BIT BIGGER. ALSO, NOT SURE WHAT COLOR CODE YOU PUT IN FOR THE BOTTOM SHADED AREA BUT I SEE YOU'VE DESCRIBED IT AS LIGHT BLUE IN THE CAPTION BUT IT LOOKS GREEN TO ME SO NOT SURE IF IT JUST ME AND COLORS OR NOT. -->

In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes. In Article 1, the smallest pre-test difference on the reaction measure was $d$ = 1.29, while the largest pre-test difference was $d$ = 35.32, although none of the groups were reported as significantly different in the article. The smallest post-intervention effect at any of the three time points was $d$ = 286.42, while the largest effect was $d$ = 3504.86.

A similar picture emerges when analyzing the accuracy data. All the pre-test differences were implausibly large (all $d$'s $\geq$ 2.52) despite being reported as not significantly different in the articles. Ten of the pairwise comparisons resulted in $d$'s $\geq$ 100 following treatment with the independent variables. The motor component data also revealed many post-treatment effect sizes that are implausibly large, ranging from $d$ = 1.16 to $d$ = 13.5. <!-- NOT SURE BUT IS IMPLAUSIBLY LARGE BEING THROWN AROUND TOO OFTEN THROUGHOUT THIS SECTION...SHOULD WE MAYBE JUST REPORT THE RANGE WITHOUT QUALIFYING IT LIKE THE PARAGRAPH BELOW? -->

In Article 2, post-intervention motor performance effect sizes ranged from $d$ = 3.1 to $d$ = 20.95. Similarly, post-intervention self-efficacy effect sizes ranged from $d$ = 1.79 to $d$ = 44.46. Similarly, in Article 3 post-intervention reaction time effect sizes ranged from $d$ = 2.28 to $d$ = 35.97. Continuing this pattern, post-intervention response accuracy effect sizes ranged from $d$ = 5.84 to $d$ = 29.7.

In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from $d$ = 2.53 to $d$ = 15.50. Nevertheless, all pre-test comparisons were reported as non-significant. Following intervention, the effect sizes ranged from $d$ = 23.13 to $d$ = 155.08.

The reaction time effect sizes were not implausibly large at any time point, ranging from $d$ = 0.0 to $d$ = .86. However, the authors reported an implausibly large effect size for the 4 (Group) x 3 (Time) ANOVA, $\eta^{2}$ = .94. Further, despite only one pairwise comparison being statistically significant, all post-intervention comparisons were reported as being significant in the article. <!-- IS THIS ALSO FOR ARTICLE 4, IF SO I THINK WE SHOULD COMBINE WITH PREVIOUS PARAGRAPH. I THINK IT BE GOOD TO HAVE A PARAGRAPH PER ARTICLE RATHER THAN A BUNCH OF SHORT PARAGRAPHS. THOUGHTS? -->

In Article 5 the authors did not report means and standard deviations for most of the analyses. However, $\eta^{2}$ effect sizes were reported and these ranged from $\eta^{2}$ = .52 to $\eta^{2}$ = .98. These effect sizes are discussed further below.

All the post-intervention effects reviewed above were directionally consistent with the researchers' expectations. The sometimes implausibly large pre-test effects were not expected, but also were not reported as significant.

## Impossible data and granularity analysis

In Article 1, the CSAI-2 was used to assess the level of cognitive and somatic stress experienced by participants. Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item. At each of the three low-stress time points, the means reported for all four groups ranged from 1.02 to 1.09. During the high-stress time point, the means ranged from 3.95 to 4.09. The means for two groups were reported as greater than 4, which is not possible given the maximum score on the CSAI-2 is 4.

In Article 2, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles. Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^3] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09. The perfect score was not a rounding error because the same group was reported to have a mean score of 2.99 with a standard deviation of .11 on the post-test. These data are not possible.

[^3]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [@reeve1994; @hancock1995; @fischman2015].

Articles 1, 4, and 5 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase. As a single item analysis of integers these results were suitable for a GRIMMER analysis.

In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups. In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (M = 4.8, SD = 1.78). The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent. In Article 5, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample. For two of the groups, however, they were consistent regardless which method of calculating the standard deviation was used. However, the results for the explicit group were GRIMMER inconsistent (M = 4.8, SD = 1.78).[^4]

[^4]: You may have noticed that the same mean and standard deviation pairing (M = 4.8, SD = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other. This is because of sample size differences ($n$ = 20 for the consistent result and $n$ = 12 for the inconsistent one).

## Test statistics and $\eta^{2}$

Eta-squared ($\eta^{2}$) is calculated by dividing the sum of squares for the effect by the total sum of squares. It can be interpreted as analogous to $R^{2}$: It represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an analysis of variance [@lakens2013]. Benchmarks have been suggested for small, medium, and large $\eta^{2}$ effect sizes as $\eta^{2}$ = .01, .06, and .14, respectively [@cohen1988]. Importantly, if a main effect of instruction type results in $\eta^{2}$ = .99, this suggests that 99% of the total variability in outcome measure can be explained by group assignment alone. Such a result is implausible.
<!-- IS THIS .99 JUST AN EXAMPLE? IF SO, MAYBE WE USE A MORE REALISTIC VALUE TO EXPLAIN THE INTERPRETATION. IF IT IS NOT AN EXAMPLE, THEN I THINK WE SHOULD REFER TO AN ARTICLE THAT HAS A .99 VALUE -->

The range of significant $F$-statistics reported across the five articles in question was $F$ = 28.60 to $F$ = 101,489.71. Only three $F$-statistics were under 100 (28.60, 30.73, and 91.75), and all three were for interactions.

Article 1 did not report $\eta^{2}$ values but had the largest pairwise effects and $F$-statistics of the five articles in question. Article 2 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance. Similarly, variance explained on the self-efficacy measure was $\eta^{2}$ = .995, $\eta^{2}$ = .994, $\eta^{2}$ = .997 for the Time, Group, and Time x Group effects, respectively. Article 3 also reported $\eta^{2}$ = .99 for all three effects on both response time and response accuracy measures.

Article 4 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure. Interestingly, the Time x Group interaction had the smallest reported significant $F$-statistic among the five articles in question. With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses. Article 5 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses.

## Other oddities

Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5. The reported test statistic in these four articles was $F$ = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4). Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2. Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \@ref(tab:table1)). We assumed that each article was based on different samples as none of the articles mentioned using any previously published data.
<!-- I REMOVED THE F-STATISTIC ISSUE FROM ABOVE AS IT FELT A BIT REPETITIVE BEING IN TWO SECTIONS AND DECIDED TO LET IT LIVE JUST IN THIS ODDITIES SECTION INSTEAD. FEEL FREE TO SWITCH AROUND IF YOU THINK IT WOULD BE BEST HIGHER UP. -->

# Discussion

We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning [@lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015]. These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A. Lola, personal communication, April 22, 2021). Further, the reported test statistics and associated $\eta^{2}$ values are also implausibly large, which is inconsistent with the authors' claim that their results and discussions remain valid despite these aforementioned typographic errors in the tables. Considering these findings, it seems the conclusions from these articles are not reliable.

It is noteworthy that the results reported in each of these articles perfectly reflect the authors' expectations. Indeed, our attention was drawn to these articles after the @lola2021 paper was shared on Twitter [@gray2021], possibly because the results appeared to be exemplary. Although these errors seem unlikely to have aligned with expectations by chance alone, our exposure to them occurred after they had been selected for publication. We cannot rule out that these papers were selected for publication because of exemplary results and happened to have errors, and this selection caused those errors to correlate with the authors' expectations.

Other irregularities, such a repeating $F$-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation. Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed. These errors were pervasive and appear to have substantially affected the conclusions of the articles in question. At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process. Even if the authors offer corrections, which they have suggested they intend to do[^5], many in the research community may find it difficult to trust any of these results.

[^5]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions have been taken by the authors.

# Data, materials, and code availability

\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: **[LINK]**.

# R packages used in this project

`r cite_r("../r-references.bib")`.

# Conflict of interest

The authors declare no competing interests.

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
<!-- ::: {#refs custom-style="Bibliography"} -->
<!-- ::: -->

\endgroup

### 2021-08-18 docs/manuscript/manuscript.tex
init

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Data irregularities across five implicit learning articles by the same researchers},
  pdfauthor={Brad McKay1 \& Michael J. Carter1},
  pdflang={en-EN},
  pdfkeywords={Meta-science; GRIMMER; Effect sizes; Perceptual motor learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Data irregularities}
\keywords{Meta-science; GRIMMER; Effect sizes; Perceptual motor learning\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{xcolor}
\raggedbottom
\pagewiselinenumbers
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Data irregularities across five implicit learning articles by the same researchers}
\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
\date{}

\authornote{

\addORCIDlink{Brad McKay}{0000-0002-7408-2323}

\addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

Correspondence concerning this article should be addressed to Brad McKay, 1280 Main Street West, Ivor Wynne Centre Room AB-131 A1, McMaster University, Hamilton ON Canada, L8S 4K1. E-mail: \href{mailto:bradmckay8@gmail.com}{\nolinkurl{bradmckay8@gmail.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Kinesiology, McMaster University}

\abstract{
We present a critical re-analysis of five implicit learning papers published by the same authors between 2010 and 2021. We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article. We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations. We found the pairwise effect sizes were implausible in all five articles in question, with Cohen's d values often exceeding 100 and sometimes exceeding 1000. Impossible statistics were reported in 4 out of the 5 articles. Reported test statistics and \(\eta^{2}\) values were also implausible, with several \(\eta^{2}\) = .99 and even \(\eta^{2}\) = 1.0 for between-subjects main effects. The results reported in the five articles in question are unreliable. Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.
}

\begin{document}
\maketitle

Statistical reporting errors may commonly occur in psychology articles (Brown \& Heathers, 2017; Nuijten et al., 2016) and such errors are often consistent with hypothesized results (Bakker \& Wicherts, 2011). When the primary conclusions in research articles depend on reporting errors, replicability is unlikely and future research may be wasted if researchers attempt to build on the erroneously reported results (Munafò et al., 2017). In this paper, we scrutinize five papers published by the same two authors\footnote{One of the five papers had a third author.}, where the authors report a high number of erroneous or implausible data on which their primary conclusions depend. We first became aware of the Lola and Tzetzis (2021) paper when the paper was highlighted in a social media post (Gray, 2021). During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed. The paper also referenced past research published by these authors, and given our cause for concern over the issues found in the Lola and Tzetzis (2021) paper, we deemed it necessary to examine these other papers. We remain agnostic to the sources of error in each of these papers. Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., \(F\)-statistics) across multiple papers. Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions. Below, we outline our causes for concern and the overarching issues we found across the five articles in question.

\hypertarget{the-articles-in-question}{%
\subsection{The articles in question}\label{the-articles-in-question}}

We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., 2012; Lola \& Tzetzis, 2021, 2020; Tzetzis \& Lola, 2010, 2015). All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. The five articles will be referred to throughout this paper using the following numbering system:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Lola, A.C., \& Tzetzis, G.C. (2021). The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress. \emph{International Journal of Sport and Exercise Psychology}, 1-21. \url{https://doi.org/10.1080/1612197X.2021.1877325}
\item
  Lola, A.C., \& Tzetzis, G.C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. \emph{Journal of Physical Education and Sport}, 20(5), 2478-2486. \url{https://doi.org/10.7752/jpes.2020.05339}
\item
  Tzetzis, G.C., \& Lola, A.C. (2015). The effect of analogy, implicit, and explicit learning on anticipation in volleyball serving. \emph{International Journal of Sport Psychology}, 46(2), 152-166. \url{https://doi.org/10.7352/IJSP.2015.46.152}
\item
  Lola, A.C., \& Tzetzis, G.C., \& Zetou, H. (2012). The effect of implicit and explicit practice in the development of decision making in volleyball serving. \emph{Perceptual and Motor Skills}, 114(2), 665-678. \url{https://doi.org/10.2466/05.23.25.PMS.114.2.665-678}
\item
  Tzetzis, G.C., \& Lola, C.A. (2010). The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions. \emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This article is in a journal of a publishing group that has been identified as a potential predatory journal. Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS}). In fact, the earliest available issue on the journal's webpage in from 2016.}
\end{enumerate}

\begin{table}

\caption{\label{tab:table1}Participant demographics in each of the target articles.}
\fontsize{11}{13}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{ll}
\toprule
Target article & Sample size and participant details\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 1}}\\
\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 2}}\\
\hspace{1em}Lola \& Tzetzis (2020) & 80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 3}}\\
\hspace{1em}Tzetzis \& Lola (2015) & 60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 4}}\\
\hspace{1em}Lola et al (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 5}}\\
\hspace{1em}Tzetzis \& Lola (2010) & 48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note.} 
\item[a] Articles 1-3 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2.
\end{tablenotes}
\end{threeparttable}
\end{table}

Although there were some differences between the reported experiments in the target articles, there were many methodological commonalities that can be summarized. All five articles involved female children learning a volleyball skill as part of a volleyball camp. In each case, the participants were reported to have minimal experience (i.e., were described as novices) with the task at hand. The purpose of all five experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice. Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test. The authors also included a high stress test in Articles 1 and 5.

In Articles 1-3, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy. In Articles 4 and 5, a sequential group (see below for description) replaced the analogy group. All five experiments also included a control group that did not practice the task. Implicit instruction did not contain any explicit information for how to perform the task and the learners were asked to perform a distracting task like counting backwards while practicing to prevent them from acquiring declarative rules for performance. In contrast, explicit instruction consisted of direct verbal instructions for performing the task. Analogy instruction was considered a type of implicit instruction wherein an analogy or metaphor was provided to the learner. For example, ``Imagine that the opponents' surface is covered with water. Send the ball where there is more water and no opponents at the court.'' (Lola \& Tzetzis, 2021, p. 9). Sequential instruction involved receiving explicit instruction for the first half of training followed by implicit instruction for the second half of training. Across experiments, the authors predicted that implicit forms of instruction---implicit, analogy, and sequential---would be more effective than explicit instruction for motor and perceptual learning. This advantage was also predicted to be greater when testing was conducted in a high stress situation. In Lola and Tzetzis (2021) for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team. Further, it was often predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.

The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2). In addition, Articles 1 and 5 included a measure of state anxiety with the Competitive State Anxiety Inventory-2 (CSAI-2) (Tsorbatzoudis et al., 1998), and Article 2 had a measure of self-efficacy using a Likert scale. Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

None of the five articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 11 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analysis and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2 through 5 as these articles were less recent and presumably, all planned analyses had been completed. After a 2 week period with no response, we followed up on with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication that we were concerned about irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 1 and provided some more general responses to our concerns; however, elements of their responses were inaccurate relative to the target articles. The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data \emph{and} analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: \textbf{{[}LINK{]}}.

\hypertarget{effect-size-calculations-and-simulations}{%
\subsection{Effect size calculations and simulations}\label{effect-size-calculations-and-simulations}}

Means and standard deviations were extracted from each article for all measures and time points that were reported. Cohen's \(d\) was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}. To provide context, we simulated data with true effect sizes of \(d\) = .80 and \(d\) = 3.0 one million times each and report the range of effect sizes observed in those simulations.

\hypertarget{mathematically-impossible-data-and-granularity-analysis}{%
\subsection{Mathematically impossible data and granularity analysis}\label{mathematically-impossible-data-and-granularity-analysis}}

In two of the articles in question, it was clear that the some of the reported results were not mathematically possible based on the scale of measurement that was used. When outcomes were single item integers, such as the number of explicit rules recalled, we used a web application (\url{http://www.prepubmed.org/grimmer_sd/}) to conduct a granularity analysis called GRIMMER (Anaya, 2016). Using GRIMMER it is possible to determine if specific means and standard deviations are possible for a given sample size. To be conservative, we specified that we did not know whether the standard deviation was calculated for the sample or population, nor whether ambiguous values were rounded up or down. Mean and standard deviation pairs that are mathematically possible are considered GRIMMER consistent, while mean and standard deviation pairs that are not mathematically possible are GRIMMER inconsistent.

\hypertarget{test-statistics-and-eta2}{%
\subsection{\texorpdfstring{Test statistics and \(\eta^{2}\)}{Test statistics and \textbackslash eta\^{}\{2\}}}\label{test-statistics-and-eta2}}

Each of the articles reported only omnibus test statistics and then reported post-hoc analyses with symbols demarcating significant and non-significant differences. In response to our expressions of concern, the authors suggested that many of the issues were due to misprints in the articles. Specifically, they indicated that the reported means and standard deviations in their tables were incorrect and the root of the errors had to be from them outsourcing the formatting of their tables. The authors then insisted that despite these typographic errors, their discussion of the results and corresponding conclusions were still accurate (A. Lola, personal communication, April 22, 2021). However, the test statistics reported for many analyses were implausibly large and the authors often reported \(\eta^{2}\) values associated with the omnibus test. Our examination of the reported \(\eta^{2}\) values revealed that many were not only implausibly large, but also consistent with the reported pairwise effects.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{implausible-effect-sizes}{%
\subsection{Implausible effect sizes}\label{implausible-effect-sizes}}

Cohen's \(d\) is used to describe the standardized mean difference of an effect and values can range between 0 and infinity. Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion). Conventional benchmarks for small, medium and large effects are \(d\) = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (Correll et al., 2020; Field \& Iles, 2016; Lakens, 2013; Thompson, 2007). Recently, an analysis of 6447 Cohen's \(d\) statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \(d\) values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).

To evaluate the maximum range of plausible Cohen's \(d\) statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of 1,000,000 experiments. For the first simulation we set the true effect size at \(d\) = .80, the conventional benchmark for a ``large'' treatment effect. The largest effect size observed from the 1,000,000 simulated experiments was \(d\) = 2.97 (see Figure \ref{fig:fig1}). In the second simulation, we set the true effect size at \(d\) = 3.0, an unrealistically large effect size that might rarely be encountered in the psychology literature. The maximum effect size observed in the 1,000,000 simulated experiments was \(d\) = 6.6.

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1}

}

\caption{Absolute Cohen's d estimates from Articles 1-4 plotted on a logarithmic scale. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .80 is illustrated by light blue and dark blue regions of the figure, reaching a maximum value of \(d\) = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3.0 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of \(d\) = 6.86.}\label{fig:fig1}
\end{figure}

In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes. In Article 1, the smallest pre-test difference on the reaction measure was \(d\) = 1.29, while the largest pre-test difference was \(d\) = 35.32, although none of the groups were reported as significantly different in the article. The smallest post-intervention effect at any of the three time points was \(d\) = 286.42, while the largest effect was \(d\) = 3504.86.

A similar picture emerges when analyzing the accuracy data. All the pre-test differences were implausibly large (all \(d\)'s \(\geq\) 2.52) despite being reported as not significantly different in the articles. Ten of the pairwise comparisons resulted in \(d\)'s \(\geq\) 100 following treatment with the independent variables. The motor component data also revealed many post-treatment effect sizes that are implausibly large, ranging from \(d\) = 1.16 to \(d\) = 13.5.

In Article 2, post-intervention motor performance effect sizes ranged from \(d\) = 3.1 to \(d\) = 20.95. Similarly, post-intervention self-efficacy effect sizes ranged from \(d\) = 1.79 to \(d\) = 44.46. Similarly, in Article 3 post-intervention reaction time effect sizes ranged from \(d\) = 2.28 to \(d\) = 35.97. Continuing this pattern, post-intervention response accuracy effect sizes ranged from \(d\) = 5.84 to \(d\) = 29.7.

In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from \(d\) = 2.53 to \(d\) = 15.50. Nevertheless, all pre-test comparisons were reported as non-significant. Following intervention, the effect sizes ranged from \(d\) = 23.13 to \(d\) = 155.08.

The reaction time effect sizes were not implausibly large at any time point, ranging from \(d\) = 0.0 to \(d\) = .86. However, the authors reported an implausibly large effect size for the 4 (Group) x 3 (Time) ANOVA, \(\eta^{2}\) = .94. Further, despite only one pairwise comparison being statistically significant, all post-intervention comparisons were reported as being significant in the article.

In Article 5 the authors did not report means and standard deviations for most of the analyses. However, \(\eta^{2}\) effect sizes were reported and these ranged from \(\eta^{2}\) = .52 to \(\eta^{2}\) = .98. These effect sizes are discussed further below.

All the post-intervention effects reviewed above were directionally consistent with the researchers' expectations. The sometimes implausibly large pre-test effects were not expected, but also were not reported as significant.

\hypertarget{impossible-data-and-granularity-analysis}{%
\subsection{Impossible data and granularity analysis}\label{impossible-data-and-granularity-analysis}}

In Article 1, the CSAI-2 was used to assess the level of cognitive and somatic stress experienced by participants. Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item. At each of the three low-stress time points, the means reported for all four groups ranged from 1.02 to 1.09. During the high-stress time point, the means ranged from 3.95 to 4.09. The means for two groups were reported as greater than 4, which is not possible given the maximum score on the CSAI-2 is 4.

In Article 2, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles. Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.\footnote{Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task (Fischman, 2015; Hancock et al., 1995; Reeve et al., 1994).} Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09. The perfect score was not a rounding error because the same group was reported to have a mean score of 2.99 with a standard deviation of .11 on the post-test. These data are not possible.

Articles 1, 4, and 5 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase. As a single item analysis of integers these results were suitable for a GRIMMER analysis.

In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups. In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (M = 4.8, SD = 1.78). The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent. In Article 5, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample. For two of the groups, however, they were consistent regardless which method of calculating the standard deviation was used. However, the results for the explicit group were GRIMMER inconsistent (M = 4.8, SD = 1.78).\footnote{You may have noticed that the same mean and standard deviation pairing (M = 4.8, SD = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other. This is because of sample size differences (\(n\) = 20 for the consistent result and \(n\) = 12 for the inconsistent one).}

\hypertarget{test-statistics-and-eta2-1}{%
\subsection{\texorpdfstring{Test statistics and \(\eta^{2}\)}{Test statistics and \textbackslash eta\^{}\{2\}}}\label{test-statistics-and-eta2-1}}

Eta-squared (\(\eta^{2}\)) is calculated by dividing the sum of squares for the effect by the total sum of squares. It can be interpreted as analogous to \(R^{2}\): It represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an analysis of variance (Lakens, 2013). Benchmarks have been suggested for small, medium, and large \(\eta^{2}\) effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988). Importantly, if a main effect of instruction type results in \(\eta^{2}\) = .99, this suggests that 99\% of the total variability in outcome measure can be explained by group assignment alone. Such a result is implausible.

The range of significant \(F\)-statistics reported across the five articles in question was \(F\) = 28.60 to \(F\) = 101,489.71. Only three \(F\)-statistics were under 100 (28.60, 30.73, and 91.75), and all three were for interactions.

Article 1 did not report \(\eta^{2}\) values but had the largest pairwise effects and \(F\)-statistics of the five articles in question. Article 2 reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance. Similarly, variance explained on the self-efficacy measure was \(\eta^{2}\) = .995, \(\eta^{2}\) = .994, \(\eta^{2}\) = .997 for the Time, Group, and Time x Group effects, respectively. Article 3 also reported \(\eta^{2}\) = .99 for all three effects on both response time and response accuracy measures.

Article 4 reported \(\eta^{2}\) = 1.0 for the main effect of Time and the Time x Group interaction, as well as \(\eta^{2}\) = .95 for the main effect of Group on the response time measure. Interestingly, the Time x Group interaction had the smallest reported significant \(F\)-statistic among the five articles in question. With respect to response accuracy, the reported effects were \(\eta^{2}\) = .98, \(\eta^{2}\) = .94, \(\eta^{2}\) = .93 for the Time, Group, and Time x Group analyses. Article 5 reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses.

\hypertarget{other-oddities}{%
\subsection{Other oddities}\label{other-oddities}}

Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5. The reported test statistic in these four articles was \(F\) = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4). Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2. Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \ref{tab:table1}). We assumed that each article was based on different samples as none of the articles mentioned using any previously published data.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola et al., 2012; Lola \& Tzetzis, 2021, 2020; Tzetzis \& Lola, 2010, 2015). These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A. Lola, personal communication, April 22, 2021). Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that their results and discussions remain valid despite these aforementioned typographic errors in the tables. Considering these findings, it seems the conclusions from these articles are not reliable.

It is noteworthy that the results reported in each of these articles perfectly reflect the authors' expectations. Indeed, our attention was drawn to these articles after the Lola and Tzetzis (2021) paper was shared on Twitter (Gray, 2021), possibly because the results appeared to be exemplary. Although these errors seem unlikely to have aligned with expectations by chance alone, our exposure to them occurred after they had been selected for publication. We cannot rule out that these papers were selected for publication because of exemplary results and happened to have errors, and this selection caused those errors to correlate with the authors' expectations.

Other irregularities, such a repeating \(F\)-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation. Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed. These errors were pervasive and appear to have substantially affected the conclusions of the articles in question. At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process. Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-07-08), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.

\hypertarget{data-materials-and-code-availability}{%
\section{Data, materials, and code availability}\label{data-materials-and-code-availability}}

\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: \textbf{{[}LINK{]}}.

\hypertarget{r-packages-used-in-this-project}{%
\section{R packages used in this project}\label{r-packages-used-in-this-project}}

R {[}Version 4.1.0; R Core Team (2021){]} and the R-packages \emph{compute.es} {[}Version 0.2.5; Re (2013){]}, \emph{kableExtra} {[}Version 1.3.4; Zhu (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, and \emph{tidyverse} {[}Version 1.3.1; Wickham et al. (2019){]}.

\hypertarget{conflict-of-interest}{%
\section{Conflict of interest}\label{conflict-of-interest}}

The authors declare no competing interests.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\endgroup

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-anaya2016}{}%
Anaya, J. (2016). \emph{The GRIMMER test: A method for testing the validity of reported measures of variability}. \url{https://doi.org/10.7287/peerj.preprints.2400v1}

\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-bakker2011}{}%
Bakker, M., \& Wicherts, J. M. (2011). The (mis)reporting of statistical results in psychology journals. \emph{Behavior Research Methods}, \emph{43}(3), 666--678. \url{https://doi.org/10.3758/s13428-011-0089-5}

\leavevmode\hypertarget{ref-brown2017}{}%
Brown, N. J. L., \& Heathers, J. A. J. (2017). The GRIM Test: A Simple Technique Detects Numerous Anomalies in the Reporting of Results in Psychology. \emph{Social Psychological and Personality Science}, \emph{8}(4), 363--369. \url{https://doi.org/10.1177/1948550616673876}

\leavevmode\hypertarget{ref-cohen1988}{}%
Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). Routledge. \url{https://doi.org/10.4324/9780203771587}

\leavevmode\hypertarget{ref-cohen1962}{}%
Cohen, J. (1962). The statistical power of abnormal-social psychological research: a review. \emph{Journal of Abnormal and Social Psychology}, \emph{65}, 145--153. \url{https://doi.org/10.1037/h0045186}

\leavevmode\hypertarget{ref-correll2020}{}%
Correll, J., Mellinger, C., McClelland, G. H., \& Judd, C. M. (2020). Avoid cohen{'}s {`}small{'}, {`}medium{'}, and {`}large{'} for power analysis. \emph{Trends in Cognitive Sciences}, \emph{24}(3), 200--207. \url{https://doi.org/10.1016/j.tics.2019.12.009}

\leavevmode\hypertarget{ref-field2016}{}%
Field, A. P., \& Iles, J. (2016). \emph{An adventure in statistics: The reality enigma}.

\leavevmode\hypertarget{ref-fischman2015}{}%
Fischman, M. G. (2015). On the continuing problem of inappropriate learning measures: Comment on Wulf et al. (2014) and Wulf et al. (2015). \emph{Human Movement Science}, \emph{42}, 225--231. \url{https://doi.org/10.1016/j.humov.2015.05.011}

\leavevmode\hypertarget{ref-gray2021}{}%
Gray, R. {[}@ShakeyWaits{]}. (2021). \emph{The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress}. {[}Tweet; Thumbnail link to article{]}. Twitter. \url{https://twitter.com/ShakeyWaits/status/1359501377073012736}.

\leavevmode\hypertarget{ref-hancock1995}{}%
Hancock, G. R., Butler, M. S., \& Fischman, M. G. (1995). On the problem of two-dimensional error scores: Measures and analyses of accuracy, bias, and consistency. \emph{Journal of Motor Behavior}, \emph{27}(3), 241--250. \url{https://doi.org/10.1080/00222895.1995.9941714}

\leavevmode\hypertarget{ref-lakens2013}{}%
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}. \url{https://doi.org/10.3389/fpsyg.2013.00863}

\leavevmode\hypertarget{ref-lola2021}{}%
Lola, A. C., \& Tzetzis, G. C. (2021). The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress. \emph{International Journal of Sport and Exercise Psychology}, \emph{0}(0), 1--21. \url{https://doi.org/10.1080/1612197X.2021.1877325}

\leavevmode\hypertarget{ref-lola2020}{}%
Lola, A. C., \& Tzetzis, G. C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. \emph{Journal of Physical Education and Sport}, \emph{20}(5), 2478--2486. \url{https://www.cabdirect.org/cabdirect/abstract/20203562097}

\leavevmode\hypertarget{ref-lola2012}{}%
Lola, A. C., Tzetzis, G. C., \& Zetou, H. (2012). The Effect of Implicit and Explicit Practice in the Development of Decision Making in Volleyball Serving. \emph{Perceptual and Motor Skills}, \emph{114}(2), 665--678. \url{https://doi.org/10.2466/05.23.25.PMS.114.2.665-678}

\leavevmode\hypertarget{ref-lovakov2021}{}%
Lovakov, A., \& Agadullina, E. R. (2021). Empirically derived guidelines for effect size interpretation in social psychology. \emph{European Journal of Social Psychology}, \emph{00}, 1--20. \url{https://doi.org/10.1002/ejsp.2752}

\leavevmode\hypertarget{ref-munafo2017}{}%
Munafò, M. R., Nosek, B. A., Bishop, D. V. M., Button, K. S., Chambers, C. D., Percie du Sert, N., Simonsohn, U., Wagenmakers, E.-J., Ware, J. J., \& Ioannidis, J. P. A. (2017). A manifesto for reproducible science. \emph{Nature Human Behaviour}, \emph{1}(1), 1--9. \url{https://doi.org/10.1038/s41562-016-0021}

\leavevmode\hypertarget{ref-nuijten2016}{}%
Nuijten, M. B., Hartgerink, C. H. J., van Assen, M. A. L. M., Epskamp, S., \& Wicherts, J. M. (2016). The prevalence of statistical reporting errors in psychology (1985{{}}2013). \emph{Behavior Research Methods}, \emph{48}(4), 1205--1226. \url{https://doi.org/10.3758/s13428-015-0664-2}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-R-compute.es}{}%
Re, A. C. D. (2013). Compute.es: Compute effect sizes. In \emph{R Package}. \url{https://cran.r-project.org/package=compute.es}

\leavevmode\hypertarget{ref-reeve1994}{}%
Reeve, T. G., Fischman, M. G., Christina, R. W., \& Cauraugh, J. H. (1994). Using one-dimensional task error measures to assess performance on two-dimensional tasks: Comment on 'attentional control, distractors, and motor performance'. \emph{Human Performance}, \emph{7}(4), 315--319. \url{https://doi.org/10.1207/s15327043hup0704_6}

\leavevmode\hypertarget{ref-thompson2007}{}%
Thompson, B. (2007). Effect sizes, confidence intervals, and confidence intervals for effect sizes. \emph{Psychology in the Schools}, \emph{44}(5), 423--432. \url{https://doi.org/10.1002/pits.20234}

\leavevmode\hypertarget{ref-tsorbatzoudis1998}{}%
Tsorbatzoudis, H., Barkoukis, V., Kaissidis-Rodafinos, A., \& Grouios, G. (1998). A test of the reliability and factorial validity of the greek version of the CSAI-2. \emph{Research Quarterly for Exercise and Sport}, \emph{69}(4), 416--419. \url{https://doi.org/10.1080/02701367.1998.10607717}

\leavevmode\hypertarget{ref-tzetzis2010}{}%
Tzetzis, G. C., \& Lola, A. C. (2010). The role of implicit, explicit instruction and their combination in learning anticipation skill under normal and stress conditions. \emph{International Journal of Sport Sciences and Physical Education}, \emph{1}, 54--59.

\leavevmode\hypertarget{ref-tzetzis2015}{}%
Tzetzis, G. C., \& Lola, A. C. (2015). The effect of analogy, implicit, and explicit learning on anticipation in volleyball serving. \emph{International Journal of Sport Psychology}, \emph{46}(2), 152--166. \url{https://doi.org/10.7352/IJSP.2015.46.152}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T. L., Miller, E., Bache, S. M., Müller, K., Ooms, J., Robinson, D., Seidel, D. P., Spinu, V., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\hypertarget{ref-R-kableExtra}{}%
Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. \url{https://CRAN.R-project.org/package=kableExtra}

\end{CSLReferences}

\end{document}

### 2021-08-19 docs/manuscript/manuscript.Rmd
update: merge brad's edit

@@
 ---
-title             : "Data irregularities across five implicit learning articles by the same researchers"
-# title             : "Data irregularities across five implicit learning: Comments on @lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015"
+title             : "Data irregularities across five implicit learning: Comments on @lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015"
+
 shorttitle        : "Data irregularities"
@@
 
-## The articles in question
+## The Articles in Question
 
@@
 In @lola2021 for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team.
-Further, it was often predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.
+Further, it was predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.
 
 The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2).
-In addition, Articles 1 and 5 included a measure of state anxiety with the Competitive State Anxiety Inventory-2 (CSAI-2) [@tsorbatzoudis1998], and Article 2 had a measure of self-efficacy using a Likert scale.
+In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (CSAI-2) [@tsorbatzoudis1998], and Article 2 had a measure of self-efficacy using a Likert scale.
 Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.
@@
 None of the five articles in question included a link to a public repository where the data could be accessed.
-We first wrote (email sent February 11 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
+We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
 The authors' response was that the data could not be shared as they were not finished with their analysis and were in the process of running different tests (A.
@@
 The authors did address some specific concerns regarding Article 1 and provided some more general responses to our concerns; however, elements of their responses were inaccurate relative to the target articles.
-<!-- [MAYBE AN APPENDIX TO HIGHLIGHT SOME LIKE THE MENTION OF BONFERRONI YET NON USED BONFERONNI].
---> The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
+The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
 Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A.
@@
 
-## Effect size calculations and simulations
+## Effect Size Calculations and Simulations
 
@@
 Cohen's $d$ was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}.
-To provide context, we simulated data with true effect sizes of $d$ = .80 and $d$ = 3.0 one million times each and report the range of effect sizes observed in those simulations.
-<!-- SHOULD WE NEED TO MENTION SAMPLE SIZE FOR SIMS AND WHY THAT VALUE WAS PICKED?
--->
+To provide context, we simulated data from two groups of $n = 20$, consistent with groups sizes in Articles 1-4.
+We ran simulations with true effect sizes of $d = .80$ and $d = 3.0$ one million times each and report the range of effect sizes observed in those simulations.
 
-## Mathematically impossible data and granularity analysis
+## Mathematically Impossible Data and Granularity Analysis
 
 In two of the articles in question, it was clear that the some of the reported results were not mathematically possible based on the scale of measurement that was used.
-When outcomes were single item integers, such as the number of explicit rules recalled, we used a web application (<http://www.prepubmed.org/grimmer_sd/>) to conduct a granularity analysis called GRIMMER [@anaya2016].
-Using GRIMMER it is possible to determine if specific means and standard deviations are possible for a given sample size.
+When outcomes were single item integers (a granularity of 1), such as the number of explicit rules recalled, we used a web application (<http://www.prepubmed.org/grimmer_sd/>) to conduct a granularity analysis (GRIMMER) of reported means and standard deviations [@anaya2016].
+GRIMMER builds off the original Granularity-Related Inconsistency of Means (GRIM) analysis [@brown2017], which leveraged the fact that the means of granular data are also granular.
+Given a data set of size $N$ and granularity $G$, only means of granularity $G/N$ are possible.
+Thus, all possible means for data of a given $G$ and $N$ can be enumerated, and only means that match these possibilities are considered GRIM-consistent.
+The GRIMMER analysis extends this test by also evaluating whether mean-standard deviation pairs are possible.
+First, the GRIM analysis is conducted to determine if the mean is GRIM-consistent.
+Next, lower and upper bounds of the standard deviation are calculated based on how many decimals ($D$) it is reported to by $(SD\pm^[0.5/10^{D}])^{2}$.
+Then all possible variances between these bounds are enumerated, converted back to standard deviations, and rounded to the nearest $D$ decimals.
+The reported standard deviation is checked for a match with any of these values.
+Finally, the mean-variance pair is compared to possible mean-variance pairings (the GRIMMER test handles sample sizes between 5 and 99).
+Using GRIMMER it is possible to determine if specific mean and standard deviation pairs are possible for data of a given sample size.
 To be conservative, we specified that we did not know whether the standard deviation was calculated for the sample or population, nor whether ambiguous values were rounded up or down.
 Mean and standard deviation pairs that are mathematically possible are considered GRIMMER consistent, while mean and standard deviation pairs that are not mathematically possible are GRIMMER inconsistent.
-<!-- THIS IS THE SECTION I THINK WE MAY NEED TO ADD SOME EXPLANATIONS TO REGARDING THESE TESTS SO THE READER HAS AN UNDERSTANDING OF IT.
-I THINK WE COULD MODEL THIS OFF THE VAN DER ZEE ET AL PAPER AND THEIR GRANULARITY ERRORS SECTION -->
 
-## Test statistics and $\eta^{2}$
+## Eta-squared ($\eta^{2}$)
 
@@
 However, the test statistics reported for many analyses were implausibly large and the authors often reported $\eta^{2}$ values associated with the omnibus test.
-Our examination of the reported $\eta^{2}$ values revealed that many were not only implausibly large, but also consistent with the reported pairwise effects.
+Our examination of the reported $\eta^{2}$ values revealed that, as with the reported pairwise comparisons, many were implausibly large.
 
@@
 
-## Implausible effect sizes
+## Implausible Effect Sizes
 
@@
 For the first simulation we set the true effect size at $d$ = .80, the conventional benchmark for a "large" treatment effect.
-The largest effect size observed from the 1,000,000 simulated experiments was $d$ = 2.97 (see Figure \@ref(fig:fig1)).
-In the second simulation, we set the true effect size at $d$ = 3.0, an unrealistically large effect size that might rarely be encountered in the psychology literature.
-The maximum effect size observed in the 1,000,000 simulated experiments was $d$ = 6.6.
+The largest effect size observed from the 1,000,000 simulated experiments was $d = 2.97$ (see Figure \@ref(fig:fig1)).
+In the second simulation, we set the true effect size at $d = 3.0$, an unrealistically large effect size that might rarely be encountered in the psychology literature.
+The maximum effect size observed in the 1,000,000 simulated experiments was $d = 6.6$.
 
@@
 All pairwise comparisons have been included for all dependent measures in each experiment.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = .80 is illustrated by light blue and dark blue regions of the figure, reaching a maximum value of $d$ = 2.97.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3.0 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of $d$ = 6.86.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d = .80$ is illustrated by light green and dark blue regions of the figure, reaching a maximum value of $d = 2.97$.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3.0 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of $d = 6.6$.
 
@@
 
-<!-- PROBABLY NEED TO DO SOME MINOR TWEAKS TO FIG TO MAKE AXIS TEXT A BIT BIGGER.
-ALSO, NOT SURE WHAT COLOR CODE YOU PUT IN FOR THE BOTTOM SHADED AREA BUT I SEE YOU'VE DESCRIBED IT AS LIGHT BLUE IN THE CAPTION BUT IT LOOKS GREEN TO ME SO NOT SURE IF IT JUST ME AND COLORS OR NOT.
--->
+In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes.
+In Article 1, the smallest pre-test difference on the reaction measure was $d = 1.29$, while the largest pre-test difference was $d = 35.32$, although none of the groups were reported as significantly different in the article.
+The smallest post-intervention effect at any of the three time points was $d = 286.42$, while the largest effect was $d = 3504.86$.
+A similar picture emerges when analyzing the accuracy data.
+All the pre-test differences were improbably large (all $d$'s $\geq$ 2.52) despite being reported as not significantly different in the articles.
+Ten of the pairwise comparisons resulted in $d$'s $\geq$ 100 following treatment with the independent variables.
+The motor component data revealed post-treatment effect sizes ranging from $d = 1.16$ to $d = 13.5$.
 
-In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference on the reaction measure was $d$ = 1.29, while the largest pre-test difference was $d$ = 35.32, although none of the groups were reported as significantly different in the article.
-The smallest post-intervention effect at any of the three time points was $d$ = 286.42, while the largest effect was $d$ = 3504.86.
+In Article 2, post-intervention motor performance effect sizes ranged from $d = 3.1$ to $d = 20.95$.
+Similarly, post-intervention self-efficacy effect sizes ranged from $d = 1.79$ to $d = 44.46$.
+Likewise, in Article 3 post-intervention reaction time effect sizes ranged from $d = 2.28$ to $d = 35.97$.
+Continuing this pattern, post-intervention response accuracy effect sizes ranged from $d = 5.84$ to $d = 29.7$.
 
-A similar picture emerges when analyzing the accuracy data.
-All the pre-test differences were implausibly large (all $d$'s $\geq$ 2.52) despite being reported as not significantly different in the articles.
-Ten of the pairwise comparisons resulted in $d$'s $\geq$ 100 following treatment with the independent variables.
-The motor component data also revealed many post-treatment effect sizes that are implausibly large, ranging from $d$ = 1.16 to $d$ = 13.5.
-<!-- NOT SURE BUT IS IMPLAUSIBLY LARGE BEING THROWN AROUND TOO OFTEN THROUGHOUT THIS SECTION...SHOULD WE MAYBE JUST REPORT THE RANGE WITHOUT QUALIFYING IT LIKE THE PARAGRAPH BELOW?
--->
-
-In Article 2, post-intervention motor performance effect sizes ranged from $d$ = 3.1 to $d$ = 20.95.
-Similarly, post-intervention self-efficacy effect sizes ranged from $d$ = 1.79 to $d$ = 44.46.
-Similarly, in Article 3 post-intervention reaction time effect sizes ranged from $d$ = 2.28 to $d$ = 35.97.
-Continuing this pattern, post-intervention response accuracy effect sizes ranged from $d$ = 5.84 to $d$ = 29.7.
-
-In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from $d$ = 2.53 to $d$ = 15.50.
+In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from $d = 2.53$ to $d = 15.50$.
 Nevertheless, all pre-test comparisons were reported as non-significant.
-Following intervention, the effect sizes ranged from $d$ = 23.13 to $d$ = 155.08.
-
-The reaction time effect sizes were not implausibly large at any time point, ranging from $d$ = 0.0 to $d$ = .86.
+Following intervention, the effect sizes ranged from $d = 23.13$ to $d = 155.08$.
+The reaction time effect sizes were not implausibly large at any time point, ranging from $d = 0.0$ to $d = .86$.
 However, the authors reported an implausibly large effect size for the 4 (Group) x 3 (Time) ANOVA, $\eta^{2}$ = .94.
 Further, despite only one pairwise comparison being statistically significant, all post-intervention comparisons were reported as being significant in the article.
-<!-- IS THIS ALSO FOR ARTICLE 4, IF SO I THINK WE SHOULD COMBINE WITH PREVIOUS PARAGRAPH.
-I THINK IT BE GOOD TO HAVE A PARAGRAPH PER ARTICLE RATHER THAN A BUNCH OF SHORT PARAGRAPHS.
-THOUGHTS?
--->
 
@@
 These effect sizes are discussed further below.
-
 All the post-intervention effects reviewed above were directionally consistent with the researchers' expectations.
@@
 
-## Impossible data and granularity analysis
+## Impossible Data and Granularity Analysis
 
@@
 In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (M = 4.8, SD = 1.78).
+In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group ($M = 4.8$, $SD = 1.78$).
 The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
@@
 For two of the groups, however, they were consistent regardless which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent (M = 4.8, SD = 1.78).[^4]
+However, the results for the explicit group were GRIMMER inconsistent ($M = 4.8$, $SD = 1.78$).[^4]
 
-[^4]: You may have noticed that the same mean and standard deviation pairing (M = 4.8, SD = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences ($n$ = 20 for the consistent result and $n$ = 12 for the inconsistent one).
+[^4]: You may have noticed that the same mean and standard deviation pairing ($M = 4.8$, $SD = 1.78$) was classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences ($n = 20$ for the consistent result and $n = 12$ for the inconsistent one).
 
-## Test statistics and $\eta^{2}$
+## Eta-squared ($\eta^{2}$)
 
@@
 Benchmarks have been suggested for small, medium, and large $\eta^{2}$ effect sizes as $\eta^{2}$ = .01, .06, and .14, respectively [@cohen1988].
-Importantly, if a main effect of instruction type results in $\eta^{2}$ = .99, this suggests that 99% of the total variability in outcome measure can be explained by group assignment alone.
+Importantly, if a main effect of instruction-type results in $\eta^{2}$ = .99, as we will see commonly below, this suggests that $99\%$ of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
-<!-- IS THIS .99 JUST AN EXAMPLE? IF SO, MAYBE WE USE A MORE REALISTIC VALUE TO EXPLAIN THE INTERPRETATION. IF IT IS NOT AN EXAMPLE, THEN I THINK WE SHOULD REFER TO AN ARTICLE THAT HAS A .99 VALUE -->
-
-The range of significant $F$-statistics reported across the five articles in question was $F$ = 28.60 to $F$ = 101,489.71.
-Only three $F$-statistics were under 100 (28.60, 30.73, and 91.75), and all three were for interactions.
 
@@
 
-## Other oddities
+## Other Oddities
 
 Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5.
-The reported test statistic in these four articles was $F$ = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
+The reported test statistic in these four articles was $F = 52.67$, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
 Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2.
@@
 We assumed that each article was based on different samples as none of the articles mentioned using any previously published data.
-<!-- I REMOVED THE F-STATISTIC ISSUE FROM ABOVE AS IT FELT A BIT REPETITIVE BEING IN TWO SECTIONS AND DECIDED TO LET IT LIVE JUST IN THIS ODDITIES SECTION INSTEAD.
-FEEL FREE TO SWITCH AROUND IF YOU THINK IT WOULD BE BEST HIGHER UP.
--->
 
@@
 
-Other irregularities, such a repeating $F$-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
+Other irregularities, such as a repeating $F$-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
 Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed.

### 2021-08-19 docs/manuscript/manuscript.Rmd
update: minor edits

@@
 ---
-title             : "Data irregularities across five implicit learning: Comments on @lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015"
+title             : "Data irregularities across five implicit learning articles: Comments on @lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015"
 
@@
 We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations.
-We found the pairwise effect sizes were implausible in all five articles in question, with Cohen’s d values often exceeding 100 and sometimes exceeding 1000.
-Impossible statistics were reported in 4 out of the 5 articles.
+We found the pairwise effect sizes were implausible in all five articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000.
+Impossible statistics were reported in four out of the five articles.
 Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects.
@@
 
-csl               : "../apa.csl"
+# NEED TO BE RUNNING THE LATEST DEVELOPMENT SNAPSHOT OF PAPAJA
 documentclass     : "apa7"
-classoption       : "man" # use "doc" for 1-column preprint or "jou" for 2-column preprint
+classoption       : "man" 
 output            : papaja::apa6_pdf
@@
 During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed.
-The paper also referenced past research published by these authors, and given our cause for concern over the issues found in the @lola2021 paper, we deemed it necessary to examine these other papers.
+The paper also referenced past research published by these authors.
+Given our cause for concern over the issues found in the @lola2021 paper, we deemed it necessary to examine these other papers.
 We remain agnostic to the sources of error in each of these papers.
@@
 *International Journal of Sport and Exercise Psychology*, 1-21.
-<https://doi.org/10.1080/1612197X.2021.1877325>
+https://doi.org/10.1080/1612197X.2021.1877325
 
@@
 *Journal of Physical Education and Sport*, 20(5), 2478-2486.
-<https://doi.org/10.7752/jpes.2020.05339>
+https://doi.org/10.7752/jpes.2020.05339
 
@@
 *International Journal of Sport Psychology*, 46(2), 152-166.
-<https://doi.org/10.7352/IJSP.2015.46.152>
+https://doi.org/10.7352/IJSP.2015.46.152
 
@@
 *Perceptual and Motor Skills*, 114(2), 665-678.
-<https://doi.org/10.2466/05.23.25.PMS.114.2.665-678>
+https://doi.org/10.2466/05.23.25.PMS.114.2.665-678
 
@@
 [^2]: This article is in a journal of a publishing group that has been identified as a potential predatory journal.
-Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (<https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS>).
-In fact, the earliest available issue on the journal's webpage in from 2016.
+Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS).
+In fact, the earliest available issue on the journal's webpage is from 2016.
 
@@
 
-table_1 <- tibble(
+table_1 <- tibble::tibble(
   c1 = c("Lola \\& Tzetzis (2021)",
@@
 We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
-The authors' response was that the data could not be shared as they were not finished with their analysis and were in the process of running different tests (A.
+The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A.
 Lola, personal communication, February 12 2021).
 We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2 through 5 as these articles were less recent and presumably, all planned analyses had been completed.
-After a 2 week period with no response, we followed up on with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 Means and standard deviations were extracted from each article for all measures and time points that were reported.
-Cohen's $d$ was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}.
-To provide context, we simulated data from two groups of $n = 20$, consistent with groups sizes in Articles 1-4.
-We ran simulations with true effect sizes of $d = .80$ and $d = 3.0$ one million times each and report the range of effect sizes observed in those simulations.
+Cohen's *d* was calculated for each pairwise comparison using the `compute.es` package in `R`.
+To provide context, we simulated data from two groups of *n* = 20, consistent with groups sizes in Articles 1-4.
+We ran simulations with true effect sizes of *d* = .8 and *d* = 3 one million times each and report the range of effect sizes observed in those simulations.
 
@@
 
-In two of the articles in question, it was clear that the some of the reported results were not mathematically possible based on the scale of measurement that was used.
-When outcomes were single item integers (a granularity of 1), such as the number of explicit rules recalled, we used a web application (<http://www.prepubmed.org/grimmer_sd/>) to conduct a granularity analysis (GRIMMER) of reported means and standard deviations [@anaya2016].
+In two of the articles in question, it was clear that some of the reported results were not mathematically possible based on the scale of measurement that was used.
+When outcomes were single item integers (a granularity of 1), such as the number of explicit rules recalled, we used a web application (http://www.prepubmed.org/grimmer_sd/) to conduct a granularity analysis (GRIMMER) of reported means and standard deviations [@anaya2016].
 GRIMMER builds off the original Granularity-Related Inconsistency of Means (GRIM) analysis [@brown2017], which leveraged the fact that the means of granular data are also granular.
-Given a data set of size $N$ and granularity $G$, only means of granularity $G/N$ are possible.
-Thus, all possible means for data of a given $G$ and $N$ can be enumerated, and only means that match these possibilities are considered GRIM-consistent.
+Given a data set of size *N* and granularity *G*, only means of granularity $G/N$ are possible.
+Thus, all possible means for data of a given *G* and *N* can be enumerated, and only means that match these possibilities are considered GRIM-consistent.
 The GRIMMER analysis extends this test by also evaluating whether mean-standard deviation pairs are possible.
 First, the GRIM analysis is conducted to determine if the mean is GRIM-consistent.
-Next, lower and upper bounds of the standard deviation are calculated based on how many decimals ($D$) it is reported to by $(SD\pm^[0.5/10^{D}])^{2}$.
-Then all possible variances between these bounds are enumerated, converted back to standard deviations, and rounded to the nearest $D$ decimals.
+Next, lower and upper bounds of the standard deviation are calculated based on how many decimals (*D*) are reported $(SD\pm[\frac{0.5}{10^{D}}])^{2}$.
+Then all possible variances between these bounds are enumerated, converted back to standard deviations, and rounded to the nearest *D* decimals.
 The reported standard deviation is checked for a match with any of these values.
@@
 
-Cohen's $d$ is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
+Cohen's *d* is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
 Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion].
-Conventional benchmarks for small, medium and large effects are $d$ = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [@thompson2007; @lakens2013; @field2016; @correll2020].
-Recently, an analysis of 6447 Cohen's $d$ statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's $d$ values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].
+Conventional benchmarks for small, medium and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions].
+Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].
 
-To evaluate the maximum range of plausible Cohen's $d$ statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of 1,000,000 experiments.
-For the first simulation we set the true effect size at $d$ = .80, the conventional benchmark for a "large" treatment effect.
-The largest effect size observed from the 1,000,000 simulated experiments was $d = 2.97$ (see Figure \@ref(fig:fig1)).
-In the second simulation, we set the true effect size at $d = 3.0$, an unrealistically large effect size that might rarely be encountered in the psychology literature.
-The maximum effect size observed in the 1,000,000 simulated experiments was $d = 6.6$.
+To evaluate the maximum range of plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
+We set the true effect size at *d* = .8, the conventional benchmark for a "large" treatment effect, in the first simulation.
+The largest effect size observed from the one million simulated experiments was *d* = 2.97.
+In the second simulation, we set the true effect size at *d* = 3, an unrealistically large effect size that might rarely be encountered in the psychology literature.
+The maximum effect size observed in the one million simulated experiments was *d* = 6.6.
 
-(ref:fig1-caption) Absolute Cohen's d estimates from Articles 1-4 plotted on a logarithmic scale.
+(ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-4 plotted on a logarithmic scale.
 All pairwise comparisons have been included for all dependent measures in each experiment.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d = .80$ is illustrated by light green and dark blue regions of the figure, reaching a maximum value of $d = 2.97$.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3.0 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of $d = 6.6$.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = .8 is illustrated by light green and dark blue regions of the figure, reaching a maximum value of $d$ = 2.97.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of $d$ = 6.6.
 
@@
 In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference on the reaction measure was $d = 1.29$, while the largest pre-test difference was $d = 35.32$, although none of the groups were reported as significantly different in the article.
-The smallest post-intervention effect at any of the three time points was $d = 286.42$, while the largest effect was $d = 3504.86$.
+In Article 1, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
+The smallest post-intervention effect at any of the three time points was *d* = 286.42, while the largest effect was *d* = 3504.86.
 A similar picture emerges when analyzing the accuracy data.
-All the pre-test differences were improbably large (all $d$'s $\geq$ 2.52) despite being reported as not significantly different in the articles.
-Ten of the pairwise comparisons resulted in $d$'s $\geq$ 100 following treatment with the independent variables.
-The motor component data revealed post-treatment effect sizes ranging from $d = 1.16$ to $d = 13.5$.
+All the pre-test differences were improbably large (all *d*'s $\geq$ 2.52) despite being reported as not significantly different in the articles.
+Ten of the pairwise comparisons resulted in *d*'s $\geq$ 100 following treatment with the independent variables.
+The motor component data revealed post-treatment effect sizes ranging from *d* = 1.16 to *d* = 13.5.
 
-In Article 2, post-intervention motor performance effect sizes ranged from $d = 3.1$ to $d = 20.95$.
-Similarly, post-intervention self-efficacy effect sizes ranged from $d = 1.79$ to $d = 44.46$.
-Likewise, in Article 3 post-intervention reaction time effect sizes ranged from $d = 2.28$ to $d = 35.97$.
-Continuing this pattern, post-intervention response accuracy effect sizes ranged from $d = 5.84$ to $d = 29.7$.
+In Article 2, post-intervention motor performance effect sizes ranged from *d* = 3.1 to *d* = 20.95.
+Similarly, post-intervention self-efficacy effect sizes ranged from *d* = 1.79 to *d* = 44.46.
+Likewise, in Article 3 post-intervention reaction time effect sizes ranged from *d* = 2.28 to *d* = 35.97.
+Continuing this pattern, post-intervention response accuracy effect sizes ranged from *d* = 5.84 to *d* = 29.7.
 
-In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from $d = 2.53$ to $d = 15.50$.
+In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from *d* = 2.53 to *d* = 15.50.
 Nevertheless, all pre-test comparisons were reported as non-significant.
-Following intervention, the effect sizes ranged from $d = 23.13$ to $d = 155.08$.
-The reaction time effect sizes were not implausibly large at any time point, ranging from $d = 0.0$ to $d = .86$.
-However, the authors reported an implausibly large effect size for the 4 (Group) x 3 (Time) ANOVA, $\eta^{2}$ = .94.
+Following intervention, the effect sizes ranged from *d* = 23.13 to *d* = 155.08.
+Relative to other reported effect sizes, those reported for reaction time were not implausibly large at any time point, ranging from *d* = 0 to *d* = .86.
+However, the authors reported an implausibly large effect size, $\eta^{2}$ = .94, for the 4 (Group) x 3 (Time) ANOVA.
 Further, despite only one pairwise comparison being statistically significant, all post-intervention comparisons were reported as being significant in the article.
 
-In Article 5 the authors did not report means and standard deviations for most of the analyses.
+In Article 5, the authors did not report means and standard deviations for most of the analyses.
 However, $\eta^{2}$ effect sizes were reported and these ranged from $\eta^{2}$ = .52 to $\eta^{2}$ = .98.
@@
 
-[^3]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [@reeve1994; @hancock1995; @fischman2015].
+[^3]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [see @fischman2015; @hancock1995; @reeve1994 for discussions].
 
@@
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-
 In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group ($M = 4.8$, $SD = 1.78$).
+In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78).
 The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
 In Article 5, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
-For two of the groups, however, they were consistent regardless which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent ($M = 4.8$, $SD = 1.78$).[^4]
+For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
+However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^4]
 
-[^4]: You may have noticed that the same mean and standard deviation pairing ($M = 4.8$, $SD = 1.78$) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences ($n = 20$ for the consistent result and $n = 12$ for the inconsistent one).
+[^4]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences (*n* = 20 for the consistent result and *n* = 12 for the inconsistent one).
 
@@
 Eta-squared ($\eta^{2}$) is calculated by dividing the sum of squares for the effect by the total sum of squares.
-It can be interpreted as analogous to $R^{2}$: It represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an analysis of variance [@lakens2013].
-Benchmarks have been suggested for small, medium, and large $\eta^{2}$ effect sizes as $\eta^{2}$ = .01, .06, and .14, respectively [@cohen1988].
-Importantly, if a main effect of instruction-type results in $\eta^{2}$ = .99, as we will see commonly below, this suggests that $99\%$ of the total variability in the outcome measure can be explained by group assignment alone.
+It can be interpreted as analogous to $R^{2}$ as it represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an ANOVA [@lakens2013].
+Benchmarks have been suggested for small, medium, and large effect sizes as $\eta^{2}$ = .01, .06, and .14, respectively [@cohen1988].
+Importantly, if a main effect of instruction-type results in $\eta^{2}$ = .99, as we will see commonly below, this suggests that 99% of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
 
-Article 1 did not report $\eta^{2}$ values but had the largest pairwise effects and $F$-statistics of the five articles in question.
-Article 2 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance.
+Article 1 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question.
+Article 2 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
 Similarly, variance explained on the self-efficacy measure was $\eta^{2}$ = .995, $\eta^{2}$ = .994, $\eta^{2}$ = .997 for the Time, Group, and Time x Group effects, respectively.
@@
 Article 4 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure.
-Interestingly, the Time x Group interaction had the smallest reported significant $F$-statistic among the five articles in question.
-With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses.
-Article 5 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses.
+Interestingly, the Time x Group interaction had the smallest reported significant *F*-statistic among the five articles in question.
+With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses, respectively.
+Article 5 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.
 
@@
 Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5.
-The reported test statistic in these four articles was $F = 52.67$, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
+The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
 Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2.
@@
 
-Other irregularities, such as a repeating $F$-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
+Other irregularities, such as a repeating *F*-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
 Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed.
@@
 
-\newpage
-
 # References

### 2021-08-19 docs/manuscript/manuscript.tex
update: minor edits

@@
 \hypersetup{
-  pdftitle={Data irregularities across five implicit learning articles by the same researchers},
+  pdftitle={Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)},
   pdfauthor={Brad McKay1 \& Michael J. Carter1},
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
 
@@
 
-\title{Data irregularities across five implicit learning articles by the same researchers}
+\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
 \author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
@@
 We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations.
-We found the pairwise effect sizes were implausible in all five articles in question, with Cohen's d values often exceeding 100 and sometimes exceeding 1000.
-Impossible statistics were reported in 4 out of the 5 articles.
+We found the pairwise effect sizes were implausible in all five articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000.
+Impossible statistics were reported in four out of the five articles.
 Reported test statistics and \(\eta^{2}\) values were also implausible, with several \(\eta^{2}\) = .99 and even \(\eta^{2}\) = 1.0 for between-subjects main effects.
@@
 
-Statistical reporting errors may commonly occur in psychology articles (Brown \& Heathers, 2017; Nuijten et al., 2016) and such errors are often consistent with hypothesized results (Bakker \& Wicherts, 2011).
+Statistical reporting errors may commonly occur in psychology articles (Brown \& Heathers, 2017; Nuijten, Hartgerink, van Assen, Epskamp, \& Wicherts, 2016) and such errors are often consistent with hypothesized results (Bakker \& Wicherts, 2011).
 When the primary conclusions in research articles depend on reporting errors, replicability is unlikely and future research may be wasted if researchers attempt to build on the erroneously reported results (Munafò et al., 2017).
@@
 During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed.
-The paper also referenced past research published by these authors, and given our cause for concern over the issues found in the Lola and Tzetzis (2021) paper, we deemed it necessary to examine these other papers.
+The paper also referenced past research published by these authors.
+Given our cause for concern over the issues found in the Lola and Tzetzis (2021) paper, we deemed it necessary to examine these other papers.
 We remain agnostic to the sources of error in each of these papers.
@@
 \hypertarget{the-articles-in-question}{%
-\subsection{The articles in question}\label{the-articles-in-question}}
+\subsection{The Articles in Question}\label{the-articles-in-question}}
 
-We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., 2012; Lola \& Tzetzis, 2021, 2020; Tzetzis \& Lola, 2010, 2015).
+We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
@@
 Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS}).
-In fact, the earliest available issue on the journal's webpage in from 2016.}
+In fact, the earliest available issue on the journal's webpage is from 2016.}
 \end{enumerate}
@@
 In Lola and Tzetzis (2021) for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team.
-Further, it was often predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.
+Further, it was predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.
 
 The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2).
-In addition, Articles 1 and 5 included a measure of state anxiety with the Competitive State Anxiety Inventory-2 (CSAI-2) (Tsorbatzoudis et al., 1998), and Article 2 had a measure of self-efficacy using a Likert scale.
+In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (CSAI-2) (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 2 had a measure of self-efficacy using a Likert scale.
 Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.
@@
 None of the five articles in question included a link to a public repository where the data could be accessed.
-We first wrote (email sent February 11 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
-The authors' response was that the data could not be shared as they were not finished with their analysis and were in the process of running different tests (A.
+We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
+The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A.
 Lola, personal communication, February 12 2021).
 We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2 through 5 as these articles were less recent and presumably, all planned analyses had been completed.
-After a 2 week period with no response, we followed up on with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 \hypertarget{effect-size-calculations-and-simulations}{%
-\subsection{Effect size calculations and simulations}\label{effect-size-calculations-and-simulations}}
+\subsection{Effect Size Calculations and Simulations}\label{effect-size-calculations-and-simulations}}
 
 Means and standard deviations were extracted from each article for all measures and time points that were reported.
-Cohen's \(d\) was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}.
-To provide context, we simulated data with true effect sizes of \(d\) = .80 and \(d\) = 3.0 one million times each and report the range of effect sizes observed in those simulations.
+Cohen's \emph{d} was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}.
+To provide context, we simulated data from two groups of \emph{n} = 20, consistent with groups sizes in Articles 1-4.
+We ran simulations with true effect sizes of \emph{d} = .8 and \emph{d} = 3 one million times each and report the range of effect sizes observed in those simulations.
 
 \hypertarget{mathematically-impossible-data-and-granularity-analysis}{%
-\subsection{Mathematically impossible data and granularity analysis}\label{mathematically-impossible-data-and-granularity-analysis}}
+\subsection{Mathematically Impossible Data and Granularity Analysis}\label{mathematically-impossible-data-and-granularity-analysis}}
 
-In two of the articles in question, it was clear that the some of the reported results were not mathematically possible based on the scale of measurement that was used.
-When outcomes were single item integers, such as the number of explicit rules recalled, we used a web application (\url{http://www.prepubmed.org/grimmer_sd/}) to conduct a granularity analysis called GRIMMER (Anaya, 2016).
-Using GRIMMER it is possible to determine if specific means and standard deviations are possible for a given sample size.
+In two of the articles in question, it was clear that some of the reported results were not mathematically possible based on the scale of measurement that was used.
+When outcomes were single item integers (a granularity of 1), such as the number of explicit rules recalled, we used a web application (\url{http://www.prepubmed.org/grimmer_sd/}) to conduct a granularity analysis (GRIMMER) of reported means and standard deviations (Anaya, 2016).
+GRIMMER builds off the original Granularity-Related Inconsistency of Means (GRIM) analysis (Brown \& Heathers, 2017), which leveraged the fact that the means of granular data are also granular.
+Given a data set of size \emph{N} and granularity \emph{G}, only means of granularity \(G/N\) are possible.
+Thus, all possible means for data of a given \emph{G} and \emph{N} can be enumerated, and only means that match these possibilities are considered GRIM-consistent.
+The GRIMMER analysis extends this test by also evaluating whether mean-standard deviation pairs are possible.
+First, the GRIM analysis is conducted to determine if the mean is GRIM-consistent.
+Next, lower and upper bounds of the standard deviation are calculated based on how many decimals (\emph{D}) are reported \((SD\pm[\frac{0.5}{10^{D}}])^{2}\).
+Then all possible variances between these bounds are enumerated, converted back to standard deviations, and rounded to the nearest \emph{D} decimals.
+The reported standard deviation is checked for a match with any of these values.
+Finally, the mean-variance pair is compared to possible mean-variance pairings (the GRIMMER test handles sample sizes between 5 and 99).
+Using GRIMMER it is possible to determine if specific mean and standard deviation pairs are possible for data of a given sample size.
 To be conservative, we specified that we did not know whether the standard deviation was calculated for the sample or population, nor whether ambiguous values were rounded up or down.
@@
 
-\hypertarget{test-statistics-and-eta2}{%
-\subsection{\texorpdfstring{Test statistics and \(\eta^{2}\)}{Test statistics and \textbackslash eta\^{}\{2\}}}\label{test-statistics-and-eta2}}
+\hypertarget{eta-squared-eta2}{%
+\subsection{\texorpdfstring{Eta-squared (\(\eta^{2}\))}{Eta-squared (\textbackslash eta\^{}\{2\})}}\label{eta-squared-eta2}}
 
@@
 However, the test statistics reported for many analyses were implausibly large and the authors often reported \(\eta^{2}\) values associated with the omnibus test.
-Our examination of the reported \(\eta^{2}\) values revealed that many were not only implausibly large, but also consistent with the reported pairwise effects.
+Our examination of the reported \(\eta^{2}\) values revealed that, as with the reported pairwise comparisons, many were implausibly large.
 
@@
 \hypertarget{implausible-effect-sizes}{%
-\subsection{Implausible effect sizes}\label{implausible-effect-sizes}}
+\subsection{Implausible Effect Sizes}\label{implausible-effect-sizes}}
 
-Cohen's \(d\) is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
+Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
 Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion).
-Conventional benchmarks for small, medium and large effects are \(d\) = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (Correll et al., 2020; Field \& Iles, 2016; Lakens, 2013; Thompson, 2007).
-Recently, an analysis of 6447 Cohen's \(d\) statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \(d\) values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).
+Conventional benchmarks for small, medium and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions).
+Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).
 
-To evaluate the maximum range of plausible Cohen's \(d\) statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of 1,000,000 experiments.
-For the first simulation we set the true effect size at \(d\) = .80, the conventional benchmark for a ``large'' treatment effect.
-The largest effect size observed from the 1,000,000 simulated experiments was \(d\) = 2.97 (see Figure \ref{fig:fig1}).
-In the second simulation, we set the true effect size at \(d\) = 3.0, an unrealistically large effect size that might rarely be encountered in the psychology literature.
-The maximum effect size observed in the 1,000,000 simulated experiments was \(d\) = 6.6.
+To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
+We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation.
+The largest effect size observed from the one million simulated experiments was \emph{d} = 2.97.
+In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology literature.
+The maximum effect size observed in the one million simulated experiments was \emph{d} = 6.6.
 
@@
 
-\caption{Absolute Cohen's d estimates from Articles 1-4 plotted on a logarithmic scale.
+\caption{Absolute Cohen's \(d\) estimates from Articles 1-4 plotted on a logarithmic scale.
 All pairwise comparisons have been included for all dependent measures in each experiment.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .80 is illustrated by light blue and dark blue regions of the figure, reaching a maximum value of \(d\) = 2.97.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3.0 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of \(d\) = 6.86.}\label{fig:fig1}
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by light green and dark blue regions of the figure, reaching a maximum value of \(d\) = 2.97.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
 \end{figure}
@@
 In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference on the reaction measure was \(d\) = 1.29, while the largest pre-test difference was \(d\) = 35.32, although none of the groups were reported as significantly different in the article.
-The smallest post-intervention effect at any of the three time points was \(d\) = 286.42, while the largest effect was \(d\) = 3504.86.
+In Article 1, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
+The smallest post-intervention effect at any of the three time points was \emph{d} = 286.42, while the largest effect was \emph{d} = 3504.86.
+A similar picture emerges when analyzing the accuracy data.
+All the pre-test differences were improbably large (all \emph{d}'s \(\geq\) 2.52) despite being reported as not significantly different in the articles.
+Ten of the pairwise comparisons resulted in \emph{d}'s \(\geq\) 100 following treatment with the independent variables.
+The motor component data revealed post-treatment effect sizes ranging from \emph{d} = 1.16 to \emph{d} = 13.5.
 
-A similar picture emerges when analyzing the accuracy data.
-All the pre-test differences were implausibly large (all \(d\)'s \(\geq\) 2.52) despite being reported as not significantly different in the articles.
-Ten of the pairwise comparisons resulted in \(d\)'s \(\geq\) 100 following treatment with the independent variables.
-The motor component data also revealed many post-treatment effect sizes that are implausibly large, ranging from \(d\) = 1.16 to \(d\) = 13.5.
+In Article 2, post-intervention motor performance effect sizes ranged from \emph{d} = 3.1 to \emph{d} = 20.95.
+Similarly, post-intervention self-efficacy effect sizes ranged from \emph{d} = 1.79 to \emph{d} = 44.46.
+Likewise, in Article 3 post-intervention reaction time effect sizes ranged from \emph{d} = 2.28 to \emph{d} = 35.97.
+Continuing this pattern, post-intervention response accuracy effect sizes ranged from \emph{d} = 5.84 to \emph{d} = 29.7.
 
-In Article 2, post-intervention motor performance effect sizes ranged from \(d\) = 3.1 to \(d\) = 20.95.
-Similarly, post-intervention self-efficacy effect sizes ranged from \(d\) = 1.79 to \(d\) = 44.46.
-Similarly, in Article 3 post-intervention reaction time effect sizes ranged from \(d\) = 2.28 to \(d\) = 35.97.
-Continuing this pattern, post-intervention response accuracy effect sizes ranged from \(d\) = 5.84 to \(d\) = 29.7.
-
-In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from \(d\) = 2.53 to \(d\) = 15.50.
+In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from \emph{d} = 2.53 to \emph{d} = 15.50.
 Nevertheless, all pre-test comparisons were reported as non-significant.
-Following intervention, the effect sizes ranged from \(d\) = 23.13 to \(d\) = 155.08.
-
-The reaction time effect sizes were not implausibly large at any time point, ranging from \(d\) = 0.0 to \(d\) = .86.
-However, the authors reported an implausibly large effect size for the 4 (Group) x 3 (Time) ANOVA, \(\eta^{2}\) = .94.
+Following intervention, the effect sizes ranged from \emph{d} = 23.13 to \emph{d} = 155.08.
+Relative to other reported effect sizes, those reported for reaction time were not implausibly large at any time point, ranging from \emph{d} = 0 to \emph{d} = .86.
+However, the authors reported an implausibly large effect size, \(\eta^{2}\) = .94, for the 4 (Group) x 3 (Time) ANOVA.
 Further, despite only one pairwise comparison being statistically significant, all post-intervention comparisons were reported as being significant in the article.
 
-In Article 5 the authors did not report means and standard deviations for most of the analyses.
+In Article 5, the authors did not report means and standard deviations for most of the analyses.
 However, \(\eta^{2}\) effect sizes were reported and these ranged from \(\eta^{2}\) = .52 to \(\eta^{2}\) = .98.
 These effect sizes are discussed further below.
-
 All the post-intervention effects reviewed above were directionally consistent with the researchers' expectations.
@@
 \hypertarget{impossible-data-and-granularity-analysis}{%
-\subsection{Impossible data and granularity analysis}\label{impossible-data-and-granularity-analysis}}
+\subsection{Impossible Data and Granularity Analysis}\label{impossible-data-and-granularity-analysis}}
 
@@
 In Article 2, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
-Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.\footnote{Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task (Fischman, 2015; Hancock et al., 1995; Reeve et al., 1994).} Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
+Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.\footnote{Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task (see Fischman, 2015; Hancock, Butler, \& Fischman, 1995; Reeve, Fischman, Christina, \& Cauraugh, 1994 for discussions).} Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
 The perfect score was not a rounding error because the same group was reported to have a mean score of 2.99 with a standard deviation of .11 on the post-test.
@@
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-
 In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (M = 4.8, SD = 1.78).
+In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78).
 The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
 In Article 5, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
-For two of the groups, however, they were consistent regardless which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent (M = 4.8, SD = 1.78).\footnote{You may have noticed that the same mean and standard deviation pairing (M = 4.8, SD = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences (\(n\) = 20 for the consistent result and \(n\) = 12 for the inconsistent one).}
+For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
+However, the results for the explicit group were GRIMMER inconsistent (\emph{M} = 4.8, \emph{SD} = 1.78).\footnote{You may have noticed that the same mean and standard deviation pairing (\emph{M} = 4.8, \emph{SD} = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences (\emph{n} = 20 for the consistent result and \emph{n} = 12 for the inconsistent one).}
 
-\hypertarget{test-statistics-and-eta2-1}{%
-\subsection{\texorpdfstring{Test statistics and \(\eta^{2}\)}{Test statistics and \textbackslash eta\^{}\{2\}}}\label{test-statistics-and-eta2-1}}
+\hypertarget{eta-squared-eta2-1}{%
+\subsection{\texorpdfstring{Eta-squared (\(\eta^{2}\))}{Eta-squared (\textbackslash eta\^{}\{2\})}}\label{eta-squared-eta2-1}}
 
 Eta-squared (\(\eta^{2}\)) is calculated by dividing the sum of squares for the effect by the total sum of squares.
-It can be interpreted as analogous to \(R^{2}\): It represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an analysis of variance (Lakens, 2013).
-Benchmarks have been suggested for small, medium, and large \(\eta^{2}\) effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988).
-Importantly, if a main effect of instruction type results in \(\eta^{2}\) = .99, this suggests that 99\% of the total variability in outcome measure can be explained by group assignment alone.
+It can be interpreted as analogous to \(R^{2}\) as it represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an ANOVA (Lakens, 2013).
+Benchmarks have been suggested for small, medium, and large effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988).
+Importantly, if a main effect of instruction-type results in \(\eta^{2}\) = .99, as we will see commonly below, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
 
-The range of significant \(F\)-statistics reported across the five articles in question was \(F\) = 28.60 to \(F\) = 101,489.71.
-Only three \(F\)-statistics were under 100 (28.60, 30.73, and 91.75), and all three were for interactions.
-
-Article 1 did not report \(\eta^{2}\) values but had the largest pairwise effects and \(F\)-statistics of the five articles in question.
-Article 2 reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance.
+Article 1 did not report \(\eta^{2}\) values but had the largest pairwise effects and \emph{F}-statistics of the five articles in question.
+Article 2 reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
 Similarly, variance explained on the self-efficacy measure was \(\eta^{2}\) = .995, \(\eta^{2}\) = .994, \(\eta^{2}\) = .997 for the Time, Group, and Time x Group effects, respectively.
@@
 Article 4 reported \(\eta^{2}\) = 1.0 for the main effect of Time and the Time x Group interaction, as well as \(\eta^{2}\) = .95 for the main effect of Group on the response time measure.
-Interestingly, the Time x Group interaction had the smallest reported significant \(F\)-statistic among the five articles in question.
-With respect to response accuracy, the reported effects were \(\eta^{2}\) = .98, \(\eta^{2}\) = .94, \(\eta^{2}\) = .93 for the Time, Group, and Time x Group analyses.
-Article 5 reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses.
+Interestingly, the Time x Group interaction had the smallest reported significant \emph{F}-statistic among the five articles in question.
+With respect to response accuracy, the reported effects were \(\eta^{2}\) = .98, \(\eta^{2}\) = .94, \(\eta^{2}\) = .93 for the Time, Group, and Time x Group analyses, respectively.
+Article 5 reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses, respectively.
 
 \hypertarget{other-oddities}{%
-\subsection{Other oddities}\label{other-oddities}}
+\subsection{Other Oddities}\label{other-oddities}}
 
 Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5.
-The reported test statistic in these four articles was \(F\) = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
+The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
 Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2.
@@
 
-We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola et al., 2012; Lola \& Tzetzis, 2021, 2020; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 
-Other irregularities, such a repeating \(F\)-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
+Other irregularities, such as a repeating \emph{F}-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
 Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed.
@@
 At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-07-08), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-08-19), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
 
@@
 
-R {[}Version 4.1.0; R Core Team (2021){]} and the R-packages \emph{compute.es} {[}Version 0.2.5; Re (2013){]}, \emph{kableExtra} {[}Version 1.3.4; Zhu (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, and \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
-(2019){]}.
+R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
 
@@
 The authors declare no competing interests.
-
-\newpage
 
@@
 \leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
@@
 
-\leavevmode\hypertarget{ref-cohen1988}{}%
-Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). Routledge. \url{https://doi.org/10.4324/9780203771587}
-
 \leavevmode\hypertarget{ref-cohen1962}{}%
@@
 \url{https://doi.org/10.1037/h0045186}
+
+\leavevmode\hypertarget{ref-cohen1988}{}%
+Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). New York: Routledge. \url{https://doi.org/10.4324/9780203771587}
 
@@
 \leavevmode\hypertarget{ref-field2016}{}%
-Field, A. P., \& Iles, J. (2016). \emph{An adventure in statistics: The reality enigma}.
+Field, A. P. (2016). \emph{An adventure in statistics: The reality enigma}.
 
@@
 
+\leavevmode\hypertarget{ref-lola2020}{}%
+Lola, A.
+C., \& Tzetzis, G.
+C.
+(2020).
+Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy.
+\emph{Journal of Physical Education and Sport}, \emph{20}(5), 2478--2486.
+Retrieved from \url{https://www.cabdirect.org/cabdirect/abstract/20203562097}
+
 \leavevmode\hypertarget{ref-lola2021}{}%
@@
 \url{https://doi.org/10.1080/1612197X.2021.1877325}
-
-\leavevmode\hypertarget{ref-lola2020}{}%
-Lola, A.
-C., \& Tzetzis, G.
-C.
-(2020).
-Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy.
-\emph{Journal of Physical Education and Sport}, \emph{20}(5), 2478--2486.
-\url{https://www.cabdirect.org/cabdirect/abstract/20203562097}
 
@@
 S., Chambers, C.
-D., Percie du Sert, N., Simonsohn, U., Wagenmakers, E.-J., Ware, J.
-J., \& Ioannidis, J.
+D., Percie du Sert, N., \ldots{} Ioannidis, J.
 P.
@@
 \leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
 \leavevmode\hypertarget{ref-R-compute.es}{}%
-Re, A. C. D. (2013). Compute.es: Compute effect sizes. In \emph{R Package}. \url{https://cran.r-project.org/package=compute.es}
+Re, A. C. D. (2013). Compute.es: Compute effect sizes. In \emph{R Package}. Retrieved from \url{https://cran.r-project.org/package=compute.es}
 
@@
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
+D., François, R., \ldots{} Yutani, H.
 (2019).
@@
 \leavevmode\hypertarget{ref-R-kableExtra}{}%
-Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. \url{https://CRAN.R-project.org/package=kableExtra}
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
 

### 2021-08-22 docs/manuscript/manuscript.Rmd
update: add r package citations

@@
 
-shorttitle        : "Data irregularities"
+shorttitle        : "Commentary on Lola & Tzetzis papers"
 
@@
 keywords          : "Meta-science; GRIMMER; Effect sizes; Perceptual motor learning"
-wordcount         : "X"
+#wordcount         : "X"
 
@@
 
+# Acknowledgements
+We would like to thank Abbey Corson for her help with data extraction from the target articles.
+
 # Data, materials, and code availability

### 2021-08-22 docs/manuscript/manuscript.tex
update: add r package citations

@@
 \makeatother
-\shorttitle{Data irregularities}
-\keywords{Meta-science; GRIMMER; Effect sizes; Perceptual motor learning\newline\indent Word count: X}
+\shorttitle{Commentary on Lola \& Tzetzis papers}
+\keywords{Meta-science; GRIMMER; Effect sizes; Perceptual motor learning}
 \usepackage{lineno}
@@
 At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-08-19), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-08-20), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+We would like to thank Abbey Corson for her help with data extraction from the target articles.
 
@@
 
-R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
+R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
 
@@
 
+\leavevmode\hypertarget{ref-R-lemon}{}%
+Edwards, S. M. (2020). \emph{Lemon: Freshing up your 'ggplot2' plots}. Retrieved from \url{https://CRAN.R-project.org/package=lemon}
+
 \leavevmode\hypertarget{ref-field2016}{}%
@@
 \url{https://doi.org/10.1016/j.humov.2015.05.011}
+
+\leavevmode\hypertarget{ref-R-daff}{}%
+Fitzpatrick, P., de Jonge, E., \& Warnes, G. R. (2019). \emph{Daff: Diff, patch and merge for data.frames}. Retrieved from \url{https://CRAN.R-project.org/package=daff}
 
@@
 
+\leavevmode\hypertarget{ref-R-gridGraphics}{}%
+Murrell, P., \& Wen, Z. (2020). \emph{gridGraphics: Redraw base graphics using 'grid' graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridGraphics}
+
+\leavevmode\hypertarget{ref-R-lsr}{}%
+Navarro, D.
+(2015).
+\emph{Learning statistics with r: A tutorial for psychology students and other beginners.
+(Version 0.5)}.
+Adelaide, Australia: University of Adelaide.
+Retrieved from \url{http://ua.edu.au/ccs/teaching/lsr}
+
+\leavevmode\hypertarget{ref-R-RColorBrewer}{}%
+Neuwirth, E. (2014). \emph{RColorBrewer: ColorBrewer palettes}. Retrieved from \url{https://CRAN.R-project.org/package=RColorBrewer}
+
 \leavevmode\hypertarget{ref-nuijten2016}{}%
@@
 
+\leavevmode\hypertarget{ref-R-scales}{}%
+Wickham, H., \& Seidel, D. (2020). \emph{Scales: Scale functions for visualization}. Retrieved from \url{https://CRAN.R-project.org/package=scales}
+
 \leavevmode\hypertarget{ref-R-kableExtra}{}%

### 2021-08-22 scripts/sim_script.R
init

@@ -1,0 +1,81 @@
+library(lsr)
+library(cowplot)
+library(ggplot2)
+library(gridGraphics)
+# set seed for reproducible results
+
+set.seed(9293)
+
+# specify number of simulations
+
+iters <- 1000000
+
+
+# save cohens d estimate from each simulation
+
+d <- rep(NA, iters)
+
+# run simulations
+
+for (i in 1:iters) {
+  
+  x1 <- rnorm(20, mean=0, sd=1)
+  x2 <- rnorm(20, mean=0.8, sd=1)
+  res <- cohensD(x1, x2)
+  d[i] <- res
+  
+}
+
+round(max(d), digits = 2)
+
+round(mean(d), digits = 2)
+
+dres <- density(d)
+a <- plot(dres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == .80))+
+polygon(dres, col="blue", border="black")
+
+p1_recorded <- recordPlot(a)
+
+ggdraw(p1_recorded)
+
+#### repeat with true effect of d = 3
+
+
+
+# specify number of simulations
+
+iters <- 1000000
+
+
+# save cohens d estimate from each simulation
+
+dmax <- rep(NA, iters)
+
+# run simulations
+
+for (i in 1:iters) {
+  
+  x1 <- rnorm(20, mean=0, sd=1)
+  x2 <- rnorm(20, mean=3, sd=1)
+  res <- cohensD(x1, x2)
+  dmax[i] <- res
+  
+}
+
+round(max(dmax), digits = 2)
+
+round(mean(dmax), digits = 2)
+
+round(min(dmax), digits = 2)
+
+dmaxres <- density(dmax)
+b <- plot(dmaxres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == 3.0))+
+polygon(dmaxres, col="black", border="black")
+
+p2_recorded <- recordPlot(b)
+
+ggdraw(p2_recorded)
+
+
+
+plot_grid(p1_recorded, p2_recorded, labels = c('A', 'B'), label_size = 12)

### 2021-08-22 scripts/script.R
init

@@ -1,0 +1,583 @@
+library(compute.es)
+library(daff)
+library(ggplot2)
+library(tidyr)
+library(scales)
+library(RColorBrewer)
+library(lemon)
+
+## read in Brad's extraction for 2012 paper
+
+bac12 <- read.csv("2012/data_Ac.csv")
+brt12 <- read.csv("2012/data_RT.csv")
+
+
+## read in Abbey's extraction for 2012 paper
+
+aac12 <- read.csv("Abbey/data/2012/data_Ac.csv")
+
+art12 <- read.csv("Abbey/data/2012/data_Rt.csv")
+
+#### compare Brad and Abbey's extractions
+
+# accuracy data
+
+dif <- diff_data(bac12, aac12)
+
+render_diff(dif)
+
+##### Brad's extraction contained an error on explicit pre-test mean. Label Abbey's extraction "data_Ac'
+
+data_Ac <- aac12
+
+# response time data
+
+dif2 <- diff_data(brt12, art12)
+
+render_diff(dif2)
+
+##### extractions match. Label Brad's data "data_Rt"
+
+data_RT <- brt12
+
+## 2012 paper accuracy effect size calculations
+
+I_E <- mes(E_m, I_m, E_sd, I_sd, n, n, id = id, data = data_Ac)
+
+I_E <- I_E$d
+
+E_S <- mes(E_m, S_m, E_sd, S_sd, n, n, id = id, data = data_Ac)
+
+E_S <- E_S$d
+ 
+E_C <- mes(E_m, C_m, E_sd, C_sd, n, n, id = id, data = data_Ac)
+
+E_C <- E_C$d
+ 
+I_S <- mes(I_m, S_m, I_sd, S_sd, n, n, id = id, data = data_Ac)
+
+I_S <- I_S$d
+
+I_C <- mes(I_m, C_m, I_sd, C_sd, n, n, id = id, data = data_Ac)
+
+I_C <- I_C$d
+ 
+S_C <- mes(S_m, C_m, S_sd, C_sd, n, n, id = id, data = data_Ac)
+
+S_C <- S_C$d
+
+id <- data_Ac$id
+
+#### create table of accuracy effect sizes for 2012 paper
+
+accuracy_2012 <- cbind(I_E, E_S, E_C, I_S, I_C, S_C, id)
+accuracy_2012 <- as.data.frame(accuracy_2012)
+
+
[…]

### 2021-09-11 docs/manuscript/manuscript.Rmd
update: minor edits

@@
 documentclass     : "apa7"
-classoption       : "man" 
+classoption       : "man, donotrepeattitle" 
 output            : papaja::apa6_pdf
@@
 Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-The five articles will be referred to throughout this paper using the following numbering system:
+We will refer to the five articles throughout this paper using the following numbering system:
 
@@
 The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2).
-In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (CSAI-2) [@tsorbatzoudis1998], and Article 2 had a measure of self-efficacy using a Likert scale.
+In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 2 had a measure of self-efficacy using a Likert scale.
 Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.
@@
 Lola, personal communication, February 12 2021).
-We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2 through 5 as these articles were less recent and presumably, all planned analyses had been completed.
-After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5.
+We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2-5 as these articles were less recent and presumably, all planned analyses had been completed.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2-5.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 
-Our first two requests did not include any indication that we were concerned about irregularities.
+Our first two requests did not include any indication about our concerns regarding the data irregularities.
 Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 1 and provided some more general responses to our concerns; however, elements of their responses were inaccurate relative to the target articles.
+The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns.
+Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles.
 The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
@@
 We illustrate below that the data *and* analyses reported in each of the articles reviewed are unreliable.
-Our extracted data and analysis scripts can be accessed at the following link: **[LINK]**.
+Our extracted data and analysis scripts can be accessed at the following link: https://osf.io/raz6q/.
 
@@
 The largest effect size observed from the one million simulated experiments was *d* = 2.97.
-In the second simulation, we set the true effect size at *d* = 3, an unrealistically large effect size that might rarely be encountered in the psychology literature.
+In the second simulation, we set the true effect size at *d* = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature.
 The maximum effect size observed in the one million simulated experiments was *d* = 6.6.
@@
 All pairwise comparisons have been included for all dependent measures in each experiment.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = .8 is illustrated by light green and dark blue regions of the figure, reaching a maximum value of $d$ = 2.97.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of $d$ = 6.6.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of $d$ = 2.97.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of $d$ = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of $d$ = 6.6.
 
@@
 
-In Article 1, the CSAI-2 was used to assess the level of cognitive and somatic stress experienced by participants.
+In Article 1, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants.
 Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item.
@@
 During the high-stress time point, the means ranged from 3.95 to 4.09.
-The means for two groups were reported as greater than 4, which is not possible given the maximum score on the CSAI-2 is 4.
+The means for two groups were reported as greater than 4, which is not possible given the maximum score on the Competitive State Anxiety Inventory-2 is 4.
 
@@
 Benchmarks have been suggested for small, medium, and large effect sizes as $\eta^{2}$ = .01, .06, and .14, respectively [@cohen1988].
-Importantly, if a main effect of instruction-type results in $\eta^{2}$ = .99, as we will see commonly below, this suggests that 99% of the total variability in the outcome measure can be explained by group assignment alone.
+Importantly, if a main effect of instruction-type results in $\eta^{2}$ = .99, as was commonly reported in the target articles, this suggests that 99% of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
@@
 Lola, personal communication, April 22, 2021).
-Further, the reported test statistics and associated $\eta^{2}$ values are also implausibly large, which is inconsistent with the authors' claim that their results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Considering these findings, it seems the conclusions from these articles are not reliable.
+Further, the reported test statistics and associated $\eta^{2}$ values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
+Considering these findings, the conclusions from these articles are not reliable.
 
 It is noteworthy that the results reported in each of these articles perfectly reflect the authors' expectations.
-Indeed, our attention was drawn to these articles after the @lola2021 paper was shared on Twitter [@gray2021], possibly because the results appeared to be exemplary.
+Indeed, our attention was drawn to these articles after the @lola2021 paper was shared on Twitter [@gray2021]; possibly because the results appeared to be exemplary.
 Although these errors seem unlikely to have aligned with expectations by chance alone, our exposure to them occurred after they had been selected for publication.
@@
 
-\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: **[LINK]**.
+\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: https://osf.io/raz6q/.
 

### 2021-09-11 docs/manuscript/manuscript.tex
update: minor edits

@@
   english,
-  man,floatsintext]{apa7}
+  man, donotrepeattitle,floatsintext]{apa7}
+\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
+\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
+\date{}
+
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 \pagewiselinenumbers
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
-\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
-\date{}
 
@@
 
-We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
+We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
 All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
@@
 The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2).
-In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (CSAI-2) (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 2 had a measure of self-efficacy using a Likert scale.
+In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 2 had a measure of self-efficacy using a Likert scale.
 Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.
@@
 We illustrate below that the data \emph{and} analyses reported in each of the articles reviewed are unreliable.
-Our extracted data and analysis scripts can be accessed at the following link: \textbf{{[}LINK{]}}.
+Our extracted data and analysis scripts can be accessed at the following link: \url{https://osf.io/raz6q/}.
 
@@
 The largest effect size observed from the one million simulated experiments was \emph{d} = 2.97.
-In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology literature.
+In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature.
 The maximum effect size observed in the one million simulated experiments was \emph{d} = 6.6.
@@
 All pairwise comparisons have been included for all dependent measures in each experiment.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by light green and dark blue regions of the figure, reaching a maximum value of \(d\) = 2.97.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of \(d\) = 2.97.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
 \end{figure}
@@
 Benchmarks have been suggested for small, medium, and large effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988).
-Importantly, if a main effect of instruction-type results in \(\eta^{2}\) = .99, as we will see commonly below, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone.
+Importantly, if a main effect of instruction-type results in \(\eta^{2}\) = .99, as was commonly reported in the target articles, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
@@
 
-We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
 Lola, personal communication, April 22, 2021).
-Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that their results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Considering these findings, it seems the conclusions from these articles are not reliable.
+Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
+Considering these findings, the conclusions from these articles are not reliable.
 
 It is noteworthy that the results reported in each of these articles perfectly reflect the authors' expectations.
-Indeed, our attention was drawn to these articles after the Lola and Tzetzis (2021) paper was shared on Twitter (Gray, 2021), possibly because the results appeared to be exemplary.
+Indeed, our attention was drawn to these articles after the Lola and Tzetzis (2021) paper was shared on Twitter (Gray, 2021); possibly because the results appeared to be exemplary.
 Although these errors seem unlikely to have aligned with expectations by chance alone, our exposure to them occurred after they had been selected for publication.
@@
 At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-08-20), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-11), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
 
@@
 
-\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: \textbf{{[}LINK{]}}.
+\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: \url{https://osf.io/raz6q/}.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-anaya2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-anaya2016}{}}%
 Anaya, J. (2016). \emph{The GRIMMER test: A method for testing the validity of reported measures of variability}. \url{https://doi.org/10.7287/peerj.preprints.2400v1}
 
-\leavevmode\hypertarget{ref-R-papaja}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-bakker2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2011}{}}%
 Bakker, M., \& Wicherts, J.
@@
 
-\leavevmode\hypertarget{ref-brown2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-brown2017}{}}%
 Brown, N.
@@
 
-\leavevmode\hypertarget{ref-cohen1962}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cohen1962}{}}%
 Cohen, J.
@@
 
-\leavevmode\hypertarget{ref-cohen1988}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cohen1988}{}}%
 Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). New York: Routledge. \url{https://doi.org/10.4324/9780203771587}
 
-\leavevmode\hypertarget{ref-correll2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-correll2020}{}}%
 Correll, J., Mellinger, C., McClelland, G.
@@
 
-\leavevmode\hypertarget{ref-R-lemon}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-lemon}{}}%
 Edwards, S. M. (2020). \emph{Lemon: Freshing up your 'ggplot2' plots}. Retrieved from \url{https://CRAN.R-project.org/package=lemon}
 
-\leavevmode\hypertarget{ref-field2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-field2016}{}}%
 Field, A. P. (2016). \emph{An adventure in statistics: The reality enigma}.
 
-\leavevmode\hypertarget{ref-fischman2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-fischman2015}{}}%
 Fischman, M.
@@
 
-\leavevmode\hypertarget{ref-R-daff}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-daff}{}}%
 Fitzpatrick, P., de Jonge, E., \& Warnes, G. R. (2019). \emph{Daff: Diff, patch and merge for data.frames}. Retrieved from \url{https://CRAN.R-project.org/package=daff}
 
-\leavevmode\hypertarget{ref-gray2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gray2021}{}}%
 Gray, R.
@@
 
-\leavevmode\hypertarget{ref-hancock1995}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hancock1995}{}}%
 Hancock, G.
@@
 
-\leavevmode\hypertarget{ref-lakens2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2013}{}}%
 Lakens, D.
@@
 
-\leavevmode\hypertarget{ref-lola2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lola2020}{}}%
 Lola, A.
@@
 
-\leavevmode\hypertarget{ref-lola2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lola2021}{}}%
 Lola, A.
@@
 
-\leavevmode\hypertarget{ref-lola2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lola2012}{}}%
 Lola, A.
@@
 
-\leavevmode\hypertarget{ref-lovakov2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lovakov2021}{}}%
 Lovakov, A., \& Agadullina, E.
@@
 
-\leavevmode\hypertarget{ref-munafo2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-munafo2017}{}}%
 Munafò, M.
@@
 
-\leavevmode\hypertarget{ref-R-gridGraphics}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-gridGraphics}{}}%
 Murrell, P., \& Wen, Z. (2020). \emph{gridGraphics: Redraw base graphics using 'grid' graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridGraphics}
 
-\leavevmode\hypertarget{ref-R-lsr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-lsr}{}}%
 Navarro, D.
@@
 
-\leavevmode\hypertarget{ref-R-RColorBrewer}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-RColorBrewer}{}}%
 Neuwirth, E. (2014). \emph{RColorBrewer: ColorBrewer palettes}. Retrieved from \url{https://CRAN.R-project.org/package=RColorBrewer}
 
-\leavevmode\hypertarget{ref-nuijten2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-nuijten2016}{}}%
 Nuijten, M.
@@
 (2016).
-The prevalence of statistical reporting errors in psychology (1985{{}}2013).
+The prevalence of statistical reporting errors in psychology (1985{\textendash}2013).
 \emph{Behavior Research Methods}, \emph{48}(4), 1205--1226.
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-R-compute.es}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-compute.es}{}}%
 Re, A. C. D. (2013). Compute.es: Compute effect sizes. In \emph{R Package}. Retrieved from \url{https://cran.r-project.org/package=compute.es}
 
-\leavevmode\hypertarget{ref-reeve1994}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-reeve1994}{}}%
 Reeve, T.
@@
 
-\leavevmode\hypertarget{ref-thompson2007}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-thompson2007}{}}%
 Thompson, B. (2007). Effect sizes, confidence intervals, and confidence intervals for effect sizes. \emph{Psychology in the Schools}, \emph{44}(5), 423--432. \url{https://doi.org/10.1002/pits.20234}
 
-\leavevmode\hypertarget{ref-tsorbatzoudis1998}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tsorbatzoudis1998}{}}%
 Tsorbatzoudis, H., Barkoukis, V., Kaissidis-Rodafinos, A., \& Grouios, G.
@@
 
-\leavevmode\hypertarget{ref-tzetzis2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tzetzis2010}{}}%
 Tzetzis, G.
@@
 
-\leavevmode\hypertarget{ref-tzetzis2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tzetzis2015}{}}%
 Tzetzis, G.
@@
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
@@
 
-\leavevmode\hypertarget{ref-R-scales}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-scales}{}}%
 Wickham, H., \& Seidel, D. (2020). \emph{Scales: Scale functions for visualization}. Retrieved from \url{https://CRAN.R-project.org/package=scales}
 
-\leavevmode\hypertarget{ref-R-kableExtra}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
 Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}

### 2021-09-11 scripts/sim_script.R
update: rename scripts

@@ -1,81 +1,0 @@
-library(lsr)
-library(cowplot)
-library(ggplot2)
-library(gridGraphics)
-# set seed for reproducible results
-
-set.seed(9293)
-
-# specify number of simulations
-
-iters <- 1000000
-
-
-# save cohens d estimate from each simulation
-
-d <- rep(NA, iters)
-
-# run simulations
-
-for (i in 1:iters) {
-  
-  x1 <- rnorm(20, mean=0, sd=1)
-  x2 <- rnorm(20, mean=0.8, sd=1)
-  res <- cohensD(x1, x2)
-  d[i] <- res
-  
-}
-
-round(max(d), digits = 2)
-
-round(mean(d), digits = 2)
-
-dres <- density(d)
-a <- plot(dres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == .80))+
-polygon(dres, col="blue", border="black")
-
-p1_recorded <- recordPlot(a)
-
-ggdraw(p1_recorded)
-
-#### repeat with true effect of d = 3
-
-
-
-# specify number of simulations
-
-iters <- 1000000
-
-
-# save cohens d estimate from each simulation
-
-dmax <- rep(NA, iters)
-
-# run simulations
-
-for (i in 1:iters) {
-  
-  x1 <- rnorm(20, mean=0, sd=1)
-  x2 <- rnorm(20, mean=3, sd=1)
-  res <- cohensD(x1, x2)
-  dmax[i] <- res
-  
-}
-
-round(max(dmax), digits = 2)
-
-round(mean(dmax), digits = 2)
-
-round(min(dmax), digits = 2)
-
-dmaxres <- density(dmax)
-b <- plot(dmaxres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == 3.0))+
-polygon(dmaxres, col="black", border="black")
-
-p2_recorded <- recordPlot(b)
-
-ggdraw(p2_recorded)
-
-
-
-plot_grid(p1_recorded, p2_recorded, labels = c('A', 'B'), label_size = 12)

### 2021-09-11 scripts/wrangle.R

@@ -1,0 +1,583 @@
+library(compute.es)
+library(daff)
+library(ggplot2)
+library(tidyr)
+library(scales)
+library(RColorBrewer)
+library(lemon)
+
+## read in Brad's extraction for 2012 paper
+
+bac12 <- read.csv("2012/data_Ac.csv")
+brt12 <- read.csv("2012/data_RT.csv")
+
+
+## read in Abbey's extraction for 2012 paper
+
+aac12 <- read.csv("Abbey/data/2012/data_Ac.csv")
+
+art12 <- read.csv("Abbey/data/2012/data_Rt.csv")
+
+#### compare Brad and Abbey's extractions
+
+# accuracy data
+
+dif <- diff_data(bac12, aac12)
+
+render_diff(dif)
+
+##### Brad's extraction contained an error on explicit pre-test mean. Label Abbey's extraction "data_Ac'
+
+data_Ac <- aac12
+
+# response time data
+
+dif2 <- diff_data(brt12, art12)
+
+render_diff(dif2)
+
+##### extractions match. Label Brad's data "data_Rt"
+
+data_RT <- brt12
+
+## 2012 paper accuracy effect size calculations
+
+I_E <- mes(E_m, I_m, E_sd, I_sd, n, n, id = id, data = data_Ac)
+
+I_E <- I_E$d
+
+E_S <- mes(E_m, S_m, E_sd, S_sd, n, n, id = id, data = data_Ac)
+
+E_S <- E_S$d
+
+E_C <- mes(E_m, C_m, E_sd, C_sd, n, n, id = id, data = data_Ac)
+
+E_C <- E_C$d
+
+I_S <- mes(I_m, S_m, I_sd, S_sd, n, n, id = id, data = data_Ac)
+
+I_S <- I_S$d
+
+I_C <- mes(I_m, C_m, I_sd, C_sd, n, n, id = id, data = data_Ac)
+
+I_C <- I_C$d
+
+S_C <- mes(S_m, C_m, S_sd, C_sd, n, n, id = id, data = data_Ac)
+
+S_C <- S_C$d
+
+id <- data_Ac$id
+
+#### create table of accuracy effect sizes for 2012 paper
+
+accuracy_2012 <- cbind(I_E, E_S, E_C, I_S, I_C, S_C, id)
+accuracy_2012 <- as.data.frame(accuracy_2012)
+
+
[…]

### 2021-09-11 scripts/script.R
update: rename scripts

@@ -1,583 +1,0 @@
-library(compute.es)
-library(daff)
-library(ggplot2)
-library(tidyr)
-library(scales)
-library(RColorBrewer)
-library(lemon)
-
-## read in Brad's extraction for 2012 paper
-
-bac12 <- read.csv("2012/data_Ac.csv")
-brt12 <- read.csv("2012/data_RT.csv")
-
-
-## read in Abbey's extraction for 2012 paper
-
-aac12 <- read.csv("Abbey/data/2012/data_Ac.csv")
-
-art12 <- read.csv("Abbey/data/2012/data_Rt.csv")
-
-#### compare Brad and Abbey's extractions
-
-# accuracy data
-
-dif <- diff_data(bac12, aac12)
-
-render_diff(dif)
-
-##### Brad's extraction contained an error on explicit pre-test mean. Label Abbey's extraction "data_Ac'
-
-data_Ac <- aac12
-
-# response time data
-
-dif2 <- diff_data(brt12, art12)
-
-render_diff(dif2)
-
-##### extractions match. Label Brad's data "data_Rt"
-
-data_RT <- brt12
-
-## 2012 paper accuracy effect size calculations
-
-I_E <- mes(E_m, I_m, E_sd, I_sd, n, n, id = id, data = data_Ac)
-
-I_E <- I_E$d
-
-E_S <- mes(E_m, S_m, E_sd, S_sd, n, n, id = id, data = data_Ac)
-
-E_S <- E_S$d
- 
-E_C <- mes(E_m, C_m, E_sd, C_sd, n, n, id = id, data = data_Ac)
-
-E_C <- E_C$d
- 
-I_S <- mes(I_m, S_m, I_sd, S_sd, n, n, id = id, data = data_Ac)
-
-I_S <- I_S$d
-
-I_C <- mes(I_m, C_m, I_sd, C_sd, n, n, id = id, data = data_Ac)
-
-I_C <- I_C$d
- 
-S_C <- mes(S_m, C_m, S_sd, C_sd, n, n, id = id, data = data_Ac)
-
-S_C <- S_C$d
-
-id <- data_Ac$id
-
-#### create table of accuracy effect sizes for 2012 paper
-
-accuracy_2012 <- cbind(I_E, E_S, E_C, I_S, I_C, S_C, id)
-accuracy_2012 <- as.data.frame(accuracy_2012)
-
-
[…]

### 2021-09-11 scripts/simulations.R

@@ -1,0 +1,81 @@
+library(lsr)
+library(cowplot)
+library(ggplot2)
+library(gridGraphics)
+# set seed for reproducible results
+
+set.seed(9293)
+
+# specify number of simulations
+
+iters <- 1000000
+
+
+# save cohens d estimate from each simulation
+
+d <- rep(NA, iters)
+
+# run simulations
+
+for (i in 1:iters) {
+
+  x1 <- rnorm(20, mean=0, sd=1)
+  x2 <- rnorm(20, mean=0.8, sd=1)
+  res <- cohensD(x1, x2)
+  d[i] <- res
+
+}
+
+round(max(d), digits = 2)
+
+round(mean(d), digits = 2)
+
+dres <- density(d)
+a <- plot(dres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == .80))+
+polygon(dres, col="blue", border="black")
+
+p1_recorded <- recordPlot(a)
+
+ggdraw(p1_recorded)
+
+#### repeat with true effect of d = 3
+
+
+
+# specify number of simulations
+
+iters <- 1000000
+
+
+# save cohens d estimate from each simulation
+
+dmax <- rep(NA, iters)
+
+# run simulations
+
+for (i in 1:iters) {
+
+  x1 <- rnorm(20, mean=0, sd=1)
+  x2 <- rnorm(20, mean=3, sd=1)
+  res <- cohensD(x1, x2)
+  dmax[i] <- res
+
+}
+
+round(max(dmax), digits = 2)
+
+round(mean(dmax), digits = 2)
+
+round(min(dmax), digits = 2)
+
+dmaxres <- density(dmax)
+b <- plot(dmaxres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == 3.0))+
+polygon(dmaxres, col="black", border="black")
+
+p2_recorded <- recordPlot(b)
+
+ggdraw(p2_recorded)
+
+
+
+plot_grid(p1_recorded, p2_recorded, labels = c('A', 'B'), label_size = 12)

### 2021-09-11 docs/manuscript/manuscript.tex
update: rearrange articles by year in title to match numbering in body

@@
   man, donotrepeattitle,floatsintext]{apa7}
-\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
+\title{Data irregularities across five implicit learning articles: Comments on Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
 \author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
@@
 \hypersetup{
-  pdftitle={Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)},
+  pdftitle={Data irregularities across five implicit learning articles: Comments on Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
   pdfauthor={Brad McKay1 \& Michael J. Carter1},

### 2021-09-12 scripts/wrangle.R
rm: single, really long script

@@ -1,583 +1,0 @@
-library(compute.es)
-library(daff)
-library(ggplot2)
-library(tidyr)
-library(scales)
-library(RColorBrewer)
-library(lemon)
-
-## read in Brad's extraction for 2012 paper
-
-bac12 <- read.csv("2012/data_Ac.csv")
-brt12 <- read.csv("2012/data_RT.csv")
-
-
-## read in Abbey's extraction for 2012 paper
-
-aac12 <- read.csv("Abbey/data/2012/data_Ac.csv")
-
-art12 <- read.csv("Abbey/data/2012/data_Rt.csv")
-
-#### compare Brad and Abbey's extractions
-
-# accuracy data
-
-dif <- diff_data(bac12, aac12)
-
-render_diff(dif)
-
-##### Brad's extraction contained an error on explicit pre-test mean. Label Abbey's extraction "data_Ac'
-
-data_Ac <- aac12
-
-# response time data
-
-dif2 <- diff_data(brt12, art12)
-
-render_diff(dif2)
-
-##### extractions match. Label Brad's data "data_Rt"
-
-data_RT <- brt12
-
-## 2012 paper accuracy effect size calculations
-
-I_E <- mes(E_m, I_m, E_sd, I_sd, n, n, id = id, data = data_Ac)
-
-I_E <- I_E$d
-
-E_S <- mes(E_m, S_m, E_sd, S_sd, n, n, id = id, data = data_Ac)
-
-E_S <- E_S$d
-
-E_C <- mes(E_m, C_m, E_sd, C_sd, n, n, id = id, data = data_Ac)
-
-E_C <- E_C$d
-
-I_S <- mes(I_m, S_m, I_sd, S_sd, n, n, id = id, data = data_Ac)
-
-I_S <- I_S$d
-
-I_C <- mes(I_m, C_m, I_sd, C_sd, n, n, id = id, data = data_Ac)
-
-I_C <- I_C$d
-
-S_C <- mes(S_m, C_m, S_sd, C_sd, n, n, id = id, data = data_Ac)
-
-S_C <- S_C$d
-
-id <- data_Ac$id
-
-#### create table of accuracy effect sizes for 2012 paper
-
-accuracy_2012 <- cbind(I_E, E_S, E_C, I_S, I_C, S_C, id)
-accuracy_2012 <- as.data.frame(accuracy_2012)
-
-
[…]

### 2021-09-13 scripts/simulations.R
rm: script directory

@@ -1,81 +1,0 @@
-library(lsr)
-library(cowplot)
-library(ggplot2)
-library(gridGraphics)
-# set seed for reproducible results
-
-set.seed(9293)
-
-# specify number of simulations
-
-iters <- 1000000
-
-
-# save cohens d estimate from each simulation
-
-d <- rep(NA, iters)
-
-# run simulations
-
-for (i in 1:iters) {
-
-  x1 <- rnorm(20, mean=0, sd=1)
-  x2 <- rnorm(20, mean=0.8, sd=1)
-  res <- cohensD(x1, x2)
-  d[i] <- res
-
-}
-
-round(max(d), digits = 2)
-
-round(mean(d), digits = 2)
-
-dres <- density(d)
-a <- plot(dres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == .80))+
-polygon(dres, col="blue", border="black")
-
-p1_recorded <- recordPlot(a)
-
-ggdraw(p1_recorded)
-
-#### repeat with true effect of d = 3
-
-
-
-# specify number of simulations
-
-iters <- 1000000
-
-
-# save cohens d estimate from each simulation
-
-dmax <- rep(NA, iters)
-
-# run simulations
-
-for (i in 1:iters) {
-
-  x1 <- rnorm(20, mean=0, sd=1)
-  x2 <- rnorm(20, mean=3, sd=1)
-  res <- cohensD(x1, x2)
-  dmax[i] <- res
-
-}
-
-round(max(dmax), digits = 2)
-
-round(mean(dmax), digits = 2)
-
-round(min(dmax), digits = 2)
-
-dmaxres <- density(dmax)
-b <- plot(dmaxres,xlab = expression("Cohen's "*italic(d)), bty = "n", main= expression(italic('d') == 3.0))+
-polygon(dmaxres, col="black", border="black")
-
-p2_recorded <- recordPlot(b)
-
-ggdraw(p2_recorded)
-
-
-
-plot_grid(p1_recorded, p2_recorded, labels = c('A', 'B'), label_size = 12)

### 2021-09-13 scripts/wrangle_2012.R
init

@@ -1,0 +1,114 @@
+# Data wrangling for Lola et al 2012
+#
+# Lola, A.C., & Tzetzis, G.C., & Zetou, H. (2012). The effect of implicit and
+# explicit practice in the development of decision making in volleyball
+# serving. Perceptual and Motor Skills, 114(2), 665-678.
+# https://doi.org/10.2466/05.23.25.PMS.114.2.665-678
+#
+# Created by Brad McKay
+# Cleaned by Mike Carter
+
+# SCRIPT SETUP ---------------
+#
+# Required libraries
+library(compute.es)
+library(daff)
+library(tidyverse)
+
+# Load data files
+#
+# Brad's extraction for accuracy and response time data
+bm_2012_accuracy <- readr::read_csv("data/brad/2012/data_ac.csv")
+bm_2012_rt <- readr::read_csv("data/brad/2012/data_rt.csv")
+
+# Abbey's extraction for accuracy and response time data
+ac_2012_accuracy <- readr::read_csv("data/abbey/2012/data_ac.csv")
+ac_2012_rt <- readr::read_csv("data/abbey/2012/data_rt.csv")
+
+
+# EXTRACTION COMPARISONS ---------------
+#
+# Compare Brad's and Abbey's extractions for accuracy data
+accuracy_diff <- daff::diff_data(bm_2012_accuracy, ac_2012_accuracy)
+daff::render_diff(accuracy_diff)
+
+#>>> Outcome of diff: Brad's extraction contained an error on explicit
+#>>> pre-test mean.
+
+# Use Abbey's extraction for the main accuracy variable
+main_2012_accuracy <- ac_2012_accuracy
+
+# Compare Brad's and Abbey's extractions for response time data
+rt_diff <- daff::diff_data(bm_2012_rt, ac_2012_rt)
+daff::render_diff(rt_diff)
+
+#>>> Outcome of diff: Extractions match
+
+# Use Brad's extraction for the main response time variable
+main_2012_rt <- bm_2012_rt
+
+
+# EFFECT SIZE CALCULATIONS ---------------
+#
+# Accuracy data
+I_E <- compute.es::mes(E_m, I_m, E_sd, I_sd, n, n,
+                       id = id, data = main_2012_accuracy)
+I_E <- I_E$d
+
[…]

### 2021-09-13 scripts/wrangle_2015.R

@@ -1,0 +1,114 @@
+# Data wrangling for Tzetzis & Lola 2015
+#
+# Tzetzis, G.C., & Lola, A.C. (2015). The effect of analogy, implicit, and
+# explicit learning on anticipation in volleyball serving. International
+# Journal of Sport Psychology, 46(2), 152-166.
+# https://doi.org/10.7352/IJSP.2015.46.152
+#
+# Created by Brad McKay
+# Cleaned by Mike Carter
+
+# SCRIPT SETUP ---------------
+#
+# Required libraries
+library(compute.es)
+library(daff)
+library(tidyverse)
+
+# Load data files
+#
+# Brad's extraction for accuracy and response time data
+bm_2015_accuracy <- readr::read_csv("data/brad/2015/data_ac.csv")
+bm_2015_rt <- readr::read_csv("data/brad/2015/data_rt.csv")
+
+# Abbey's extraction for accuracy and response time data
+ac_2015_accuracy <- readr::read_csv("data/abbey/2015/data_ac.csv")
+ac_2015_rt <- readr::read_csv("data/abbey/2015/data_rt.csv")
+
+
+# EXTRACTION COMPARISONS ---------------
+#
+# Compare Brad's and Abbey's extractions for accuracy data
+accuracy_diff <- daff::diff_data(bm_2015_accuracy, ac_2015_accuracy)
+daff::render_diff(accuracy_diff)
+
+#>>> Outcome of diff: Extractions match
+
+# Use Brad's extraction for the main response time variable
+main_2015_accuracy <- bm_2015_accuracy
+
+# Compare Brad's and Abbey's extractions for response time data
+rt_diff <- daff::diff_data(bm_2015_rt, ac_2015_rt)
+daff::render_diff(rt_diff)
+
+#>>> Outcome of diff: Abbey's extraction contained an error on explicit mean
+#>>> at post test.
+
+# Use Brad's extraction for the main response time variable
+main_2015_rt <- bm_2015_rt
+
+
+# EFFECT SIZE CALCULATIONS ---------------
+#
+# Accuracy data
+A_I <- compute.es::mes(I_m, A_m, I_sd, A_sd, n, n,
+                       id = id, data = main_2015_accuracy)
+A_I <- A_I$d
+
[…]

### 2021-09-13 scripts/wrangle_2021.R

@@ -1,0 +1,201 @@
+# Data wrangling for Lola & Tzetzis 2021
+#
+# Lola, A.C., & Tzetzis, G.C. (2021). The effect of explicit, implicit and
+# analogy instruction on decision making skill for novices, under stress.
+# International Journal of Sport and Exercise Psychology, 1-21.
+# https://doi.org/10.1080/1612197X.2021.1877325
+#
+# Created by Brad McKay
+# Cleaned by Mike Carter
+
+# SCRIPT SETUP ---------------
+#
+# Required libraries
+library(compute.es)
+library(daff)
+library(tidyverse)
+
+# Load data files
+#
+# Brad's extraction for perceptual accuracy, anxiety, motor accuracy,
+# and reaction time
+bm_2021_perceptual <- readr::read_csv("data/brad/2021/data_ac.csv")
+bm_2021_anxiety <- readr::read_csv("data/brad/2021/data_csai.csv")
+bm_2021_motor <- readr::read_csv("data/brad/2021/data_mac.csv")
+bm_2021_rt <- readr::read_csv("data/brad/2021/data_rt.csv")
+
+# Abbey's extraction for perceptual accuracy, anxiety, motor accuracy,
+# and response time
+ac_2021_perceptual <- readr::read_csv("data/abbey/2021/data_ac.csv")
+ac_2021_anxiety <- readr::read_csv("data/abbey/2021/data_csai.csv")
+ac_2021_motor <- readr::read_csv("data/abbey/2021/data_mac.csv")
+ac_2021_rt <- readr::read_csv("data/abbey/2021/data_rt.csv")
+
+
+# EXTRACTION COMPARISONS ---------------
+#
+# Compare Brad's and Abbey's extractions for perceptual accuracy data
+perceptual_diff <- daff::diff_data(bm_2021_perceptual, ac_2021_perceptual)
+daff::render_diff(perceptual_diff)
+
+#>>> Outcome of diff: Brad's extraction contained an error on explicit stress
+#>>> test mean.
+
+# Use Abbey's extraction for the main perceptual accuracy variable
+main_2021_perceptual <- ac_2021_perceptual
+
+# Compare Brad's and Abbey's extractions for anxiety data
+anxiety_diff <- daff::diff_data(bm_2021_anxiety, ac_2021_anxiety)
[…]

### 2021-09-13 scripts/wrangle_2020.R
init

@@ -1,0 +1,114 @@
+# Data wrangling for Lola & Tzetzis 2020
+#
+# Lola, A.C., & Tzetzis, G.C. (2020). Analogy versus explicit and implicit
+# learning of a volleyball skill for novices: The effect on motor performance
+# and self-efficacy. Journal of Physical Education and Sport, 20(5), 2478-2486.
+# https://doi.org/10.7752/jpes.2020.05339
+#
+# Created by Brad McKay
+# Cleaned by Mike Carter
+
+# SCRIPT SETUP ---------------
+#
+# Required libraries
+library(compute.es)
+library(daff)
+library(tidyverse)
+
+# Load data files
+#
+# Brad's extraction for motor performance and self-efficacy
+bm_2020_performance <- readr::read_csv("data/brad/2020/data_mp.csv")
+bm_2020_selfefficacy <- readr::read_csv("data/brad/2020/data_se.csv")
+
+# Abbey's extraction for motor performance and self-efficacy
+ac_2020_performance <- readr::read_csv("data/abbey/2020/data_mp.csv")
+ac_2020_selfefficacy <- readr::read_csv("data/abbey/2020/data_se.csv")
+
+
+# EXTRACTION COMPARISONS ---------------
+#
+# Compare Brad's and Abbey's extractions for performance data
+performance_diff <- daff::diff_data(bm_2020_performance, ac_2020_performance)
+daff::render_diff(performance_diff)
+
+#>>> Outcome of diff: Extractions match
+
+# Use Brad's extraction for the main motor performance variable
+main_2020_performance <- bm_2020_performance
+
+# Compare Brad's and Abbey's extractions for self-efficacy data
+selfefficacy_diff <- daff::diff_data(bm_2020_selfefficacy,
+                                     ac_2020_selfefficacy)
+daff::render_diff(selfefficacy_diff)
+
+#>>> Outcome of diff: Extractions match
+
+# Use Brad's extraction for the main motor performance variable
+main_2020_selfefficacy <- bm_2020_selfefficacy
+
+
+# EFFECT SIZE CALCULATIONS ---------------
+#
+# Motor performance data
+E_A <- compute.es::mes(E_m, A_m, E_sd, A_sd, n, n,
+                       id = id, data = main_2020_performance)
[…]

### 2021-09-24 docs/updated_manuscript/updated_manuscript.Rmd
updated version of preprint with sixth article

--- 2021-09-11 docs/manuscript/manuscript.Rmd
@@
 ---
-title             : "Data irregularities across five implicit learning articles: Comments on @lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015"
+title             : "Data irregularities across six implicit learning articles: Comments on @lola2021, @lola2021b, @lola2020, @tzetzis2015, @lola2012, and @tzetzis2010"
 
@@
 abstract: |
-  We present a critical re-analysis of five implicit learning papers published by the same authors between 2010 and 2021.
+  We present a critical re-analysis of six implicit learning papers published by the same authors between 2010 and 2021.
 We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article.
 We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations.
-We found the pairwise effect sizes were implausible in all five articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000.
-Impossible statistics were reported in four out of the five articles.
+We found the pairwise effect sizes were implausible in all six articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000.
+Impossible statistics were reported in four out of the six articles.
 Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects.
-The results reported in the five articles in question are unreliable.
+The results reported in the six articles in question are unreliable.
 Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.
@@
 When the primary conclusions in research articles depend on reporting errors, replicability is unlikely and future research may be wasted if researchers attempt to build on the erroneously reported results [@munafo2017].
-In this paper, we scrutinize five papers published by the same two authors[^1], where the authors report a high number of erroneous or implausible data on which their primary conclusions depend.
+In this paper, we scrutinize six papers published by the same two authors[^1], where the authors report a high number of erroneous or implausible data on which their primary conclusions depend.
 We first became aware of the @lola2021 paper when the paper was highlighted in a social media post [@gray2021].
@@
 Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., $F$-statistics) across multiple papers.
-Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions.
-Below, we outline our causes for concern and the overarching issues we found across the five articles in question.
+Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions[^2].
+Below, we outline our causes for concern and the overarching issues we found across the six articles in question.
 
-[^1]: One of the five papers had a third author.
+[^1]: One of the six papers had a third author and one had a third and fourth author.
+[^2]: After sharing a preprint of the original version of this paper, the editors of the *International Journal of Sport and Exercise Psychology* have indicated they intend to retract @lola2021.
 
@@
 
-We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague [@lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015].
-All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)).
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague [@lola2012; @lola2020; @lola2021; @lola2021b; @tzetzis2010; @tzetzis2015].
+All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)).
 In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills.
 Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-We will refer to the five articles throughout this paper using the following numbering system:
+We will refer to the six articles throughout this paper using the following numbering system:
 
@@
 2.
+Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+*Journal of Human Sport and Exercise, in press*.
+https://doi.org/10.14198/jhse.2023.181.12
+
+3.
 Lola, A.C., & Tzetzis, G.C.
@@
 
-3.
+4.
 Tzetzis, G.C., & Lola, A.C.
@@
 
-4.
+5.
 Lola, A.C., & Tzetzis, G.C., & Zetou, H.
@@
 
-5.
+6.
 Tzetzis, G.C., & Lola, C.A.
@@
 The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions.
-*International Journal of Sport Sciences and Physical Education*, 1, 54-59.[^2]
+*International Journal of Sport Sciences and Physical Education*, 1, 54-59.[^3]
 
-[^2]: This article is in a journal of a publishing group that has been identified as a potential predatory journal.
+[^3]: This article is in a journal of a publishing group that has been identified as a potential predatory journal.
 Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS).
@@
   c1 = c("Lola \\& Tzetzis (2021)",
+         "Lola et al (2021)",
          "Lola \\& Tzetzis (2020)",
@@
   c2 = c("60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
+         "60 females, age range: 11 to 12 years (mean and standard deviation not reported)",
          "80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
@@
   pack_rows("Article 5", 5, 5) %>%
-  footnote(alphabet = c("Articles 1-3 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2."),
+  pack_rows("Article 6", 6, 6) %>%
+  footnote(alphabet = c("Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2."),
            alphabet_title = "Note.",
@@
 Although there were some differences between the reported experiments in the target articles, there were many methodological commonalities that can be summarized.
-All five articles involved female children learning a volleyball skill as part of a volleyball camp.
+All six articles involved female children learning a volleyball skill as part of a volleyball camp.
 In each case, the participants were reported to have minimal experience (i.e., were described as novices) with the task at hand.
-The purpose of all five experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice.
+The purpose of all six experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice.
 Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test.
-The authors also included a high stress test in Articles 1 and 5.
+The authors also included a high stress test in Articles 1, 2 and 6.
 
-In Articles 1-3, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy.
-In Articles 4 and 5, a sequential group (see below for description) replaced the analogy group.
-All five experiments also included a control group that did not practice the task.
+In Articles 1-4, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy.
+In Articles 5 and 6, a sequential group (see below for description) replaced the analogy group.
+All six experiments also included a control group that did not practice the task.
 Implicit instruction did not contain any explicit information for how to perform the task and the learners were asked to perform a distracting task like counting backwards while practicing to prevent them from acquiring declarative rules for performance.
@@
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2).
-In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 2 had a measure of self-efficacy using a Likert scale.
-Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
+In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 3 had a measure of self-efficacy using a Likert scale.
+Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
 
@@
 
-None of the five articles in question included a link to a public repository where the data could be accessed.
+None of the six articles in question included a link to a public repository where the data could be accessed.
 We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
@@
 Lola, personal communication, February 12 2021).
-We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2-5 as these articles were less recent and presumably, all planned analyses had been completed.
-After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2-5.
+We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent and presumably, all planned analyses had been completed.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article (except @lola2021b, which was not published yet) and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
@@
 Cohen's *d* was calculated for each pairwise comparison using the `compute.es` package in `R`.
-To provide context, we simulated data from two groups of *n* = 20, consistent with groups sizes in Articles 1-4.
+To provide context, we simulated data from two groups of *n* = 20, consistent with group sizes in Article 3, which had the largest groups among the target articles.
 We ran simulations with true effect sizes of *d* = .8 and *d* = 3 one million times each and report the range of effect sizes observed in those simulations.
@@
 
-To evaluate the maximum range of plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
+To evaluate the maximum range of plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
 We set the true effect size at *d* = .8, the conventional benchmark for a "large" treatment effect, in the first simulation.
@@
 
-(ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-4 plotted on a logarithmic scale.
+(ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-5 plotted on a logarithmic scale.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 
-In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes.
+In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
 In Article 1, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
@@
 
-In Article 2, post-intervention motor performance effect sizes ranged from *d* = 3.1 to *d* = 20.95.
+In Article 2, the smallest post-intervention difference in reaction times was *d* = .64.
+However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.0.
+The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger *d* = 5.0 and a largest effect of *d* = 13.35.
+
+In Article 3, post-intervention motor performance effect sizes ranged from *d* = 3.1 to *d* = 20.95.
 Similarly, post-intervention self-efficacy effect sizes ranged from *d* = 1.79 to *d* = 44.46.
-Likewise, in Article 3 post-intervention reaction time effect sizes ranged from *d* = 2.28 to *d* = 35.97.
+Likewise, in Article 4 post-intervention reaction time effect sizes ranged from *d* = 2.28 to *d* = 35.97.
 Continuing this pattern, post-intervention response accuracy effect sizes ranged from *d* = 5.84 to *d* = 29.7.
 
-In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from *d* = 2.53 to *d* = 15.50.
+In Article 5, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from *d* = 2.53 to *d* = 15.50.
 Nevertheless, all pre-test comparisons were reported as non-significant.
@@
 
-In Article 5, the authors did not report means and standard deviations for most of the analyses.
+In Article 6, the authors did not report means and standard deviations for most of the analyses.
 However, $\eta^{2}$ effect sizes were reported and these ranged from $\eta^{2}$ = .52 to $\eta^{2}$ = .98.
@@
 
-In Article 2, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
-Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^3] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
+In Article 3, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
+Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^4] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
 The perfect score was not a rounding error because the same group was reported to have a mean score of 2.99 with a standard deviation of .11 on the post-test.
@@
 
-[^3]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [see @fischman2015; @hancock1995; @reeve1994 for discussions].
+[^4]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [see @fischman2015; @hancock1995; @reeve1994 for discussions].
 
-Articles 1, 4, and 5 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
 In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78).
+In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78).
 The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
-In Article 5, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
+In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
 For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^4]
+However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^5]
 
-[^4]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
+[^5]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
 This is because of sample size differences (*n* = 20 for the consistent result and *n* = 12 for the inconsistent one).
@@
 Article 1 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question.
-Article 2 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
+Article 3 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
 Similarly, variance explained on the self-efficacy measure was $\eta^{2}$ = .995, $\eta^{2}$ = .994, $\eta^{2}$ = .997 for the Time, Group, and Time x Group effects, respectively.
-Article 3 also reported $\eta^{2}$ = .99 for all three effects on both response time and response accuracy measures.
+Article 4 also reported $\eta^{2}$ = .99 for all three effects on both response time and response accuracy measures.
 
-Article 4 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure.
+Article 5 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure.
 Interestingly, the Time x Group interaction had the smallest reported significant *F*-statistic among the five articles in question.
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5.
-The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
+The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
+Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \@ref(tab:table1)).
@@
 
+Article 2 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online 11 days before we posted the first preprint of this paper (published September 3rd, 2021; preprint posted September 14th, 2021).
+We were unaware of Article 2 when posting the original preprint and it was not included in that version.
+However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Further, in comparing the reaction time and accuracy means and standard deviations reported in @lola2021b to those reported in @lola2021, it appeared the data shared a remarkably similar pattern.
+To investigate this similarity further, we conducted a correlation analysis between the two data sets.
+To do so, we created a vector of data for each article: Row 1 contained the pretest reaction time mean for the analogy group, row 2 the pretest reaction time standard deviation for the analogy group, and so on listing the means and standard deviations for the four groups and four time points on the two measures.
+Our analysis revealed the two data sets were highly correlated, *r* = .994.
+
 # Discussion
 
-We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning [@lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015].
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning [@lola2012; @lola2020; @lola2021;@lola2021b; @tzetzis2010; @tzetzis2015].
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated $\eta^{2}$ values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
+Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations [@lola2021; @lola2021b].
 Considering these findings, the conclusions from these articles are not reliable.
@@
 These errors were pervasive and appear to have substantially affected the conclusions of the articles in question.
-At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do[^5], many in the research community may find it difficult to trust any of these results.
+At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
+Even if the authors offer corrections, which they have suggested they intend to do[^6], many in the research community may find it difficult to trust any of these results.
 
-[^5]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions have been taken by the authors.
+## Comments on Article 2
+
+The data published in Article 2 are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors have published an additional article with data that are not only implausible, but highly correlated with data in a previous article (*r* = .994).
+We cannot think of a benign explanation for this sequence of events.
+
+[^6]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions have been taken by the authors.
 

### 2021-09-24 docs/updated_manuscript/updated_manuscript.tex
updated version of preprint with sixth article

--- 2021-08-22 docs/manuscript/manuscript.tex
@@
   english,
-  man,floatsintext]{apa7}
+  man, donotrepeattitle,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)},
+  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
   pdfauthor={Brad McKay1 \& Michael J. Carter1},
@@
 
-\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
+\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
 \author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
@@
 \abstract{
-We present a critical re-analysis of five implicit learning papers published by the same authors between 2010 and 2021.
+We present a critical re-analysis of six implicit learning papers published by the same authors between 2010 and 2021.
 We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article.
 We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations.
-We found the pairwise effect sizes were implausible in all five articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000.
-Impossible statistics were reported in four out of the five articles.
+We found the pairwise effect sizes were implausible in all six articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000.
+Impossible statistics were reported in four out of the six articles.
 Reported test statistics and \(\eta^{2}\) values were also implausible, with several \(\eta^{2}\) = .99 and even \(\eta^{2}\) = 1.0 for between-subjects main effects.
-The results reported in the five articles in question are unreliable.
+The results reported in the six articles in question are unreliable.
 Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.
@@
 When the primary conclusions in research articles depend on reporting errors, replicability is unlikely and future research may be wasted if researchers attempt to build on the erroneously reported results (Munafò et al., 2017).
-In this paper, we scrutinize five papers published by the same two authors\footnote{One of the five papers had a third author.}, where the authors report a high number of erroneous or implausible data on which their primary conclusions depend.
+In this paper, we scrutinize six papers published by the same two authors\footnote{One of the six papers had a third author and one had a third and fourth author.}, where the authors report a high number of erroneous or implausible data on which their primary conclusions depend.
 We first became aware of the Lola and Tzetzis (2021) paper when the paper was highlighted in a social media post (Gray, 2021).
@@
 Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., \(F\)-statistics) across multiple papers.
-Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions.
-Below, we outline our causes for concern and the overarching issues we found across the five articles in question.
+Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions\footnote{After sharing a preprint of the original version of this paper, the editors of the \emph{International Journal of Sport and Exercise Psychology} have indicated they intend to retract Lola and Tzetzis (2021).}.
+Below, we outline our causes for concern and the overarching issues we found across the six articles in question.
 
@@
 
-We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
-All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
+All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
 In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills.
 Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-The five articles will be referred to throughout this paper using the following numbering system:
+We will refer to the six articles throughout this paper using the following numbering system:
 
@@
 \url{https://doi.org/10.1080/1612197X.2021.1877325}
+\item
+  Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., \& Tzetzis, G.C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+\emph{Journal of Human Sport and Exercise, in press}.
+\url{https://doi.org/10.14198/jhse.2023.181.12}
 \item
@@
 \multicolumn{2}{l}{\textbf{Article 2}}\\
+\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years (mean and standard deviation not reported)\\
+\addlinespace[0.3em]
+\multicolumn{2}{l}{\textbf{Article 3}}\\
 \hspace{1em}Lola \& Tzetzis (2020) & 80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
 \addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 3}}\\
+\multicolumn{2}{l}{\textbf{Article 4}}\\
 \hspace{1em}Tzetzis \& Lola (2015) & 60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\textsuperscript{a}\\
 \addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 4}}\\
+\multicolumn{2}{l}{\textbf{Article 5}}\\
 \hspace{1em}Lola et al (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
 \addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 5}}\\
+\multicolumn{2}{l}{\textbf{Article 6}}\\
 \hspace{1em}Tzetzis \& Lola (2010) & 48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)\\
@@
 \item \textit{Note.} 
-\item[a] Articles 1-3 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2.
+\item[a] Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2.
 \end{tablenotes}
@@
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2).
-In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (CSAI-2) (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 2 had a measure of self-efficacy using a Likert scale.
-Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
+In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale.
+Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
 
@@
 Lola, personal communication, February 12 2021).
-We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2 through 5 as these articles were less recent and presumably, all planned analyses had been completed.
-After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5.
+We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent and presumably, all planned analyses had been completed.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 
-Our first two requests did not include any indication that we were concerned about irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles.
+Our first two requests did not include any indication about our concerns regarding the data irregularities.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article (except Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), which was not published yet) and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 1 and provided some more general responses to our concerns; however, elements of their responses were inaccurate relative to the target articles.
+The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns.
+Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles.
 The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
@@
 Cohen's \emph{d} was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}.
-To provide context, we simulated data from two groups of \emph{n} = 20, consistent with groups sizes in Articles 1-4.
+To provide context, we simulated data from two groups of \emph{n} = 20, consistent with group sizes in Article 3, which had the largest groups among the target articles.
 We ran simulations with true effect sizes of \emph{d} = .8 and \emph{d} = 3 one million times each and report the range of effect sizes observed in those simulations.
@@
 
-To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
+To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
 We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation.
 The largest effect size observed from the one million simulated experiments was \emph{d} = 2.97.
-In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology literature.
+In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature.
 The maximum effect size observed in the one million simulated experiments was \emph{d} = 6.6.
@@
 
-\caption{Absolute Cohen's \(d\) estimates from Articles 1-4 plotted on a logarithmic scale.
+\caption{Absolute Cohen's \(d\) estimates from Articles 1-5 plotted on a logarithmic scale.
 All pairwise comparisons have been included for all dependent measures in each experiment.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by light green and dark blue regions of the figure, reaching a maximum value of \(d\) = 2.97.
-The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of \(d\) = 2.97.
+The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
 \end{figure}
 
-In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes.
+In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
 In Article 1, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
@@
 
-In Article 2, post-intervention motor performance effect sizes ranged from \emph{d} = 3.1 to \emph{d} = 20.95.
+In Article 2, the smallest post-intervention difference in reaction times was \emph{d} = .64.
+However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.0.
+The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger \emph{d} = 5.0 and a largest effect of \emph{d} = 13.35.
+
+In Article 3, post-intervention motor performance effect sizes ranged from \emph{d} = 3.1 to \emph{d} = 20.95.
 Similarly, post-intervention self-efficacy effect sizes ranged from \emph{d} = 1.79 to \emph{d} = 44.46.
-Likewise, in Article 3 post-intervention reaction time effect sizes ranged from \emph{d} = 2.28 to \emph{d} = 35.97.
+Likewise, in Article 4 post-intervention reaction time effect sizes ranged from \emph{d} = 2.28 to \emph{d} = 35.97.
 Continuing this pattern, post-intervention response accuracy effect sizes ranged from \emph{d} = 5.84 to \emph{d} = 29.7.
 
-In Article 4, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from \emph{d} = 2.53 to \emph{d} = 15.50.
+In Article 5, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from \emph{d} = 2.53 to \emph{d} = 15.50.
 Nevertheless, all pre-test comparisons were reported as non-significant.
@@
 
-In Article 5, the authors did not report means and standard deviations for most of the analyses.
+In Article 6, the authors did not report means and standard deviations for most of the analyses.
 However, \(\eta^{2}\) effect sizes were reported and these ranged from \(\eta^{2}\) = .52 to \(\eta^{2}\) = .98.
@@
 During the high-stress time point, the means ranged from 3.95 to 4.09.
-The means for two groups were reported as greater than 4, which is not possible given the maximum score on the CSAI-2 is 4.
+The means for two groups were reported as greater than 4, which is not possible given the maximum score on the Competitive State Anxiety Inventory-2 is 4.
 
-In Article 2, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
+In Article 3, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
 Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.\footnote{Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task (see Fischman, 2015; Hancock, Butler, \& Fischman, 1995; Reeve, Fischman, Christina, \& Cauraugh, 1994 for discussions).} Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
@@
 
-Articles 1, 4, and 5 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
 In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 4, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78).
+In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78).
 The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
-In Article 5, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
+In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
 For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
@@
 Article 1 did not report \(\eta^{2}\) values but had the largest pairwise effects and \emph{F}-statistics of the five articles in question.
-Article 2 reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
+Article 3 reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
 Similarly, variance explained on the self-efficacy measure was \(\eta^{2}\) = .995, \(\eta^{2}\) = .994, \(\eta^{2}\) = .997 for the Time, Group, and Time x Group effects, respectively.
-Article 3 also reported \(\eta^{2}\) = .99 for all three effects on both response time and response accuracy measures.
+Article 4 also reported \(\eta^{2}\) = .99 for all three effects on both response time and response accuracy measures.
 
-Article 4 reported \(\eta^{2}\) = 1.0 for the main effect of Time and the Time x Group interaction, as well as \(\eta^{2}\) = .95 for the main effect of Group on the response time measure.
+Article 5 reported \(\eta^{2}\) = 1.0 for the main effect of Time and the Time x Group interaction, as well as \(\eta^{2}\) = .95 for the main effect of Group on the response time measure.
 Interestingly, the Time x Group interaction had the smallest reported significant \emph{F}-statistic among the five articles in question.
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5.
-The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
+The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
+Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \ref{tab:table1}).
 We assumed that each article was based on different samples as none of the articles mentioned using any previously published data.
+
+Article 2 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online 11 days before we posted the first preprint of this paper (published September 3rd, 2021; preprint posted September 14th, 2021).
+We were unaware of Article 2 when posting the original preprint and it was not included in that version.
+However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Further, in comparing the reaction time and accuracy means and standard deviations reported in Lola, Giatis, Pérez-Turpin, and Tzetzis (2021) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
+To investigate this similarity further, we conducted a correlation analysis between the two data sets.
+To do so, we created a vector of data for each article: Row 1 contained the pretest reaction time mean for the analogy group, row 2 the pretest reaction time standard deviation for the analogy group, and so on listing the means and standard deviations for the four groups and four time points on the two measures.
+Our analysis revealed the two data sets were highly correlated, \emph{r} = .994.
 
@@
 
-We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
 Lola, personal communication, April 22, 2021).
-Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that their results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Considering these findings, it seems the conclusions from these articles are not reliable.
+Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
+Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2021).
+Considering these findings, the conclusions from these articles are not reliable.
 
 It is noteworthy that the results reported in each of these articles perfectly reflect the authors' expectations.
-Indeed, our attention was drawn to these articles after the Lola and Tzetzis (2021) paper was shared on Twitter (Gray, 2021), possibly because the results appeared to be exemplary.
+Indeed, our attention was drawn to these articles after the Lola and Tzetzis (2021) paper was shared on Twitter (Gray, 2021); possibly because the results appeared to be exemplary.
 Although these errors seem unlikely to have aligned with expectations by chance alone, our exposure to them occurred after they had been selected for publication.
@@
 These errors were pervasive and appear to have substantially affected the conclusions of the articles in question.
-At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-08-20), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
+Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-23), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+
+\hypertarget{comments-on-article-2}{%
+\subsection{Comments on Article 2}\label{comments-on-article-2}}
+
+The data published in Article 2 are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors have published an additional article with data that are not only implausible, but highly correlated with data in a previous article (\emph{r} = .994).
+We cannot think of a benign explanation for this sequence of events.
 
@@
 
-R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
+R (Version 4.0.4; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Version 0.5.1; Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Version 0.5; Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019).
 
@@
 \url{https://doi.org/10.3389/fpsyg.2013.00863}
+
+\leavevmode\hypertarget{ref-lola2021b}{}%
+Lola, A.
+C., Giatis, G., Pérez-Turpin, J.
+A., \& Tzetzis, G.
+C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+\emph{Journal of Human Sport and Exercise}, \emph{in press}(0), 1--14.
+\url{https://doi.org/10.14198/jhse.2023.181.12}
 

### 2021-09-24 scripts/main.R
updated version of preprint with sixth article

@@ -16,11 +16,14 @@ source("scripts/wrangle_2012.R")
 source("scripts/wrangle_2015.R")
 source("scripts/wrangle_2020.R")
 source("scripts/wrangle_2021.R")
+source("scripts/wrangle_2021b.R")
 
 # DATA WRANGLING ---------------
 #
 # Combine all effect sizes across experiments
-all_effects <- plyr::rbind.fill(perceptual_2021,
+all_effects <- plyr::rbind.fill(perceptual_2021b,
+                                rt_2021b,
+                                perceptual_2021,
                                 anxiety_2021,
                                 motor_2021,
                                 rt_2021,
@@ -37,6 +40,29 @@ all_long <- all_effects %>%
 
 # Make all d vaues positive
 all_long$d <- abs(all_long$d)
+
+# Combine RT and accuracy values for 2021 paper into one column
+
+# First, combine RT and accuracy dataframes
+
+rt_ac_2021 <- plyr::rbind.fill(main_2021_rt, main_2021_perceptual)
+
+# Same for 2021b paper
+
+rt_ac_2021b <- plyr::rbind.fill(main_2021b_rt, main_2021b_perceptual)
+
+# reshape 2021 data to long format
+long_2021 <- rt_ac_2021 %>%
+  tidyr::pivot_longer(!id | n,  names_to = "comparison", values_to = "value")
+
+# reshape 2021b data to long format
+
+long_2021b <- rt_ac_2021b %>%
+  tidyr::pivot_longer(!id | n,  names_to = "comparison", values_to = "value")
+
+# combine the datasets
+
+all_2021 <- cbind(long_2021, long_2021b$value)
 
 
 # CREATE FIGURE ---------------
@@ -111,3 +137,8 @@ ggplot2::ggplot(data = all_long,
            x = 2.5,
            y = .5,
            label = "Cohen's benchmark\nfor a large effect")
+
+
+# CORRELATION ANALYSIS ---------------
+
+cor(all_2021$value, all_2021$`long_2021b$value`)

### 2021-09-24 scripts/wrangle_2021b.R

@@ -1,0 +1,110 @@
+# Data wrangling for Lola & Tzetzis 2021
+#
+#
+#Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C. (2021). The influence of analogies on the development
+#of selective attention in novices in normal or stressful conditions. Journal of Human Sport and Exercise, in press.
+#https://doi.org/10.14198/jhse.2023.181.12
+# Created by Brad McKay
+# Cleaned by Mike Carter
+
+# SCRIPT SETUP ---------------
+#
+# Required libraries
+library(compute.es)
+library(daff)
+library(tidyverse)
+
+# Load data files
+#
+# Brad's extraction for perceptual accuracy and reaction time
+bm_2021b_rt <- readr::read_csv("data/brad/2021b/data_rt.csv")
+bm_2021b_perceptual <- readr::read_csv("data/brad/2021b/data_ac.csv")
+
+# Mike's extraction for perceptual accuracy and reaction time
+mc_2021b_rt <- readr::read_csv("data/mike/2021b/data_rt.csv")
+mc_2021b_perceptual <- readr::read_csv("data/mike/2021b/data_ac.csv")
+
+
+# EXTRACTION COMPARISONS ---------------
+#
+# Compare Brad's and Mike's extractions for perceptual accuracy data
+perceptual_diff <- daff::diff_data(bm_2021b_perceptual, mc_2021b_perceptual)
+daff::render_diff(perceptual_diff)
+
+#>>> Outcome of diff: Mike's extraction contained an error on n values
+
+# Use Brad's extraction for the main perceptual accuracy variable
+main_2021b_perceptual <- bm_2021b_perceptual
+
+# Compare Brad's and Mike's extractions for reaction time data
+rt_diff <- daff::diff_data(bm_2021b_rt, mc_2021b_rt)
+daff::render_diff(rt_diff)
+
+#>>> Outcome of diff: Mike's extraction contained an error on n values
+
+# Use Brad's extraction for the main reaction variable
+main_2021b_rt <- bm_2021b_rt
+
+# EFFECT SIZE CALCULATIONS ---------------
+#
+# Perceptual accuracy data
+E_A <- compute.es::mes(E_m, A_m, E_sd, A_sd, n, n,
[…]

### 2021-09-27 scripts/main.R
update: edits to script and manuscript

@@ -41,28 +41,24 @@ all_long <- all_effects %>%
 # Make all d vaues positive
 all_long$d <- abs(all_long$d)
 
-# Combine RT and accuracy values for 2021 paper into one column
 
-# First, combine RT and accuracy dataframes
+# reshape 2021 RT mean data to long format
+long_2021_rt_m <- main_2021_rt %>%
+  tidyr::pivot_longer(!id & !n & !I_sd & !A_sd & !E_sd & !C_sd,  names_to = "comparison", values_to = "value")
 
-rt_ac_2021 <- plyr::rbind.fill(main_2021_rt, main_2021_perceptual)
+# reshape 2021b RT mean data to long format
+long_2021b_rt_m <- main_2021b_rt %>%
+  tidyr::pivot_longer(!id & !n & !I_sd & !A_sd & !E_sd & !C_sd,  names_to = "comparison", values_to = "value")
 
-# Same for 2021b paper
+# reshape 2021 accuracy mean data to long format
+long_2021_ac_m <- main_2021_perceptual %>%
+  tidyr::pivot_longer(!id & !n & !I_sd & !A_sd & !E_sd & !C_sd,  names_to = "comparison", values_to = "value")
 
-rt_ac_2021b <- plyr::rbind.fill(main_2021b_rt, main_2021b_perceptual)
+# reshape 2021b accuracy mean data to long format
+long_2021b_ac_m <- main_2021b_perceptual %>%
+  tidyr::pivot_longer(!id & !n & !I_sd & !A_sd & !E_sd & !C_sd,  names_to = "comparison", values_to = "value")
 
-# reshape 2021 data to long format
-long_2021 <- rt_ac_2021 %>%
-  tidyr::pivot_longer(!id | n,  names_to = "comparison", values_to = "value")
 
-# reshape 2021b data to long format
-
-long_2021b <- rt_ac_2021b %>%
-  tidyr::pivot_longer(!id | n,  names_to = "comparison", values_to = "value")
-
-# combine the datasets
-
-all_2021 <- cbind(long_2021, long_2021b$value)
 
 
 # CREATE FIGURE ---------------
@@ -141,4 +137,10 @@ ggplot2::ggplot(data = all_long,
 
 # CORRELATION ANALYSIS ---------------
 
-cor(all_2021$value, all_2021$`long_2021b$value`)
+# correlation between accuracy 2021 and 2021b accuracy means
[…]

### 2021-09-28 docs/manuscript/manuscript.Rmd
update: rearrange articles by year in title to match numbering in body
merge: updated_manuscript directory into manuscript directory

@@
 
+Article 2 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online 11 days before we posted the first preprint of this paper (published September 3rd, 2021; preprint posted September 14th, 2021).
+We were unaware of Article 2 when posting the original preprint and it was not included in that version.
+However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Further, in comparing the reaction time and accuracy means reported in @lola2021b to those reported in @lola2021, it appeared the data shared a remarkably similar pattern.
+To investigate this similarity further, we conducted a correlation analysis between the two data sets.
+The reaction time means for each group and time point were highly correlated between the two papers, *r* = .99, as were the accuracy means, *r* = .99.
+
 # Discussion
 
-We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning [@lola2012; @lola2020; @lola2021; @tzetzis2010; @tzetzis2015].
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning [@lola2012; @lola2020; @lola2021;@lola2021b; @tzetzis2010; @tzetzis2015].
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 These errors were pervasive and appear to have substantially affected the conclusions of the articles in question.
-At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do[^5], many in the research community may find it difficult to trust any of these results.
+At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
+Even if the authors offer corrections, which they have suggested they intend to do[^6], many in the research community may find it difficult to trust any of these results.
 
-[^5]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions have been taken by the authors.
+## Comments on Article 2
+
+The data published in Article 2 are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors have published an additional article with results that are not only implausible, but highly correlated with the results reported in a previous article.
+We cannot think of a benign explanation for this sequence of events.
+
+[^6]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions have been taken by the authors.
 

### 2021-09-28 docs/manuscript/manuscript.tex
merge: updated_manuscript directory into manuscript directory

--- 2021-09-11 docs/manuscript/manuscript.tex
@@
   man, donotrepeattitle,floatsintext]{apa7}
-\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
+\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
 \author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
@@
 
-We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
-All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., 2021; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
 In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills.
 Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-We will refer to the five articles throughout this paper using the following numbering system:
+We will refer to the six articles throughout this paper using the following numbering system:
 
@@
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2).
-In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 2 had a measure of self-efficacy using a Likert scale.
-Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
+In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale.
+Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
 
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article (except Lola et al.
+(2021), which was not published yet) and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
@@
 
-To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
+To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
 We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation.
@@
 
-\caption{Absolute Cohen's \(d\) estimates from Articles 1-4 plotted on a logarithmic scale.
+\caption{Absolute Cohen's \(d\) estimates from Articles 1-5 plotted on a logarithmic scale.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 
-In the context of the maximum values observed in our simulations, all five articles in question reported implausibly large effect sizes.
+In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
 In Article 1, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
@@
 
-In Article 2, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
+In Article 3, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
 Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.\footnote{Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task (see Fischman, 2015; Hancock, Butler, \& Fischman, 1995; Reeve, Fischman, Christina, \& Cauraugh, 1994 for discussions).} Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 3, 4, and 5.
-The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 5 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1-3 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 3, and 80 in Article 2.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
+The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
+Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \ref{tab:table1}).
 We assumed that each article was based on different samples as none of the articles mentioned using any previously published data.
+
+Article 2 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online 11 days before we posted the first preprint of this paper (published September 3rd, 2021; preprint posted September 14th, 2021).
+We were unaware of Article 2 when posting the original preprint and it was not included in that version.
+However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Further, in comparing the reaction time and accuracy means reported in Lola et al.
+(2021) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
+To investigate this similarity further, we conducted a correlation analysis between the two data sets.
+The reaction time means for each group and time point were highly correlated between the two papers, \emph{r} = .99, as were the accuracy means, \emph{r} = .99.
 
@@
 
-We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola et al., 2021; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
+Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., 2021; Lola \& Tzetzis, 2021).
 Considering these findings, the conclusions from these articles are not reliable.
@@
 These errors were pervasive and appear to have substantially affected the conclusions of the articles in question.
-At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-11), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
+Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-27), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+
+\hypertarget{comments-on-article-2}{%
+\subsection{Comments on Article 2}\label{comments-on-article-2}}
+
+The data published in Article 2 are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors have published an additional article with results that are not only implausible, but highly correlated with the results reported in a previous article.
+We cannot think of a benign explanation for this sequence of events.
 
@@
 
-R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
+R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
 
@@
 \url{https://doi.org/10.3389/fpsyg.2013.00863}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lola2021b}{}}%
+Lola, A.
+C., Giatis, G., Pérez-Turpin, J.
+A., \& Tzetzis, G.
+C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+\emph{Journal of Human Sport and Exercise}, \emph{in press}(0), 1--14.
+\url{https://doi.org/10.14198/jhse.2023.181.12}
 

### 2021-09-28 docs/manuscript/manuscript.Rmd
update: minor edits

@@
 [^1]: One of the six papers had a third author and one had a third and fourth author.
-[^2]: After sharing a preprint of the original version of this paper, the editors of the *International Journal of Sport and Exercise Psychology* have indicated they intend to retract @lola2021.
+[^2]: We contacted the Editors of the journals that published Articles 1, 3, 4, and 5 on Sept 22 2021.
+The Editors have either indicated their intention to further investigate these issues and/or take corrective actions.
 
@@
 Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C.
-(2021).
+(In Press).
 The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
-*Journal of Human Sport and Exercise, in press*.
+*Journal of Human Sport and Exercise*.
 https://doi.org/10.14198/jhse.2023.181.12
@@
 
+\vspace{6ex}
+
 ```{r table1, echo = FALSE, results = "asis"}
@@
   c2 = c("60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
-         "60 females, age range: 11 to 12 years (mean and standard deviation not reported)",
+         "60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)",
          "80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
@@
 ```
+
+\newpage
 
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article (except @lola2021b, which was not published yet) and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article[^4] and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
@@
 Our extracted data and analysis scripts can be accessed at the following link: https://osf.io/raz6q/.
+
+[^4]: Excluding @lola2021b article as it had not yet been accepted for publication.
 
@@
 Finally, the mean-variance pair is compared to possible mean-variance pairings (the GRIMMER test handles sample sizes between 5 and 99).
-Using GRIMMER it is possible to determine if specific mean and standard deviation pairs are possible for data of a given sample size.
+Using GRIMMER, it is possible to determine if specific mean and standard deviation pairs are possible for data of a given sample size.
 To be conservative, we specified that we did not know whether the standard deviation was calculated for the sample or population, nor whether ambiguous values were rounded up or down.
@@
 Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion].
-Conventional benchmarks for small, medium and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions].
+Conventional benchmarks for small, medium, and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions].
 Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].
@@
 The motor component data revealed post-treatment effect sizes ranging from *d* = 1.16 to *d* = 13.5.
-
 In Article 2, the smallest post-intervention difference in reaction times was *d* = .64.
-However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.0.
-The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger *d* = 5.0 and a largest effect of *d* = 13.35.
+However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.
+The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than *d* = 5 and a largest effect of *d* = 13.35.
 
@@
 In Article 3, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
-Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^4] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
+Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^5] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
 The perfect score was not a rounding error because the same group was reported to have a mean score of 2.99 with a standard deviation of .11 on the post-test.
@@
 
-[^4]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [see @fischman2015; @hancock1995; @reeve1994 for discussions].
+[^5]: Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task [see @fischman2015; @hancock1995; @reeve1994 for discussions].
 
@@
 For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^5]
+However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^6]
 
-[^5]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
+[^6]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
 This is because of sample size differences (*n* = 20 for the consistent result and *n* = 12 for the inconsistent one).
@@
 
-Article 2 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online 11 days before we posted the first preprint of this paper (published September 3rd, 2021; preprint posted September 14th, 2021).
+Article 2 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
 We were unaware of Article 2 when posting the original preprint and it was not included in that version.
@@
 Other irregularities, such as a repeating *F*-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
-Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed.
+Indeed, the authors have already admitted that some values reported in their tables were in error, but failed to identify which values and which articles.
+Overall, it seems errors occurred in all of the articles we have reviewed.
 These errors were pervasive and appear to have substantially affected the conclusions of the articles in question.
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do[^6], many in the research community may find it difficult to trust any of these results.
+Even if the authors offer corrections, which they have suggested they intend to do[^7], many in the research community may find it difficult to trust any of these results.
+
+[^7]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
 
@@
 We cannot think of a benign explanation for this sequence of events.
-
-[^6]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions have been taken by the authors.
 

### 2021-09-28 docs/manuscript/manuscript.tex
update: minor edits

@@
   man, donotrepeattitle,floatsintext]{apa7}
-\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
+\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
 \author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
@@
 \hypersetup{
-  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
+  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
   pdfauthor={Brad McKay1 \& Michael J. Carter1},
@@
 Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., \(F\)-statistics) across multiple papers.
-Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions\footnote{After sharing a preprint of the original version of this paper, the editors of the \emph{International Journal of Sport and Exercise Psychology} have indicated they intend to retract Lola and Tzetzis (2021).}.
+Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions\footnote{We contacted the Editors of the journals that published Articles 1, 3, 4, and 5 on Sept 22 2021.
+The Editors have either indicated their intention to further investigate these issues and/or take corrective actions.}.
 Below, we outline our causes for concern and the overarching issues we found across the six articles in question.
@@
 
-We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., 2021; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., In Press; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
 All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
@@
   Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., \& Tzetzis, G.C.
-(2021).
+(In Press).
 The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
-\emph{Journal of Human Sport and Exercise, in press}.
+\emph{Journal of Human Sport and Exercise}.
 \url{https://doi.org/10.14198/jhse.2023.181.12}
@@
 
+\vspace{6ex}
+
 \begin{table}
@@
 \multicolumn{2}{l}{\textbf{Article 2}}\\
-\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years (mean and standard deviation not reported)\\
+\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
 \addlinespace[0.3em]
@@
 \end{table}
+
+\newpage
 
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article (except Lola et al.
-(2021), which was not published yet) and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola et al.
+(In Press) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
@@
 Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion).
-Conventional benchmarks for small, medium and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions).
+Conventional benchmarks for small, medium, and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions).
 Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).
@@
 The motor component data revealed post-treatment effect sizes ranging from \emph{d} = 1.16 to \emph{d} = 13.5.
-
 In Article 2, the smallest post-intervention difference in reaction times was \emph{d} = .64.
-However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.0.
-The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger \emph{d} = 5.0 and a largest effect of \emph{d} = 13.35.
+However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.
+The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35.
 
@@
 
-Article 2 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online 11 days before we posted the first preprint of this paper (published September 3rd, 2021; preprint posted September 14th, 2021).
+Article 2 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
 We were unaware of Article 2 when posting the original preprint and it was not included in that version.
@@
 Further, in comparing the reaction time and accuracy means reported in Lola et al.
-(2021) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
+(In Press) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
 To investigate this similarity further, we conducted a correlation analysis between the two data sets.
@@
 
-We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola et al., 2021; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola et al., In Press; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., 2021; Lola \& Tzetzis, 2021).
+Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., In Press; Lola \& Tzetzis, 2021).
 Considering these findings, the conclusions from these articles are not reliable.
@@
 Other irregularities, such as a repeating \emph{F}-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
-Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed.
+Indeed, the authors have already admitted that some values reported in their tables were in error, but failed to identify which values and which articles.
+Overall, it seems errors occurred in all of the articles we have reviewed.
 These errors were pervasive and appear to have substantially affected the conclusions of the articles in question.
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-27), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-27), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.}, many in the research community may find it difficult to trust any of these results.
 
@@
 C.
-(2021).
+(In Press).
 The influence of analogies on the development of selective attention in novices in normal or stressful conditions.

### 2021-09-28 docs/manuscript/manuscript.tex
update: added front matter for submission to meta-psychology

@@
   man, donotrepeattitle,floatsintext]{apa7}
-\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
-\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
-\date{}
-
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 \pagewiselinenumbers
-\ifXeTeX
+\ifxetex
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifLuaTeX
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
+\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
+\date{}
+
+\note{
+
+\vspace{\baselineskip}
+
+\raggedright Submitted to \emph{Meta-Psychology}.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+The full editorial process of all articles under review at \emph{Meta-Psychology} can be found here: \url{https://tinyurl.com/mp-submissions} You will find this preprint by searching for the first author's name.
+
+}
 
@@
 
+\vspace{-.5cm} 
 \addORCIDlink{Brad McKay}{0000-0002-7408-2323}
@@
 
-We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., In Press; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola, Giatis, Pérez-Turpin, \& Tzetzis, In Press; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola et al.
-(In Press) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
@@
 However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
-Further, in comparing the reaction time and accuracy means reported in Lola et al.
-(In Press) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
+Further, in comparing the reaction time and accuracy means reported in Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
 To investigate this similarity further, we conducted a correlation analysis between the two data sets.
@@
 
-We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola et al., In Press; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola, Giatis, Pérez-Turpin, \& Tzetzis, In Press; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., In Press; Lola \& Tzetzis, 2021).
+Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola, Giatis, Pérez-Turpin, \& Tzetzis, In Press; Lola \& Tzetzis, 2021).
 Considering these findings, the conclusions from these articles are not reliable.
@@
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-27), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-28), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.}, many in the research community may find it difficult to trust any of these results.
 
@@
 
-R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
+R (Version 4.0.4; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Version 0.5.1; Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Version 0.5; Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019).
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-anaya2016}{}}%
+\leavevmode\hypertarget{ref-anaya2016}{}%
 Anaya, J. (2016). \emph{The GRIMMER test: A method for testing the validity of reported measures of variability}. \url{https://doi.org/10.7287/peerj.preprints.2400v1}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+\leavevmode\hypertarget{ref-R-papaja}{}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2011}{}}%
+\leavevmode\hypertarget{ref-bakker2011}{}%
 Bakker, M., \& Wicherts, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-brown2017}{}}%
+\leavevmode\hypertarget{ref-brown2017}{}%
 Brown, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cohen1962}{}}%
+\leavevmode\hypertarget{ref-cohen1962}{}%
 Cohen, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cohen1988}{}}%
+\leavevmode\hypertarget{ref-cohen1988}{}%
 Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). New York: Routledge. \url{https://doi.org/10.4324/9780203771587}
 
-\leavevmode\vadjust pre{\hypertarget{ref-correll2020}{}}%
+\leavevmode\hypertarget{ref-correll2020}{}%
 Correll, J., Mellinger, C., McClelland, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lemon}{}}%
+\leavevmode\hypertarget{ref-R-lemon}{}%
 Edwards, S. M. (2020). \emph{Lemon: Freshing up your 'ggplot2' plots}. Retrieved from \url{https://CRAN.R-project.org/package=lemon}
 
-\leavevmode\vadjust pre{\hypertarget{ref-field2016}{}}%
+\leavevmode\hypertarget{ref-field2016}{}%
 Field, A. P. (2016). \emph{An adventure in statistics: The reality enigma}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-fischman2015}{}}%
+\leavevmode\hypertarget{ref-fischman2015}{}%
 Fischman, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-daff}{}}%
+\leavevmode\hypertarget{ref-R-daff}{}%
 Fitzpatrick, P., de Jonge, E., \& Warnes, G. R. (2019). \emph{Daff: Diff, patch and merge for data.frames}. Retrieved from \url{https://CRAN.R-project.org/package=daff}
 
-\leavevmode\vadjust pre{\hypertarget{ref-gray2021}{}}%
+\leavevmode\hypertarget{ref-gray2021}{}%
 Gray, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hancock1995}{}}%
+\leavevmode\hypertarget{ref-hancock1995}{}%
 Hancock, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lakens2013}{}}%
+\leavevmode\hypertarget{ref-lakens2013}{}%
 Lakens, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lola2021b}{}}%
+\leavevmode\hypertarget{ref-lola2021b}{}%
 Lola, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lola2020}{}}%
+\leavevmode\hypertarget{ref-lola2020}{}%
 Lola, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lola2021}{}}%
+\leavevmode\hypertarget{ref-lola2021}{}%
 Lola, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lola2012}{}}%
+\leavevmode\hypertarget{ref-lola2012}{}%
 Lola, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lovakov2021}{}}%
+\leavevmode\hypertarget{ref-lovakov2021}{}%
 Lovakov, A., \& Agadullina, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-munafo2017}{}}%
+\leavevmode\hypertarget{ref-munafo2017}{}%
 Munafò, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-gridGraphics}{}}%
+\leavevmode\hypertarget{ref-R-gridGraphics}{}%
 Murrell, P., \& Wen, Z. (2020). \emph{gridGraphics: Redraw base graphics using 'grid' graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridGraphics}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lsr}{}}%
+\leavevmode\hypertarget{ref-R-lsr}{}%
 Navarro, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-RColorBrewer}{}}%
+\leavevmode\hypertarget{ref-R-RColorBrewer}{}%
 Neuwirth, E. (2014). \emph{RColorBrewer: ColorBrewer palettes}. Retrieved from \url{https://CRAN.R-project.org/package=RColorBrewer}
 
-\leavevmode\vadjust pre{\hypertarget{ref-nuijten2016}{}}%
+\leavevmode\hypertarget{ref-nuijten2016}{}%
 Nuijten, M.
@@
 (2016).
-The prevalence of statistical reporting errors in psychology (1985{\textendash}2013).
+The prevalence of statistical reporting errors in psychology (1985{{}}2013).
 \emph{Behavior Research Methods}, \emph{48}(4), 1205--1226.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+\leavevmode\hypertarget{ref-R-base}{}%
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-compute.es}{}}%
+\leavevmode\hypertarget{ref-R-compute.es}{}%
 Re, A. C. D. (2013). Compute.es: Compute effect sizes. In \emph{R Package}. Retrieved from \url{https://cran.r-project.org/package=compute.es}
 
-\leavevmode\vadjust pre{\hypertarget{ref-reeve1994}{}}%
+\leavevmode\hypertarget{ref-reeve1994}{}%
 Reeve, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-thompson2007}{}}%
+\leavevmode\hypertarget{ref-thompson2007}{}%
 Thompson, B. (2007). Effect sizes, confidence intervals, and confidence intervals for effect sizes. \emph{Psychology in the Schools}, \emph{44}(5), 423--432. \url{https://doi.org/10.1002/pits.20234}
 
-\leavevmode\vadjust pre{\hypertarget{ref-tsorbatzoudis1998}{}}%
+\leavevmode\hypertarget{ref-tsorbatzoudis1998}{}%
 Tsorbatzoudis, H., Barkoukis, V., Kaissidis-Rodafinos, A., \& Grouios, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tzetzis2010}{}}%
+\leavevmode\hypertarget{ref-tzetzis2010}{}%
 Tzetzis, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tzetzis2015}{}}%
+\leavevmode\hypertarget{ref-tzetzis2015}{}%
 Tzetzis, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-scales}{}}%
+\leavevmode\hypertarget{ref-R-scales}{}%
 Wickham, H., \& Seidel, D. (2020). \emph{Scales: Scale functions for visualization}. Retrieved from \url{https://CRAN.R-project.org/package=scales}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+\leavevmode\hypertarget{ref-R-kableExtra}{}%
 Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}

### 2021-09-29 docs/manuscript/manuscript.tex
fix: spacing issues on title page and location of Table 1

--- 2021-09-28 docs/manuscript/manuscript.tex
@@
 
+\note{
+
+\vspace{\baselineskip}
+
+\raggedright Submitted to \emph{Meta-Psychology}.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+The full editorial process of all articles under review at \emph{Meta-Psychology} can be found here: \url{https://tinyurl.com/mp-submissions} You will find this preprint by searching for the first author's name.
+
+}
+
 \authornote{
 
+\vspace{-4em} 
 \addORCIDlink{Brad McKay}{0000-0002-7408-2323}  
-
-\addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+\newline \indent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
 

### 2021-09-29 scripts/wrangle_2021b.R
update: add b indicator to year published online (and ahead of print)

@@ -1,4 +1,4 @@
-# Data wrangling for Lola & Tzetzis 2021
+# Data wrangling for Lola & Tzetzis 2021b
 #
 #
 #Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C. (2021). The influence of analogies on the development

### 2022-01-14 docs/manuscript/manuscript.tex
update: revisions following feedback from meta-psychology

--- 2021-09-28 docs/manuscript/manuscript.tex
@@
 \hypersetup{
-  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
+  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
   pdfauthor={Brad McKay1 \& Michael J. Carter1},
   pdflang={en-EN},
-  pdfkeywords={Meta-science; GRIMMER; Effect sizes; Perceptual motor learning},
+  pdfkeywords={Metascience; GRIMMER; Effect sizes; Perceptual motor learning},
   hidelinks,
@@
 \shorttitle{Commentary on Lola \& Tzetzis papers}
-\keywords{Meta-science; GRIMMER; Effect sizes; Perceptual motor learning}
+\keywords{Metascience; GRIMMER; Effect sizes; Perceptual motor learning}
 \usepackage{lineno}
@@
 
-\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
+\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
 \author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
@@
 We found the pairwise effect sizes were implausible in all six articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000.
-Impossible statistics were reported in four out of the six articles.
+\textcolor{red}{In contrast, the largest effect size observed in a million simulated experiments with a true effect of} \emph{d} \textcolor{red}{= 3 was} \emph{d}\textcolor{red}{ = 6.6.} Impossible statistics were reported in four out of the six articles.
 Reported test statistics and \(\eta^{2}\) values were also implausible, with several \(\eta^{2}\) = .99 and even \(\eta^{2}\) = 1.0 for between-subjects main effects.
@@
 
-We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola, Giatis, Pérez-Turpin, \& Tzetzis, In Press; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
@@
 \item
+  Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., \& Tzetzis, G.C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+\emph{Journal of Human Sport and Exercise}.
+\url{https://doi.org/10.14198/jhse.2023.181.12}
+\item
   Lola, A.C., \& Tzetzis, G.C.
@@
 \url{https://doi.org/10.1080/1612197X.2021.1877325}
-\item
-  Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., \& Tzetzis, G.C.
-(In Press).
-The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
-\emph{Journal of Human Sport and Exercise}.
-\url{https://doi.org/10.14198/jhse.2023.181.12}
 \item
@@
 \emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This article is in a journal of a publishing group that has been identified as a potential predatory journal.
-Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS}).
+Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf\#page=57}).
 In fact, the earliest available issue on the journal's webpage is from 2016.}
@@
 \multicolumn{2}{l}{\textbf{Article 1}}\\
-\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
+\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
 \addlinespace[0.3em]
 \multicolumn{2}{l}{\textbf{Article 2}}\\
-\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
+\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
 \addlinespace[0.3em]
@@
 \item \textit{Note.} 
-\item[a] Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2.
+\item[a] Articles 2, 3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 3 from Articles 2 and 4, and a different age range in Article 4 from Articles 2 and 3.
 \end{tablenotes}
@@
 Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test.
-The authors also included a high stress test in Articles 1, 2 and 6.
+The authors also included a high stress test in Articles 1 (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021), 2 (Lola \& Tzetzis, 2021) and 6 {[}Tzetzis and Lola (2010)\}.
 
@@
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
-In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale.
-Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and \textcolor{red}{6}), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
+In addition, Articles 2 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale.
+Articles 2, 4, 5, and 6 also analyzed the number of explicit rules recalled.
 
@@
 None of the six articles in question included a link to a public repository where the data could be accessed.
-We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
+We first wrote (email sent February 10, 2021) the corresponding author for Article 2 and asked if they would be willing to share the data for this experiment.
 The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A.
 Lola, personal communication, February 12 2021).
-We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent and presumably, all planned analyses had been completed.
+We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent, and presumably all planned analyses had been completed.
 After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6.
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola, Giatis, Pérez-Turpin, and Tzetzis (2021) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns.
-Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles.
-The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
+The authors did address some specific concerns regarding Article 2, but for the most part only provided more general responses to our concerns.
+The authors admitted that some of the values reported in the other target articles were incorrect but did not identify which values or articles.
 Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A.
@@
 
-Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
+Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity \textcolor{red}{in both the negative and positive direction.
+We calculated absolute values so that all effects were positive}.
 Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion).
 Conventional benchmarks for small, medium, and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions).
-Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).
+Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).\textcolor{red}{In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of} \emph{d} = .19 (McKay et al., 2021), \emph{d}= .54 (McKay, Yantha, Hussien, Carter, \& Ste-Marie, in press), and \emph{d} = .71 (Lohse, Buchanan, \& Miller, 2016).
 
-To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
+To evaluate the maximum plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
 We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation.
@@
 
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1}
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1b}
 
@@
 \caption{Absolute Cohen's \(d\) estimates from Articles 1-5 plotted on a logarithmic scale.
+Only data from the original tables in Article 2 are included.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
+\textcolor{red}{The original table of summary statistics in Article 1 indicated that} the smallest post-intervention difference in reaction times was \emph{d} = .64.
+However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.
+The accuracy data also reflected improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35.
+\textcolor{red}{However, a correction to the tables of summary statistics was published that included substantially smaller standard deviations than the original tables.
+While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the analyses reported in Article 2.}
+
+In Article 2, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
 The smallest post-intervention effect at any of the three time points was \emph{d} = 286.42, while the largest effect was \emph{d} = 3504.86.
@@
 The motor component data revealed post-treatment effect sizes ranging from \emph{d} = 1.16 to \emph{d} = 13.5.
-In Article 2, the smallest post-intervention difference in reaction times was \emph{d} = .64.
-However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.
-The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35.
 
@@
 
-In Article 1, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants.
+In Article 2, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants.
 Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item.
@@
 
-Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+Articles 2, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78).
-The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
-In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
+In Article 2, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups (I: \emph{M} = .73, \emph{SD} = .35; A: \emph{M} = 1.03, \emph{SD} = .25; E: \emph{M} = 4.8, \emph{SD} = .78; C: \emph{M} = .67, \emph{SD} = .48; \emph{n} = 15).
+In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78) \textcolor{red}{and the implicit group} (\emph{M} = 2.3, \emph{SD} = 1.3).
+The mean and standard deviation pairs for the remaining \textcolor{red}{two} groups were GRIMMER inconsistent (S: \emph{M} = 4.2, \emph{SD} = 1.07; C: \emph{M} = 1.8, \emph{SD} = .3; \emph{n} = 15).
+In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample (S: \emph{M} = 4.2, \emph{SD} = 1.07; I: \emph{M} = 2.3, \emph{SD} = 1.3; C: \emph{M} = 1.4, \emph{SD} = .9; \emph{n} = 12).
 For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent (\emph{M} = 4.8, \emph{SD} = 1.78).\footnote{You may have noticed that the same mean and standard deviation pairing (\emph{M} = 4.8, \emph{SD} = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences (\emph{n} = 20 for the consistent result and \emph{n} = 12 for the inconsistent one).}
+However, the results for the explicit group were GRIMMER inconsistent (\emph{M} = 4.8, \emph{SD} = 1.78).\footnote{You may have noticed that \textcolor{red}{two} of the same mean and standard deviation pairings (\emph{M} = 4.8, \emph{SD} = 1.78; \emph{M} = 4.2, \emph{SD} = 1.07) were classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences (\emph{n} = 15 and \emph{n} = 12).}
 
@@
 Benchmarks have been suggested for small, medium, and large effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988).
-Importantly, if a main effect of instruction-type results in \(\eta^{2}\) = .99, as was commonly reported in the target articles, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone.
+Importantly, if the main effect of instruction-type results in \(\eta^{2}\) = .99, as was commonly reported in the target articles, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
 
-Article 1 did not report \(\eta^{2}\) values but had the largest pairwise effects and \emph{F}-statistics of the five articles in question.
+Article 2 did not report \(\eta^{2}\) values but had the largest pairwise effects and \emph{F}-statistics of the five articles in question.
 Article 3 reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
@@
 With respect to response accuracy, the reported effects were \(\eta^{2}\) = .98, \(\eta^{2}\) = .94, \(\eta^{2}\) = .93 for the Time, Group, and Time x Group analyses, respectively.
-Article 5 reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses, respectively.
+Article \textcolor{red}{6} reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses, respectively.
 
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
-The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 2, 4, 5, and 6.
+The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 2, 4, and 5).
+Articles 2, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 2 and 4, and 80 in Article 3.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \ref{tab:table1}).
@@
 
-Article 2 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
-We were unaware of Article 2 when posting the original preprint and it was not included in that version.
-However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
-Further, in comparing the reaction time and accuracy means reported in Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
+Article 1 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
+We were unaware of Article 1 when posting the original preprint and it was not included in that version.
+However, when we became aware of Article 1 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Further, in comparing the reaction time and accuracy means reported in Lola, Giatis, Pérez-Turpin, and Tzetzis (2021) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
 To investigate this similarity further, we conducted a correlation analysis between the two data sets.
 The reaction time means for each group and time point were highly correlated between the two papers, \emph{r} = .99, as were the accuracy means, \emph{r} = .99.
+
+\hypertarget{new-developments-following-september-28-2021-update}{%
+\subsection{New Developments Following September 28, 2021 Update}\label{new-developments-following-september-28-2021-update}}
+
+\textcolor{red}{After contacting the editors of Articles 2, 3, 4, and 5 on September 22nd and updating the preprint of this paper on September 28th, at least two important developments transpired.
+First, there was a response from all four editors indicating an intention to investigate the issues we raised.
+The} \emph{International Journal of Sport and Exercise Psychology} \textcolor{red}{is so far the only journal that has taken observable action, issuing an Expression of Concern regarding Article 2 on October 11th, 2021.
+The editor of Article 4 included us in an email to the authors and we were included in their reply, wherein they again insisted that their analyses and conclusions remained valid.
+They offered an updated manuscript to the journal but as far as we are aware no action has since been taken.}
+
+\textcolor{red}{The second important development was that the tables in Article 1 were updated on October 8th, 2021.
+The new tables made changes to the standard deviation values for both the reaction time and accuracy measures.
+The standard deviations of the reaction time data were adjusted such that the decimal point was shifted one place to the right compared to the original version.
+For example, an original standard deviation of 10.25 is now 102.51.
+The adjustments to the accuracy data now show the original standard deviation values as standard errors and new standard deviations are reported.
+Although the adjustments to the tables reflect corrections to plausible mishaps in the publication process and correcting such errors should be applauded, the new data themselves are problematic when compared to the reported analyses.}
+
+\textcolor{red}{To illustrate the disconnect between the new values and the test statistics in Article 1, we used the `faux` package in `R` to simulate data from multivariate normal distributions with the same mean and standard deviation parameters as the original and updated tables.
+We then analyzed the data using the same 4 X 4 mixed ANOVA model reported by the authors and compared the test statistics we observed to those reported in Article 1.
+We tried various correlations between timepoints and chose the value that produced the closest agreement between our analyses and theirs} (\emph{r} = .8).
+
+\textcolor{red}{Our analysis of simulated reaction time data using the originally reported standard deviations produced} \emph{F}-statistics \textcolor{red}{that were more similar to the values reported in Article 1 than our analysis based on the updated numbers.
+Using the originally reported figures, we observed an} \emph{F} = 18,193 \textcolor{red}{for the main effect of time.
+The authors reported} \emph{F} = 16,055 \textcolor{red}{for this analysis.
+Our analysis using the updated statistics resulted in} \emph{F} = 186.
+\textcolor{red}{Similarly, the Time X Group interaction was} \emph{F} = 4242 \textcolor{red}{in Article 1,} \emph{F} = 6208 \textcolor{red}{in our simulation of the original parameters, and} \emph{F} = 54 \textcolor{red}{using the updated numbers.
+The main effect of group was} \emph{F} = 7156 \textcolor{red}{in Article 1,} \emph{F} = 3030 \textcolor{red}{in our simulation of the original parameters, and} \emph{F} = 23 \textcolor{red}{using the updated numbers.
+As is evident, although the updated standard deviations lead to more plausible effect size calculations than the originally reported values, they are not consistent with the analyses reported in the paper.}
+
+\textcolor{red}{We observed similarly discordant *F*-statistics with analyses of simulated accuracy data based on the updated statistics.
+Article 1 reported a main effect of time of} \emph{F} = 3278,\textcolor{red}{ we observed} \emph{F} = 2412 \textcolor{red}{when analyzing our simulation of the original parameters, and} \emph{F} = 132\textcolor{red}{ when using the updated parameters.
+The authors reported a Group X Time interaction of} \emph{F} = 657, \textcolor{red}{we found} \emph{F} = 494 \textcolor{red}{with simulations of the original statistics, and} \emph{F} = 27 \textcolor{red}{when using the updated values.
+Finally, the main effect of group was reported as} \emph{F} = 922, \textcolor{red}{we found} \emph{F} = 254 \textcolor{red}{with simulations of the original statistics, and} \emph{F} = 21 \textcolor{red}{when analyzing simulations of the updated data.}
 
@@
 
-We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola, Giatis, Pérez-Turpin, \& Tzetzis, In Press; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola, Giatis, Pérez-Turpin, \& Tzetzis, In Press; Lola \& Tzetzis, 2021).
-Considering these findings, the conclusions from these articles are not reliable.
+We discovered that the data reported in two articles are very highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2021).
+\textcolor{red}{Finally, we observed that recently updated tables of summary statistics in Article 1 were incompatible with the analyses reported in the paper, while the original summary statistics, which indicate implausible effect sizes, were more compatible with the analyses.} Considering these findings, the conclusions from these articles are not reliable.
 
@@
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-28), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer \textcolor{red}{additional} corrections, which they have suggested they intend to do\footnote{\textcolor{red}{There is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
+However, as mentioned, the tables in Article 2 were updated and the authors offered corrections in response to the editors of Article 5.
+We do not know if additional corrections have been submitted.}}, many in the research community may find it difficult to trust any of these results.
 
-\hypertarget{comments-on-article-2}{%
-\subsection{Comments on Article 2}\label{comments-on-article-2}}
+\hypertarget{comments-on-article-1}{%
+\subsection{Comments on Article 1}\label{comments-on-article-1}}
 
-The data published in Article 2 are especially concerning.
+The data published in Article 1 are especially concerning.
 The article information indicates that it was submitted on June 17, 2021.
 Our email correspondence with the authors ended on April 22, 2021.
-Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
-Despite this correspondence, the authors have published an additional article with results that are not only implausible, but highly correlated with the results reported in a previous article.
-We cannot think of a benign explanation for this sequence of events.
+Therefore, Article 1 was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors published an additional article with results that \textcolor{red}{were} not only implausible, but highly correlated with the results reported in a previous article.
+\textcolor{red}{Subsequently, the authors published corrected tables with new standard deviation values.
+The means remained highly correlated with those reported in Article 2, but the new standard deviations were substantially larger than the original values.
+The updated summary statistics are not consistent with the test statistics reported in Article 1.
+Without commenting further on the possible causes of this sequence of events, we note only that they do not inspire confidence in the validity of the results reported in the target articles.}
 
@@
 
-R (Version 4.0.4; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Version 0.5.1; Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Version 0.5; Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019).
+R (Version 4.0.4; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{faux} (Version 1.1.0; DeBruine, 2021), \emph{gridGraphics} (Version 0.5.1; Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Version 0.5; Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019).
 
@@
 
+\leavevmode\hypertarget{ref-R-faux}{}%
+DeBruine, L. (2021). \emph{Faux: Simulation for factorial designs}. Zenodo. \url{https://doi.org/10.5281/zenodo.2669586}
+
 \leavevmode\hypertarget{ref-R-lemon}{}%
@@
 
+\leavevmode\hypertarget{ref-lohse2016}{}%
+Lohse, K., Buchanan, T., \& Miller, M.
+(2016).
+Underpowered and overworked: Problems with data analysis in motor learning studies.
+\emph{Journal of Motor Learning and Development}, \emph{4}(1), 37--58.
+\url{https://doi.org/10.1123/jmld.2015-0010}
+
 \leavevmode\hypertarget{ref-lola2021b}{}%
@@
 C.
-(In Press).
+(2021).
 The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
@@
 \url{https://doi.org/10.1002/ejsp.2752}
+
+\leavevmode\hypertarget{ref-mckay2021b}{}%
+McKay, B., Hussien, J., Vinh, M.-A., Mir-Orefice, A., Brooks, H., \& Ste-Marie, D.
+M.
+(2021).
+\emph{Meta-analysis of reduced relative feedback frequency effect on motor learning and performance}.
+\url{https://doi.org/10.31234/osf.io/v2cp7}
+
+\leavevmode\hypertarget{ref-mckay2021a}{}%
+McKay, B., Yantha, Z.
+D., Hussien, J., Carter, M.
+J., \& Ste-Marie, D.
+M.
+(in press).
+Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value.
+\emph{Meta-Psychology}.
+\url{https://doi.org/10.31234/osf.io/8d3nb}
 

### 2022-01-14 scripts/simulated_2021b_analyses.R

@@ -1,0 +1,229 @@
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(faux)
+
+# set seed for reproducible simulation results
+set.seed(9293)
+
+### reaction time data
+
+# create data for each group at 4 correlated time points. sample from distributions
+# with mean and sd reported in original data table.
+
+implicit_or <- rnorm_multi(n = 15,
+                   mu = c(831.12, 574.27, 587.48, 595.73),
+                   sd = c(10.25, 8.37, 9.84, 11.05),
+                   r = .8,
+                   varnames = c("A", "B", "C", "D"),
+                   empirical = FALSE)
+
+analogy_or <- rnorm_multi(n = 15,
+                          mu = c(840.23, 485.26, 479.68, 490.51),
+                          sd = c(11.39, 9.63, 9.49, 10.26),
+                          r = .8,
+                          varnames = c("A", "B", "C", "D"),
+                          empirical = FALSE)
+
+explicit_or <- rnorm_multi(n = 15,
+                           mu = c(838.17, 715.24, 742.14, 950.27),
+                           sd = c(12.25, 10.24, 11.13, 13.24),
+                           r = .8,
+                           varnames = c("A", "B", "C", "D"),
+                           empirical = FALSE)
+
+control_or <- rnorm_multi(n = 15,
+                          mu = c(841.58, 828.15, 839.19, 958.56),
+                          sd = c(10.46, 11.34, 10.95, 12.47),
+                          r = .8,
+                          varnames = c("A", "B", "C", "D"),
+                          empirical = FALSE)
+
+
+original_dat <- gdata::combine(implicit_or, analogy_or, explicit_or, control_or)
+
+# conduct 4 X 4 mixed anova with simulated data
+
+jmv::anovaRM(
+  data = original_dat,
+  rm = list(
+    list(label = "phase_id",
+         levels = c("A", "B", "C", "D"))
+  ),
+  rmCells = list(
+    list(measure = "A", cell = "A"),
+    list(measure = "B", cell = "B"),
+    list(measure = "C", cell = "C"),
+    list(measure = "D", cell = "D")
+  ),
+  bs = source,
+  rmTerms = ~ phase_id,
+  bsTerms = ~source,
+  effectSize = "ges",
+  #spherCorr = "GG"
+)
+
+
+# create data using meand and standard deviations from UPDATED tables
+
+implicit_new <- rnorm_multi(n = 15,
[…]

### 2022-01-20 docs/manuscript/manuscript.Rmd
update: added front matter for submission to meta-psychology
fix: spacing issues on title page and location of Table 1

@@
 
+note: |
+
+  \vspace{\baselineskip}\raggedright Submitted to *Meta-Psychology*.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+The full editorial process of all articles under review at *Meta-Psychology* can be found here: https://tinyurl.com/mp-submissions You will find this preprint by searching for the first author's name.
+
 authornote: |
+  \vspace{-.5cm} 
   \addORCIDlink{Brad McKay}{0000-0002-7408-2323}
@@
 We found the pairwise effect sizes were implausible in all six articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000.
-Impossible statistics were reported in four out of the six articles.
+\textcolor{red}{In contrast, the largest effect size observed in a million simulated experiments with a true effect of} *d* \textcolor{red}{= 3 was} *d*\textcolor{red}{ = 6.6.} Impossible statistics were reported in four out of the six articles.
 Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects.
@@
 
-keywords          : "Meta-science; GRIMMER; Effect sizes; Perceptual motor learning"
+keywords          : "Metascience; GRIMMER; Effect sizes; Perceptual motor learning"
 #wordcount         : "X"
@@
 1.
+Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+*Journal of Human Sport and Exercise*.
+https://doi.org/10.14198/jhse.2023.181.12
+
+2.
 Lola, A.C., & Tzetzis, G.C.
@@
 https://doi.org/10.1080/1612197X.2021.1877325
-
-2.
-Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C.
-(In Press).
-The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
-*Journal of Human Sport and Exercise*.
-https://doi.org/10.14198/jhse.2023.181.12
 
@@
 [^3]: This article is in a journal of a publishing group that has been identified as a potential predatory journal.
-Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS).
+Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf#page=57).
 In fact, the earliest available issue on the journal's webpage is from 2016.
@@
 table_1 <- tibble::tibble(
-  c1 = c("Lola \\& Tzetzis (2021)",
-         "Lola et al (2021)",
+  c1 = c("Lola et al (2021)",
+         "Lola \\& Tzetzis (2021)",
          "Lola \\& Tzetzis (2020)",
@@
          "Tzetzis \\& Lola (2010)"),
-  c2 = c("60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
-         "60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)",
+  c2 = c("60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)",
+         "60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
          "80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
@@
   pack_rows("Article 6", 6, 6) %>%
-  footnote(alphabet = c("Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2."),
+  footnote(alphabet = c("Articles 2, 3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 3 from Articles 2 and 4, and a different age range in Article 4 from Articles 2 and 3."),
            alphabet_title = "Note.",
@@
 Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test.
-The authors also included a high stress test in Articles 1, 2 and 6.
+The authors also included a high stress test in Articles 1 [@lola2021b], 2 [@lola2021] and 6 [@tzetzis2010}.
 
@@
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
-In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 3 had a measure of self-efficacy using a Likert scale.
-Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and \textcolor{red}{6}), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
+In addition, Articles 2 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 3 had a measure of self-efficacy using a Likert scale.
+Articles 2, 4, 5, and 6 also analyzed the number of explicit rules recalled.
 
@@
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns.
-Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles.
-The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
+The authors did address some specific concerns regarding Article 2, but for the most part only provided more general responses to our concerns.
+The authors admitted that some of the values reported in the other target articles were incorrect but did not identify which values or articles.
 Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A.
@@
 
-Cohen's *d* is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
+Cohen's *d* is used to describe the standardized mean difference of an effect and values can range between 0 and infinity \textcolor{red}{in both the negative and positive direction.
+We calculated absolute values so that all effects were positive}.
 Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion].
 Conventional benchmarks for small, medium, and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions].
-Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].
+Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].\textcolor{red}{In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of} *d* = .19 [@mckay2021b], *d*= .54 [@mckay2021a], and *d* = .71 [@lohse2016].
 
-To evaluate the maximum range of plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
+To evaluate the maximum plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
 We set the true effect size at *d* = .8, the conventional benchmark for a "large" treatment effect, in the first simulation.
@@
 (ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-5 plotted on a logarithmic scale.
+Only data from the original tables in Article 2 are included.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 #fig.env = "figure*"
-knitr::include_graphics("../../figs/fig1.pdf")
+knitr::include_graphics("../../figs/fig1b.pdf")
 ```
@@
 In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
+\textcolor{red}{The original table of summary statistics in Article 1 indicated that} the smallest post-intervention difference in reaction times was *d* = .64.
+However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.
+The accuracy data also reflected improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than *d* = 5 and a largest effect of *d* = 13.35.
+\textcolor{red}{However, a correction to the tables of summary statistics was published that included substantially smaller standard deviations than the original tables.
+While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the analyses reported in Article 2.}
+
+In Article 2, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
 The smallest post-intervention effect at any of the three time points was *d* = 286.42, while the largest effect was *d* = 3504.86.
@@
 The motor component data revealed post-treatment effect sizes ranging from *d* = 1.16 to *d* = 13.5.
-In Article 2, the smallest post-intervention difference in reaction times was *d* = .64.
-However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.
-The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than *d* = 5 and a largest effect of *d* = 13.35.
 
@@
 
-Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+Articles 2, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78).
-The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
-In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
+In Article 2, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups (I: *M* = .73, *SD* = .35; A: *M* = 1.03, *SD* = .25; E: *M* = 4.8, *SD* = .78; C: *M* = .67, *SD* = .48; *n* = 15).
+In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78) \textcolor{red}{and the implicit group} (*M* = 2.3, *SD* = 1.3).
+The mean and standard deviation pairs for the remaining \textcolor{red}{two} groups were GRIMMER inconsistent (S: *M* = 4.2, *SD* = 1.07; C: *M* = 1.8, *SD* = .3; *n* = 15).
+In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample (S: *M* = 4.2, *SD* = 1.07; I: *M* = 2.3, *SD* = 1.3; C: *M* = 1.4, *SD* = .9; *n* = 12).
 For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
@@
 
-[^6]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences (*n* = 20 for the consistent result and *n* = 12 for the inconsistent one).
+[^6]: You may have noticed that \textcolor{red}{two} of the same mean and standard deviation pairings (*M* = 4.8, *SD* = 1.78; *M* = 4.2, *SD* = 1.07) were classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences (*n* = 15 and *n* = 12).
 
@@
 Benchmarks have been suggested for small, medium, and large effect sizes as $\eta^{2}$ = .01, .06, and .14, respectively [@cohen1988].
-Importantly, if a main effect of instruction-type results in $\eta^{2}$ = .99, as was commonly reported in the target articles, this suggests that 99% of the total variability in the outcome measure can be explained by group assignment alone.
+Importantly, if the main effect of instruction-type results in $\eta^{2}$ = .99, as was commonly reported in the target articles, this suggests that 99% of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
 
-Article 1 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question.
+Article 2 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question.
 Article 3 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
@@
 With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses, respectively.
-Article 5 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.
+Article \textcolor{red}{6} reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.
 
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
-The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 2, 4, 5, and 6.
+The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 2, 4, and 5).
+Articles 2, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 2 and 4, and 80 in Article 3.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \@ref(tab:table1)).
@@
 
-Article 2 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
-We were unaware of Article 2 when posting the original preprint and it was not included in that version.
-However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Article 1 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
+We were unaware of Article 1 when posting the original preprint and it was not included in that version.
+However, when we became aware of Article 1 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
 Further, in comparing the reaction time and accuracy means reported in @lola2021b to those reported in @lola2021, it appeared the data shared a remarkably similar pattern.
@@
 The reaction time means for each group and time point were highly correlated between the two papers, *r* = .99, as were the accuracy means, *r* = .99.
+
+## New Developments Following September 28, 2021 Update
+
+\textcolor{red}{After contacting the editors of Articles 2, 3, 4, and 5 on September 22nd and updating the preprint of this paper on September 28th, at least two important developments transpired.
+First, there was a response from all four editors indicating an intention to investigate the issues we raised.
+The} *International Journal of Sport and Exercise Psychology* \textcolor{red}{is so far the only journal that has taken observable action, issuing an Expression of Concern regarding Article 2 on October 11th, 2021.
+The editor of Article 4 included us in an email to the authors and we were included in their reply, wherein they again insisted that their analyses and conclusions remained valid.
+They offered an updated manuscript to the journal but as far as we are aware no action has since been taken.}
+
+\textcolor{red}{The second important development was that the tables in Article 1 were updated on October 8th, 2021.
+The new tables made changes to the standard deviation values for both the reaction time and accuracy measures.
+The standard deviations of the reaction time data were adjusted such that the decimal point was shifted one place to the right compared to the original version.
+For example, an original standard deviation of 10.25 is now 102.51.
+The adjustments to the accuracy data now show the original standard deviation values as standard errors and new standard deviations are reported.
+Although the adjustments to the tables reflect corrections to plausible mishaps in the publication process and correcting such errors should be applauded, the new data themselves are problematic when compared to the reported analyses.}
+
+\textcolor{red}{To illustrate the disconnect between the new values and the test statistics in Article 1, we used the `faux` package in `R` to simulate data from multivariate normal distributions with the same mean and standard deviation parameters as the original and updated tables.
+We then analyzed the data using the same 4 X 4 mixed ANOVA model reported by the authors and compared the test statistics we observed to those reported in Article 1.
+We tried various correlations between timepoints and chose the value that produced the closest agreement between our analyses and theirs} (*r* = .8).
+
+\textcolor{red}{Our analysis of simulated reaction time data using the originally reported standard deviations produced} *F*-statistics \textcolor{red}{that were more similar to the values reported in Article 1 than our analysis based on the updated numbers.
+Using the originally reported figures, we observed an} *F* = 18,193 \textcolor{red}{for the main effect of time.
+The authors reported} *F* = 16,055 \textcolor{red}{for this analysis.
+Our analysis using the updated statistics resulted in} *F* = 186.
+\textcolor{red}{Similarly, the Time X Group interaction was} *F* = 4242 \textcolor{red}{in Article 1,} *F* = 6208 \textcolor{red}{in our simulation of the original parameters, and} *F* = 54 \textcolor{red}{using the updated numbers.
+The main effect of group was} *F* = 7156 \textcolor{red}{in Article 1,} *F* = 3030 \textcolor{red}{in our simulation of the original parameters, and} *F* = 23 \textcolor{red}{using the updated numbers.
+As is evident, although the updated standard deviations lead to more plausible effect size calculations than the originally reported values, they are not consistent with the analyses reported in the paper.}
+
+\textcolor{red}{We observed similarly discordant *F*-statistics with analyses of simulated accuracy data based on the updated statistics.
+Article 1 reported a main effect of time of} *F* = 3278,\textcolor{red}{ we observed} *F* = 2412 \textcolor{red}{when analyzing our simulation of the original parameters, and} *F* = 132\textcolor{red}{ when using the updated parameters.
+The authors reported a Group X Time interaction of} *F* = 657, \textcolor{red}{we found} *F* = 494 \textcolor{red}{with simulations of the original statistics, and} *F* = 27 \textcolor{red}{when using the updated values.
+Finally, the main effect of group was reported as} *F* = 922, \textcolor{red}{we found} *F* = 254 \textcolor{red}{with simulations of the original statistics, and} *F* = 21 \textcolor{red}{when analyzing simulations of the updated data.}
 
@@
 Further, the reported test statistics and associated $\eta^{2}$ values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations [@lola2021; @lola2021b].
-Considering these findings, the conclusions from these articles are not reliable.
+We discovered that the data reported in two articles are very highly correlated despite ostensibly coming from different experiments, samples, and situations [@lola2021; @lola2021b].
+\textcolor{red}{Finally, we observed that recently updated tables of summary statistics in Article 1 were incompatible with the analyses reported in the paper, while the original summary statistics, which indicate implausible effect sizes, were more compatible with the analyses.} Considering these findings, the conclusions from these articles are not reliable.
 
@@
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do[^7], many in the research community may find it difficult to trust any of these results.
+Even if the authors offer \textcolor{red}{additional} corrections, which they have suggested they intend to do[^7], many in the research community may find it difficult to trust any of these results.
 
-[^7]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
+[^7]: \textcolor{red}{There is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
+However, as mentioned, the tables in Article 2 were updated and the authors offered corrections in response to the editors of Article 5.
+We do not know if additional corrections have been submitted.}
 
-## Comments on Article 2
+## Comments on Article 1
 
-The data published in Article 2 are especially concerning.
+The data published in Article 1 are especially concerning.
 The article information indicates that it was submitted on June 17, 2021.
 Our email correspondence with the authors ended on April 22, 2021.
-Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
-Despite this correspondence, the authors have published an additional article with results that are not only implausible, but highly correlated with the results reported in a previous article.
-We cannot think of a benign explanation for this sequence of events.
+Therefore, Article 1 was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors published an additional article with results that \textcolor{red}{were} not only implausible, but highly correlated with the results reported in a previous article.
+\textcolor{red}{Subsequently, the authors published corrected tables with new standard deviation values.
+The means remained highly correlated with those reported in Article 2, but the new standard deviations were substantially larger than the original values.
+The updated summary statistics are not consistent with the test statistics reported in Article 1.
+Without commenting further on the possible causes of this sequence of events, we note only that they do not inspire confidence in the validity of the results reported in the target articles.}
 

### 2022-01-21 docs/manuscript/manuscript.tex
update: mjc edits

--- 2021-09-29 docs/manuscript/manuscript.tex
@@
   man, donotrepeattitle,floatsintext]{apa7}
-\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
+\title{Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
 \author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
@@
 \hypersetup{
-  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
+  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
   pdfauthor={Brad McKay1 \& Michael J. Carter1},
   pdflang={en-EN},
-  pdfkeywords={Meta-science; GRIMMER; Effect sizes; Perceptual motor learning},
+  pdfkeywords={Metascience; GRIMMER; Effect sizes; Perceptual motor learning},
   hidelinks,
@@
 \makeatother
-\shorttitle{Commentary on Lola \& Tzetzis papers}
-\keywords{Meta-science; GRIMMER; Effect sizes; Perceptual motor learning}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{Metascience; GRIMMER; Effect sizes; Perceptual motor learning}
 \usepackage{lineno}
@@
 
-\note{
-
-\vspace{\baselineskip}
-
-\raggedright Submitted to \emph{Meta-Psychology}.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.
-The full editorial process of all articles under review at \emph{Meta-Psychology} can be found here: \url{https://tinyurl.com/mp-submissions} You will find this preprint by searching for the first author's name.
-
-}
+\shorttitle{Commentary on Lola \& Tzetzis papers}
 
@@
 
-\vspace{-4em} 
+\vspace{-.5cm} 
 \addORCIDlink{Brad McKay}{0000-0002-7408-2323}
@@
 
+\note{
+
+\vspace{\baselineskip}
+
+\raggedright Submitted to \emph{Meta-Psychology}.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+The full editorial process of all articles under review at \emph{Meta-Psychology} can be found here: \url{https://tinyurl.com/mp-submissions}.
+You will find this preprint by searching for the first author's name.
+
+}
+
 \abstract{
@@
 We found the pairwise effect sizes were implausible in all six articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000.
-Impossible statistics were reported in four out of the six articles.
+\textcolor{red}{In contrast, the largest effect size observed in a million simulated experiments with a true effect of $d$ = 3 was $d$ = 6.6.} Impossible statistics were reported in four out of the six articles.
 Reported test statistics and \(\eta^{2}\) values were also implausible, with several \(\eta^{2}\) = .99 and even \(\eta^{2}\) = 1.0 for between-subjects main effects.
@@
 We first became aware of the Lola and Tzetzis (2021) paper when the paper was highlighted in a social media post (Gray, 2021).
-During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed.
+During an initial read through by one of us (BM), a number of reporting and statistical issues were noticed.
 The paper also referenced past research published by these authors.
-Given our cause for concern over the issues found in the Lola and Tzetzis (2021) paper, we deemed it necessary to examine these other papers.
+Given our concerns over the issues found in the Lola and Tzetzis (2021) paper, we deemed it necessary to examine these other papers.
 We remain agnostic to the sources of error in each of these papers.
 Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., \(F\)-statistics) across multiple papers.
-Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions\footnote{We contacted the Editors of the journals that published Articles 1, 3, 4, and 5 on Sept 22 2021.
-The Editors have either indicated their intention to further investigate these issues and/or take corrective actions.}.
+Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions\footnote{On Sept 22 2021, we contacted the journal editors \textcolor{red}{of all articles except} Lola et al.
+(2021) \textcolor{red}{as we were unaware of this article at the time}.
+The Editors indicated their intention to further investigate these issues and/or take corrective actions.
+\textcolor{red}{On Jan 21 2022, we contacted the journal editor regarding the} Lola et al.
+(2021) \textcolor{red}{article.}}.
 Below, we outline our causes for concern and the overarching issues we found across the six articles in question.
@@
 
-We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., In Press; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
-All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
-In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills.
-Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-We will refer to the six articles throughout this paper using the following numbering system:
+\textcolor{red}{We reanalyzed the following six articles by Afroditi Lola and George Tzetzis:}
 
@@
 \def\labelenumi{\arabic{enumi}.}
+\item
+  Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., \& Tzetzis, G.C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+\emph{Journal of Human Sport and Exercise}.
+\url{https://doi.org/10.14198/jhse.2023.181.12}
 \item
@@
 The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions.
-\emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This article is in a journal of a publishing group that has been identified as a potential predatory journal.
-Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS}).
-In fact, the earliest available issue on the journal's webpage is from 2016.}
+\emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This journal has been identified as a potential predatory journal.
+We were unable to find an online version of this article on the journal's webpage and interestingly, the earliest issue on the webpage is from 2016.
+We were only able to find an online version on ResearchGate (\url{https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf\#page=57}).}
 \end{enumerate}
 
-\vspace{6ex}
+\textcolor{red}{In all experiments, the authors investigated the effects of implicit and explicit instructions on perceptual and motor learning.
+All experiments sampled young females who were enrolled in a volleyball camp} (see Table \ref{tab:table1}).
+\textcolor{red}{Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.}
+
+\vspace{3ex}
 
@@
 \midrule
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 1}}\\
-\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 2}}\\
-\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 3}}\\
-\hspace{1em}Lola \& Tzetzis (2020) & 80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 4}}\\
-\hspace{1em}Tzetzis \& Lola (2015) & 60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\textsuperscript{a}\\
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 5}}\\
-\hspace{1em}Lola et al (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
-\addlinespace[0.3em]
-\multicolumn{2}{l}{\textbf{Article 6}}\\
-\hspace{1em}Tzetzis \& Lola (2010) & 48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)\\
+Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
+Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
+Lola \& Tzetzis (2020) & 80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
+Tzetzis \& Lola (2015) & 60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\textsuperscript{a}\\
+Lola et al (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
+Tzetzis \& Lola (2010) & 48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)\\
 \bottomrule
@@
 \item \textit{Note.} 
-\item[a] Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2.
+\item[a] These articles report identical means and standard deviations for the age of their participants despite a different sample size in Lola \& Tzetzis 2020 from Lola \& Tzetzis 2021 and Tzetzis \& Lola 2015, and a different age range in Tzetzis \& Lola 2015 from Lola \& Tzetzis 2020 and 2021
 \end{tablenotes}
@@
 \end{table}
-
-\newpage
 
@@
 Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test.
-The authors also included a high stress test in Articles 1, 2 and 6.
+A high stress test was also included in Lola et al.
+(2021), Lola and Tzetzis (2021), and Tzetzis and Lola (2010).
 
-In Articles 1-4, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy.
-In Articles 5 and 6, a sequential group (see below for description) replaced the analogy group.
+In Lola et al.
+(2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), and Tzetzis and Lola (2015), the groups differed with respect to the type of instruction received: implicit, explicit, or analogy.
+In Lola et al.
+(2012) and Tzetzis and Lola (2010), a sequential group (see below for description) replaced the analogy group.
 All six experiments also included a control group that did not practice the task.
@@
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
-In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale.
-Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Lola et al., 2021; Lola \& Tzetzis, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015), response accuracy (Lola et al., 2021; Lola \& Tzetzis, 2021; Lola et al., 2012; Tzetzis \& Lola, 2015), and motor performance measured on a 4-point scale (Lola \& Tzetzis, 2020).
+In addition, Lola and Tzetzis (2021) and Tzetzis and Lola (2010) included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Lola and Tzetzis (2020) had a measure of self-efficacy using a Likert scale.
+The number of explicit rules recalled was assessed in Lola and Tzetzis (2021), Tzetzis and Lola (2015), Lola et al.
+(2012), and Tzetzis and Lola (2010).
 
@@
 None of the six articles in question included a link to a public repository where the data could be accessed.
-We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
+We first wrote (email sent February 10, 2021) the corresponding author of the Lola and Tzetzis (2021) paper and asked if they would be willing to share the data for this experiment.
 The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A.
 Lola, personal communication, February 12 2021).
-We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent and presumably, all planned analyses had been completed.
-After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6.
+We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from their other articles (i.e., Lola \& Tzetzis, 2020; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015) as these were less recent, and presumably all planned analyses had been completed.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from any of these articles.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola et al.
-(In Press) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
+(2021) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns.
-Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles.
-The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
+The authors did address some specific concerns regarding Lola and Tzetzis (2021), but for the most part only provided more general responses to our concerns.
+The authors admitted that some of the values reported in the other target articles were incorrect, but did not identify which values or articles.
 Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A.
@@
 Cohen's \emph{d} was calculated for each pairwise comparison using the \texttt{compute.es} package in \texttt{R}.
-To provide context, we simulated data from two groups of \emph{n} = 20, consistent with group sizes in Article 3, which had the largest groups among the target articles.
+To provide context, we simulated data from two groups of \emph{n} = 20, consistent with group sizes in Lola and Tzetzis (2020), which had the largest groups among the target articles.
 We ran simulations with true effect sizes of \emph{d} = .8 and \emph{d} = 3 one million times each and report the range of effect sizes observed in those simulations.
@@
 Each of the articles reported only omnibus test statistics and then reported post-hoc analyses with symbols demarcating significant and non-significant differences.
-In response to our expressions of concern, the authors suggested that many of the issues were due to misprints in the articles.
+In response to our expression of concern, the authors suggested that many of the issues were due to misprints in the articles.
 Specifically, they indicated that the reported means and standard deviations in their tables were incorrect and the root of the errors had to be from them outsourcing the formatting of their tables.
@@
 
-Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
+Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity \textcolor{red}{in both the negative and positive direction.
+We calculated absolute values so that all effects were positive}.
 Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion).
@@
 Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).
+\textcolor{red}{In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of} \emph{d} = .19 (McKay et al., 2021), \emph{d} = .54 (McKay, Yantha, Hussien, Carter, \& Ste-Marie, in press), and \emph{d} = .71 (Lohse, Buchanan, \& Miller, 2016).
 
-To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
+To evaluate the maximum plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
 We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation.
@@
 
-\caption{Absolute Cohen's \(d\) estimates from Articles 1-5 plotted on a logarithmic scale.
+\caption{Absolute Cohen's \(d\) estimates from all articles except Tzetzis and Lola (2010) plotted on a logarithmic scale.
+Only data from the original tables in Lola et al.
+(2021) are included.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
+\textcolor{red}{The original table of summary statistics in} Lola et al.
+(2021) \textcolor{red}{indicated that} the smallest post-intervention difference in reaction times was \emph{d} = .64.
+However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.
+The accuracy data also reflected improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35.
+\textcolor{red}{However, a correction to the tables of summary statistics was published that included substantially smaller standard deviations than the original tables.
+While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the reported analyses.}
+
+In Lola and Tzetzis (2021), the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
 The smallest post-intervention effect at any of the three time points was \emph{d} = 286.42, while the largest effect was \emph{d} = 3504.86.
@@
 The motor component data revealed post-treatment effect sizes ranging from \emph{d} = 1.16 to \emph{d} = 13.5.
-In Article 2, the smallest post-intervention difference in reaction times was \emph{d} = .64.
-However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.
-The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35.
 
-In Article 3, post-intervention motor performance effect sizes ranged from \emph{d} = 3.1 to \emph{d} = 20.95.
+In Lola and Tzetzis (2020), post-intervention motor performance effect sizes ranged from \emph{d} = 3.1 to \emph{d} = 20.95.
 Similarly, post-intervention self-efficacy effect sizes ranged from \emph{d} = 1.79 to \emph{d} = 44.46.
-Likewise, in Article 4 post-intervention reaction time effect sizes ranged from \emph{d} = 2.28 to \emph{d} = 35.97.
+Likewise, in Tzetzis and Lola (2015) post-intervention reaction time effect sizes ranged from \emph{d} = 2.28 to \emph{d} = 35.97.
 Continuing this pattern, post-intervention response accuracy effect sizes ranged from \emph{d} = 5.84 to \emph{d} = 29.7.
 
-In Article 5, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from \emph{d} = 2.53 to \emph{d} = 15.50.
+In Lola et al.
+(2012), many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from \emph{d} = 2.53 to \emph{d} = 15.50.
 Nevertheless, all pre-test comparisons were reported as non-significant.
@@
 
-In Article 6, the authors did not report means and standard deviations for most of the analyses.
+In Tzetzis and Lola (2010), the authors did not report means and standard deviations for most of the analyses.
 However, \(\eta^{2}\) effect sizes were reported and these ranged from \(\eta^{2}\) = .52 to \(\eta^{2}\) = .98.
@@
 
-In Article 1, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants.
+In Lola and Tzetzis (2021), the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants.
 Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item.
@@
 
-In Article 3, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
+In Lola and Tzetzis (2020), participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
 Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.\footnote{Independent of the issues we have raised, this approach to measuring motor performance has been shown to be inappropriate and flawed for this type of task (see Fischman, 2015; Hancock, Butler, \& Fischman, 1995; Reeve, Fischman, Christina, \& Cauraugh, 1994 for discussions).} Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
@@
 
-Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+In Lola and Tzetzis (2021), Lola et al.
+(2012), and Tzetzis and Lola (2010), the authors reported means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78).
-The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
-In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
-For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent (\emph{M} = 4.8, \emph{SD} = 1.78).\footnote{You may have noticed that the same mean and standard deviation pairing (\emph{M} = 4.8, \emph{SD} = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences (\emph{n} = 20 for the consistent result and \emph{n} = 12 for the inconsistent one).}
+In Lola and Tzetzis (2021), the mean and standard deviation pairs were GRIMMER inconsistent for all four groups (Implicit: \emph{M} = .73, \emph{SD} = .35; Analogy: \emph{M} = 1.03, \emph{SD} = .25; Explicit: \emph{M} = 4.8, \emph{SD} = .78; Control: \emph{M} = .67, \emph{SD} = .48; \emph{n} = 15).
+In Lola et al.
+(2012), the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78) \textcolor{red}{and the implicit group} (\emph{M} = 2.3, \emph{SD} = 1.3).
+The mean and standard deviation pairs for the remaining \textcolor{red}{two} groups were GRIMMER inconsistent (Sequential: \emph{M} = 4.2, \emph{SD} = 1.07; Control: \emph{M} = 1.8, \emph{SD} = .3; \emph{n} = 15).
+In Tzetzis and Lola (2010), the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample (Sequential: \emph{M} = 4.2, \emph{SD} = 1.07; Implicit: \emph{M} = 2.3, \emph{SD} = 1.3; Control: \emph{M} = 1.4, \emph{SD} = .9; \emph{n} = 12).
+For two of the groups, they were consistent regardless of which method of calculating the standard deviation was used.
+However, the results for the explicit group were GRIMMER inconsistent (\emph{M} = 4.8, \emph{SD} = 1.78).\footnote{You may have noticed that \textcolor{red}{two} of the same mean and standard deviation pairings (\emph{M} = 4.8, \emph{SD} = 1.78 and \emph{M} = 4.2, \emph{SD} = 1.07) were classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences (\emph{n} = 15 and \emph{n} = 12).}
 
@@
 Benchmarks have been suggested for small, medium, and large effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988).
-Importantly, if a main effect of instruction-type results in \(\eta^{2}\) = .99, as was commonly reported in the target articles, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone.
+Importantly, if the main effect of instruction-type results in \(\eta^{2}\) = .99, as was commonly reported in the target articles, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone.
 Such a result is implausible.
 
-Article 1 did not report \(\eta^{2}\) values but had the largest pairwise effects and \emph{F}-statistics of the five articles in question.
-Article 3 reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
+Lola and Tzetzis (2021) did not report \(\eta^{2}\) values but had the largest pairwise effects and \emph{F}-statistics of the five articles in question.
+Lola and Tzetzis (2020) reported \(\eta^{2}\) = .994, \(\eta^{2}\) = .996, and \(\eta^{2}\) = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
 Similarly, variance explained on the self-efficacy measure was \(\eta^{2}\) = .995, \(\eta^{2}\) = .994, \(\eta^{2}\) = .997 for the Time, Group, and Time x Group effects, respectively.
-Article 4 also reported \(\eta^{2}\) = .99 for all three effects on both response time and response accuracy measures.
+Tzetzis and Lola (2015) also reported \(\eta^{2}\) = .99 for all three effects on both response time and response accuracy measures.
 
-Article 5 reported \(\eta^{2}\) = 1.0 for the main effect of Time and the Time x Group interaction, as well as \(\eta^{2}\) = .95 for the main effect of Group on the response time measure.
+Lola et al.
+(2012) reported \(\eta^{2}\) = 1.0 for the main effect of Time and the Time x Group interaction, as well as \(\eta^{2}\) = .95 for the main effect of Group on the response time measure.
 Interestingly, the Time x Group interaction had the smallest reported significant \emph{F}-statistic among the five articles in question.
 With respect to response accuracy, the reported effects were \(\eta^{2}\) = .98, \(\eta^{2}\) = .94, \(\eta^{2}\) = .93 for the Time, Group, and Time x Group analyses, respectively.
-Article 5 reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses, respectively.
+Tzetzis and Lola (2010) reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses, respectively.
 
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
-The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Lola and Tzetzis (2021), Tzetzis and Lola (2015), Lola et al.
+(2012), and Tzetzis and Lola (2010).
+The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Tzetzis and Lola (2010) that reflected the different sample size in this experiment (48 versus 60 in the others).
+Lola and Tzetzis (2021), Lola and Tzetzis (2020), and Tzetzis and Lola (2015) were published over a span of 6 years with reported samples sizes of 60 in Lola and Tzetzis (2021) and Tzetzis and Lola (2015), and 80 in Lola and Tzetzis (2020).
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \ref{tab:table1}).
@@
 
-Article 2 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
-We were unaware of Article 2 when posting the original preprint and it was not included in that version.
-However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Lola et al.
+(2021) was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the preprint version 1.
+We were unaware of this article when posting the original preprint and it was not included in that version.
+However, when we became aware of this paper it was immediately apparent that data reported therein again reflected improbably large effect sizes.
 Further, in comparing the reaction time and accuracy means reported in Lola et al.
-(In Press) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
+(2021) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
 To investigate this similarity further, we conducted a correlation analysis between the two data sets.
 The reaction time means for each group and time point were highly correlated between the two papers, \emph{r} = .99, as were the accuracy means, \emph{r} = .99.
+
+\hypertarget{new-developments-following-september-28-2021-update}{%
+\subsection{New Developments Following September 28, 2021 Update}\label{new-developments-following-september-28-2021-update}}
+
+\textcolor{red}{After contacting the editors for the} Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), and Lola et al.
+(2012) \textcolor{red}{papers on September 22 2021 and updating our preprint on September 28th, at least two important developments transpired.
+First, there was a response from all four editors indicating an intention to investigate the issues we raised.
+The \emph{International Journal of Sport and Exercise Psychology} is so far the only journal that has taken observable action, issuing an Expression of Concern regarding} Lola and Tzetzis (2021) \textcolor{red}{on October 11th, 2021 (https://doi.org/10.1080/1612197X.2021.1991102).
+The current journal editor where} Tzetzis and Lola (2015) \textcolor{red}{was published included us in an email to the authors.
+We were also included in the authors' reply, wherein they again insisted that their analyses and conclusions remained valid.
+They offered an updated manuscript to the journal, but we are unaware of any decisions or further actions.}
+
+\textcolor{red}{The second important development was that the tables in} Lola et al.
+(2021) \textcolor{red}{were updated on October 8th, 2021.
+The new tables made changes to the standard deviation values for both the reaction time and accuracy measures.
+The standard deviations of the reaction time data were adjusted such that the decimal point was shifted one place to the right compared to the original version.
+For example, an original standard deviation of 10.25 is now 102.51.
+The adjustments to the accuracy data now show the original standard deviation values as standard errors and new standard deviations are reported.
+Although the adjustments to the tables reflect corrections to plausible mishaps in the publication process and correcting such errors should be applauded, the new data themselves are problematic when compared to the reported analyses.}
+
+\textcolor{red}{To illustrate the disconnect between the new values and the test statistics in} Lola et al.
+(2021)\textcolor{red}{, we used the \texttt{faux} package in \texttt{R} to simulate data from multivariate normal distributions with the same mean and standard deviation parameters as the original and updated tables.
+We then analyzed the data using the same 4 X 4 mixed ANOVA model reported by the authors and compared the test statistics we observed to those reported in} Lola et al.
+(2021)\textcolor{red}{.
+We tried various correlations between timepoints and chose the value that produced the closest agreement between our analyses and theirs $(r = .8)$.}
+
+\textcolor{red}{Our analysis of simulated reaction time data using the originally reported standard deviations produced $F$-statistics that were more similar to the values reported in} Lola et al.
+(2021) \textcolor{red}{than our analysis based on the updated numbers.
+Using the originally reported figures, we observed an $F$ = 18193 for the main effect of time.
+The authors reported $F$ = 16055 for this analysis.
+Our analysis using the updated statistics resulted in $F$ = 186.
+Similarly, the Time X Group interaction was $F$ = 4242 in} Lola et al.
+(2021)\textcolor{red}{, $F$ = 6208 in our simulation of the original parameters, and $F$ = 54 using the updated numbers.
+The main effect of group was $F$ = 7156 in} Lola et al.
+(2021)\textcolor{red}{, $F$ = 3030 in our simulation of the original parameters, and $F$ = 23 using the updated numbers.
+As is evident, although the updated standard deviations lead to more plausible effect size calculations than the originally reported values, they are not consistent with the analyses reported in the paper.}
+
+\textcolor{red}{We observed similarly discordant $F$-statistics with analyses of simulated accuracy data based on the updated statistics.} Lola et al.
+(2021) \textcolor{red}{reported a main effect of time of $F$ = 3278, we observed $F$ = 2412 when analyzing our simulation of the original parameters, and $F$ = 132 when using the updated parameters.
+The authors reported a Group X Time interaction of $F$ = 657, we found $F$ = 494 with simulations of the original statistics, and $F$ = 27 when using the updated values.
+Finally, the main effect of group was reported as $F$ = 922, we found $F$ = 254 with simulations of the original statistics, and $F$ = 21 when analyzing simulations of the updated data.}
 
@@
 
-We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola et al., In Press; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola et al., 2021; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., In Press; Lola \& Tzetzis, 2021).
-Considering these findings, the conclusions from these articles are not reliable.
+We discovered that the data reported in Lola et al.
+(2021) and Lola and Tzetzis (2021) are very highly correlated despite ostensibly coming from different experiments, samples, and situations.
+\textcolor{red}{Finally, we observed that recently updated tables of summary statistics in} Lola et al.
+(2021) \textcolor{red}{were incompatible with the analyses reported in the paper, while the original summary statistics, which indicated implausible effect sizes, were more compatible with the analyses.} Considering these findings, the conclusions from these articles are not reliable.
+
+The data published in Lola et al.
+(2021) are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, the article was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we had shared our concerns about the previous five articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors published an additional article with results that \textcolor{red}{were} not only implausible, but highly correlated with the results reported in a previous article.
+\textcolor{red}{Subsequently, the authors published corrected tables with new standard deviation values.
+The means remained highly correlated with those reported in} Lola and Tzetzis (2021)\textcolor{red}{, but the new standard deviations were substantially larger than the original values.
+The updated summary statistics are not consistent with the test statistics reported in} Lola et al.
+(2021)\textcolor{red}{.
+Without commenting further on the possible causes of this sequence of events, we note only that they do not inspire confidence in the validity of the results reported in the target articles.}
 
@@
 
-Other irregularities, such as a repeating \emph{F}-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
+Other irregularities, such as a repeating \emph{F}-statistic for all four analyses of explicit rules and the recurring age of participants potentially reflect sloppiness more than expectation.
 Indeed, the authors have already admitted that some values reported in their tables were in error, but failed to identify which values and which articles.
@@
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-28), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer \textcolor{red}{additional} corrections, which they have suggested they intend to do\footnote{\textcolor{red}{There is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
+However, as mentioned, the tables in} Lola et al.
+(2021) \textcolor{red}{were updated and the authors offered some corrections in response to the editors of} Lola et al.
+(2012)\textcolor{red}{.
+We do not know if additional corrections have been submitted.}}, many in the research community may find it difficult to trust any of these results.
 
-\hypertarget{comments-on-article-2}{%
-\subsection{Comments on Article 2}\label{comments-on-article-2}}
-
-The data published in Article 2 are especially concerning.
-The article information indicates that it was submitted on June 17, 2021.
-Our email correspondence with the authors ended on April 22, 2021.
-Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
-Despite this correspondence, the authors have published an additional article with results that are not only implausible, but highly correlated with the results reported in a previous article.
-We cannot think of a benign explanation for this sequence of events.
+\newpage
 
@@
 
-R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
+R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{faux} (Version 1.1.0; DeBruine, 2021), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-faux}{}}%
+DeBruine, L. (2021). \emph{Faux: Simulation for factorial designs}. Zenodo. \url{https://doi.org/10.5281/zenodo.2669586}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-lemon}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lohse2016}{}}%
+Lohse, K., Buchanan, T., \& Miller, M.
+(2016).
+Underpowered and overworked: Problems with data analysis in motor learning studies.
+\emph{Journal of Motor Learning and Development}, \emph{4}(1), 37--58.
+\url{https://doi.org/10.1123/jmld.2015-0010}
+
 \leavevmode\vadjust pre{\hypertarget{ref-lola2021b}{}}%
@@
 \url{https://doi.org/10.1002/ejsp.2752}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2021b}{}}%
+McKay, B., Hussien, J., Vinh, M.-A., Mir-Orefice, A., Brooks, H., \& Ste-Marie, D.
+M.
+(2021).
+\emph{Meta-analysis of reduced relative feedback frequency effect on motor learning and performance}.
+\url{https://doi.org/10.31234/osf.io/v2cp7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mckay2021a}{}}%
+McKay, B., Yantha, Z.
+D., Hussien, J., Carter, M.
+J., \& Ste-Marie, D.
+M.
+(in press).
+Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value.
+\emph{Meta-Psychology}.
+\url{https://doi.org/10.31234/osf.io/8d3nb}
 

### 2022-01-21 docs/manuscript/manuscript.Rmd

@@
 ---
-title             : "Data irregularities across six implicit learning articles: Comments on @lola2021, @lola2021b, @lola2020, @tzetzis2015, @lola2012, and @tzetzis2010"
+title             : "Data irregularities across six implicit learning articles: Comments on @lola2021b, @lola2021, @lola2020, @tzetzis2015, @lola2012, and @tzetzis2010"
 
@@
 Participate in open peer review by commenting through hypothes.is directly on this preprint.
-The full editorial process of all articles under review at *Meta-Psychology* can be found here: https://tinyurl.com/mp-submissions You will find this preprint by searching for the first author's name.
+The full editorial process of all articles under review at *Meta-Psychology* can be found here: https://tinyurl.com/mp-submissions.
+You will find this preprint by searching for the first author's name.
 
@@
   \addORCIDlink{Brad McKay}{0000-0002-7408-2323}
-
-  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+  \newline \indent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
 
@@
 We found the pairwise effect sizes were implausible in all six articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000.
-\textcolor{red}{In contrast, the largest effect size observed in a million simulated experiments with a true effect of} *d* \textcolor{red}{= 3 was} *d*\textcolor{red}{ = 6.6.} Impossible statistics were reported in four out of the six articles.
+\textcolor{red}{In contrast, the largest effect size observed in a million simulated experiments with a true effect of $d$ = 3 was $d$ = 6.6.} Impossible statistics were reported in four out of the six articles.
 Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects.
@@
 We first became aware of the @lola2021 paper when the paper was highlighted in a social media post [@gray2021].
-During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed.
+During an initial read through by one of us (BM), a number of reporting and statistical issues were noticed.
 The paper also referenced past research published by these authors.
-Given our cause for concern over the issues found in the @lola2021 paper, we deemed it necessary to examine these other papers.
+Given our concerns over the issues found in the @lola2021 paper, we deemed it necessary to examine these other papers.
 We remain agnostic to the sources of error in each of these papers.
@@
 [^1]: One of the six papers had a third author and one had a third and fourth author.
-[^2]: We contacted the Editors of the journals that published Articles 1, 3, 4, and 5 on Sept 22 2021.
-The Editors have either indicated their intention to further investigate these issues and/or take corrective actions.
+[^2]: On Sept 22 2021, we contacted the journal editors \textcolor{red}{of all articles except} @lola2021b \textcolor{red}{as we were unaware of this article at the time}.
+The Editors indicated their intention to further investigate these issues and/or take corrective actions.
+\textcolor{red}{On Jan 21 2022, we contacted the journal editor regarding the} @lola2021b \textcolor{red}{article.}
 
@@
 
-We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague [@lola2012; @lola2020; @lola2021; @lola2021b; @tzetzis2010; @tzetzis2015].
-All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)).
-In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills.
-Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-We will refer to the six articles throughout this paper using the following numbering system:
+\textcolor{red}{We reanalyzed the following six articles by Afroditi Lola and George Tzetzis:}
 
@@
 
-[^3]: This article is in a journal of a publishing group that has been identified as a potential predatory journal.
-Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf#page=57).
-In fact, the earliest available issue on the journal's webpage is from 2016.
+[^3]: This journal has been identified as a potential predatory journal.
+We were unable to find an online version of this article on the journal's webpage and interestingly, the earliest issue on the webpage is from 2016.
+We were only able to find an online version on ResearchGate (https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf#page=57).
 
-\vspace{6ex}
+\textcolor{red}{In all experiments, the authors investigated the effects of implicit and explicit instructions on perceptual and motor learning.
+All experiments sampled young females who were enrolled in a volleyball camp} (see Table \@ref(tab:table1)).
+\textcolor{red}{Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.}
+
+\vspace{3ex}
 
@@
     booktabs = TRUE,
+    linesep = "",
     escape = FALSE,
@@
                 font_size = 11) %>%
-  pack_rows("Article 1", 1, 1) %>%
-  pack_rows("Article 2", 2, 2) %>%
-  pack_rows("Article 3", 3, 3) %>%
-  pack_rows("Article 4", 4, 4) %>%
-  pack_rows("Article 5", 5, 5) %>%
-  pack_rows("Article 6", 6, 6) %>%
-  footnote(alphabet = c("Articles 2, 3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 3 from Articles 2 and 4, and a different age range in Article 4 from Articles 2 and 3."),
+  footnote(alphabet = c("These articles report identical means and standard deviations for the age of their participants despite a different sample size in Lola & Tzetzis 2020 from Lola & Tzetzis 2021 and Tzetzis & Lola 2015, and a different age range in Tzetzis & Lola 2015 from Lola & Tzetzis 2020 and 2021"),
            alphabet_title = "Note.",
@@
 ```
-
-\newpage
 
@@
 Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test.
-The authors also included a high stress test in Articles 1 [@lola2021b], 2 [@lola2021] and 6 [@tzetzis2010}.
+A high stress test was also included in @lola2021b, @lola2021, and @tzetzis2010.
 
-In Articles 1-4, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy.
-In Articles 5 and 6, a sequential group (see below for description) replaced the analogy group.
+In @lola2021b, @lola2021, @lola2020, and @tzetzis2015, the groups differed with respect to the type of instruction received: implicit, explicit, or analogy.
+In @lola2012 and @tzetzis2010, a sequential group (see below for description) replaced the analogy group.
 All six experiments also included a control group that did not practice the task.
@@
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and \textcolor{red}{6}), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
-In addition, Articles 2 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 3 had a measure of self-efficacy using a Likert scale.
-Articles 2, 4, 5, and 6 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time [@lola2021b; @lola2021; @tzetzis2015; @lola2012; @tzetzis2010], response accuracy [@lola2021b; @lola2021; @tzetzis2015; @lola2012], and motor performance measured on a 4-point scale [@lola2020].
+In addition, @lola2021 and @tzetzis2010 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and @lola2020 had a measure of self-efficacy using a Likert scale.
+The number of explicit rules recalled was assessed in @lola2021, @tzetzis2015, @lola2012, and @tzetzis2010.
 
@@
 None of the six articles in question included a link to a public repository where the data could be accessed.
-We first wrote (email sent February 10, 2021) the corresponding author for Article 2 and asked if they would be willing to share the data for this experiment.
+We first wrote (email sent February 10, 2021) the corresponding author of the @lola2021 paper and asked if they would be willing to share the data for this experiment.
 The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A.
 Lola, personal communication, February 12 2021).
-We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent, and presumably all planned analyses had been completed.
-After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6.
+We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from their other articles [i.e., @lola2020; @tzetzis2015; @lola2012; @tzetzis2010] as these were less recent, and presumably all planned analyses had been completed.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from any of these articles.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 2, but for the most part only provided more general responses to our concerns.
-The authors admitted that some of the values reported in the other target articles were incorrect but did not identify which values or articles.
+The authors did address some specific concerns regarding @lola2021, but for the most part only provided more general responses to our concerns.
+The authors admitted that some of the values reported in the other target articles were incorrect, but did not identify which values or articles.
 Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A.
@@
 Cohen's *d* was calculated for each pairwise comparison using the `compute.es` package in `R`.
-To provide context, we simulated data from two groups of *n* = 20, consistent with group sizes in Article 3, which had the largest groups among the target articles.
+To provide context, we simulated data from two groups of *n* = 20, consistent with group sizes in @lola2020, which had the largest groups among the target articles.
 We ran simulations with true effect sizes of *d* = .8 and *d* = 3 one million times each and report the range of effect sizes observed in those simulations.
@@
 Conventional benchmarks for small, medium, and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions].
-Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].\textcolor{red}{In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of} *d* = .19 [@mckay2021b], *d*= .54 [@mckay2021a], and *d* = .71 [@lohse2016].
+Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].
+\textcolor{red}{In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of} *d* = .19 [@mckay2021b], *d* = .54 [@mckay2021a], and *d* = .71 [@lohse2016].
 
-To evaluate the maximum plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
+To evaluate the maximum plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
 We set the true effect size at *d* = .8, the conventional benchmark for a "large" treatment effect, in the first simulation.
@@
 
-(ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-5 plotted on a logarithmic scale.
-Only data from the original tables in Article 2 are included.
+(ref:fig1-caption) Absolute Cohen's $d$ estimates from all articles except @tzetzis2010 plotted on a logarithmic scale.
+Only data from the original tables in @lola2021b are included.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
-\textcolor{red}{The original table of summary statistics in Article 1 indicated that} the smallest post-intervention difference in reaction times was *d* = .64.
+\textcolor{red}{The original table of summary statistics in} @lola2021b \textcolor{red}{indicated that} the smallest post-intervention difference in reaction times was *d* = .64.
 However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.
@@
 \textcolor{red}{However, a correction to the tables of summary statistics was published that included substantially smaller standard deviations than the original tables.
-While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the analyses reported in Article 2.}
+While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the reported analyses.}
 
-In Article 2, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
+In @lola2021, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
 The smallest post-intervention effect at any of the three time points was *d* = 286.42, while the largest effect was *d* = 3504.86.
@@
 
-In Article 3, post-intervention motor performance effect sizes ranged from *d* = 3.1 to *d* = 20.95.
+In @lola2020, post-intervention motor performance effect sizes ranged from *d* = 3.1 to *d* = 20.95.
 Similarly, post-intervention self-efficacy effect sizes ranged from *d* = 1.79 to *d* = 44.46.
-Likewise, in Article 4 post-intervention reaction time effect sizes ranged from *d* = 2.28 to *d* = 35.97.
+Likewise, in @tzetzis2015 post-intervention reaction time effect sizes ranged from *d* = 2.28 to *d* = 35.97.
 Continuing this pattern, post-intervention response accuracy effect sizes ranged from *d* = 5.84 to *d* = 29.7.
 
-In Article 5, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from *d* = 2.53 to *d* = 15.50.
+In @lola2012, many response accuracy effect sizes were implausibly large beginning at pre-test, wherein effects ranged from *d* = 2.53 to *d* = 15.50.
 Nevertheless, all pre-test comparisons were reported as non-significant.
@@
 
-In Article 6, the authors did not report means and standard deviations for most of the analyses.
+In @tzetzis2010, the authors did not report means and standard deviations for most of the analyses.
 However, $\eta^{2}$ effect sizes were reported and these ranged from $\eta^{2}$ = .52 to $\eta^{2}$ = .98.
@@
 
-In Article 2, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants.
+In @lola2021, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants.
 Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item.
@@
 
-In Article 3, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
+In @lola2020, participants were asked to receive a served volleyball and pass it to a target consisting of three concentric circles.
 Motor performance was measured based on where the pass landed, with three points awarded for a pass to the central circle on the target, two points for the middle circle, one point for the outermost circle, and zero points for a pass that missed the target.[^5] Results were presented as average performance per trial and the analogy group was reported to have a mean score of 3.00 at retention (a perfect score) but with a standard deviation of .09.
@@
 
-Articles 2, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+In @lola2021, @lola2012, and @tzetzis2010, the authors reported means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-In Article 2, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups (I: *M* = .73, *SD* = .35; A: *M* = 1.03, *SD* = .25; E: *M* = 4.8, *SD* = .78; C: *M* = .67, *SD* = .48; *n* = 15).
-In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78) \textcolor{red}{and the implicit group} (*M* = 2.3, *SD* = 1.3).
-The mean and standard deviation pairs for the remaining \textcolor{red}{two} groups were GRIMMER inconsistent (S: *M* = 4.2, *SD* = 1.07; C: *M* = 1.8, *SD* = .3; *n* = 15).
-In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample (S: *M* = 4.2, *SD* = 1.07; I: *M* = 2.3, *SD* = 1.3; C: *M* = 1.4, *SD* = .9; *n* = 12).
-For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
+In @lola2021, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups (Implicit: *M* = .73, *SD* = .35; Analogy: *M* = 1.03, *SD* = .25; Explicit: *M* = 4.8, *SD* = .78; Control: *M* = .67, *SD* = .48; *n* = 15).
+In @lola2012, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78) \textcolor{red}{and the implicit group} (*M* = 2.3, *SD* = 1.3).
+The mean and standard deviation pairs for the remaining \textcolor{red}{two} groups were GRIMMER inconsistent (Sequential: *M* = 4.2, *SD* = 1.07; Control: *M* = 1.8, *SD* = .3; *n* = 15).
+In @tzetzis2010, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample (Sequential: *M* = 4.2, *SD* = 1.07; Implicit: *M* = 2.3, *SD* = 1.3; Control: *M* = 1.4, *SD* = .9; *n* = 12).
+For two of the groups, they were consistent regardless of which method of calculating the standard deviation was used.
 However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^6]
 
-[^6]: You may have noticed that \textcolor{red}{two} of the same mean and standard deviation pairings (*M* = 4.8, *SD* = 1.78; *M* = 4.2, *SD* = 1.07) were classified as GRIMMER inconsistent for one paper and consistent for the other.
+[^6]: You may have noticed that \textcolor{red}{two} of the same mean and standard deviation pairings (*M* = 4.8, *SD* = 1.78 and *M* = 4.2, *SD* = 1.07) were classified as GRIMMER inconsistent for one paper and consistent for the other.
 This is because of sample size differences (*n* = 15 and *n* = 12).
@@
 
-Article 2 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question.
-Article 3 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
+@lola2021 did not report $\eta^{2}$ values but had the largest pairwise effects and *F*-statistics of the five articles in question.
+@lola2020 reported $\eta^{2}$ = .994, $\eta^{2}$ = .996, and $\eta^{2}$ = .996 for the Time, Group, and Time x Group effects on motor performance, respectively.
 Similarly, variance explained on the self-efficacy measure was $\eta^{2}$ = .995, $\eta^{2}$ = .994, $\eta^{2}$ = .997 for the Time, Group, and Time x Group effects, respectively.
-Article 4 also reported $\eta^{2}$ = .99 for all three effects on both response time and response accuracy measures.
+@tzetzis2015 also reported $\eta^{2}$ = .99 for all three effects on both response time and response accuracy measures.
 
-Article 5 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure.
+@lola2012 reported $\eta^{2}$ = 1.0 for the main effect of Time and the Time x Group interaction, as well as $\eta^{2}$ = .95 for the main effect of Group on the response time measure.
 Interestingly, the Time x Group interaction had the smallest reported significant *F*-statistic among the five articles in question.
 With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses, respectively.
-Article \textcolor{red}{6} reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.
+@tzetzis2010 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.
 
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 2, 4, 5, and 6.
-The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 2, 4, and 5).
-Articles 2, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 2 and 4, and 80 in Article 3.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in @lola2021, @tzetzis2015, @lola2012, and @tzetzis2010.
+The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in @tzetzis2010 that reflected the different sample size in this experiment (48 versus 60 in the others).
+@lola2021, @lola2020, and @tzetzis2015 were published over a span of 6 years with reported samples sizes of 60 in @lola2021 and @tzetzis2015, and 80 in @lola2020.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \@ref(tab:table1)).
@@
 
-Article 1 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
-We were unaware of Article 1 when posting the original preprint and it was not included in that version.
-However, when we became aware of Article 1 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+@lola2021b was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the preprint version 1.
+We were unaware of this article when posting the original preprint and it was not included in that version.
+However, when we became aware of this paper it was immediately apparent that data reported therein again reflected improbably large effect sizes.
 Further, in comparing the reaction time and accuracy means reported in @lola2021b to those reported in @lola2021, it appeared the data shared a remarkably similar pattern.
@@
 
-\textcolor{red}{After contacting the editors of Articles 2, 3, 4, and 5 on September 22nd and updating the preprint of this paper on September 28th, at least two important developments transpired.
+\textcolor{red}{After contacting the editors for the} @lola2021, @lola2020, @tzetzis2015, and @lola2012 \textcolor{red}{papers on September 22 2021 and updating our preprint on September 28th, at least two important developments transpired.
 First, there was a response from all four editors indicating an intention to investigate the issues we raised.
-The} *International Journal of Sport and Exercise Psychology* \textcolor{red}{is so far the only journal that has taken observable action, issuing an Expression of Concern regarding Article 2 on October 11th, 2021.
-The editor of Article 4 included us in an email to the authors and we were included in their reply, wherein they again insisted that their analyses and conclusions remained valid.
-They offered an updated manuscript to the journal but as far as we are aware no action has since been taken.}
+The \emph{International Journal of Sport and Exercise Psychology} is so far the only journal that has taken observable action, issuing an Expression of Concern regarding} @lola2021 \textcolor{red}{on October 11th, 2021 (https://doi.org/10.1080/1612197X.2021.1991102).
+The current journal editor where} @tzetzis2015 \textcolor{red}{was published included us in an email to the authors.
+We were also included in the authors' reply, wherein they again insisted that their analyses and conclusions remained valid.
+They offered an updated manuscript to the journal, but we are unaware of any decisions or further actions.}
 
-\textcolor{red}{The second important development was that the tables in Article 1 were updated on October 8th, 2021.
+\textcolor{red}{The second important development was that the tables in} @lola2021b \textcolor{red}{were updated on October 8th, 2021.
 The new tables made changes to the standard deviation values for both the reaction time and accuracy measures.
@@
 
-\textcolor{red}{To illustrate the disconnect between the new values and the test statistics in Article 1, we used the `faux` package in `R` to simulate data from multivariate normal distributions with the same mean and standard deviation parameters as the original and updated tables.
-We then analyzed the data using the same 4 X 4 mixed ANOVA model reported by the authors and compared the test statistics we observed to those reported in Article 1.
-We tried various correlations between timepoints and chose the value that produced the closest agreement between our analyses and theirs} (*r* = .8).
+\textcolor{red}{To illustrate the disconnect between the new values and the test statistics in} @lola2021b\textcolor{red}{, we used the \texttt{faux} package in \texttt{R} to simulate data from multivariate normal distributions with the same mean and standard deviation parameters as the original and updated tables.
+We then analyzed the data using the same 4 X 4 mixed ANOVA model reported by the authors and compared the test statistics we observed to those reported in} @lola2021b\textcolor{red}{.
+We tried various correlations between timepoints and chose the value that produced the closest agreement between our analyses and theirs $(r = .8)$.}
 
-\textcolor{red}{Our analysis of simulated reaction time data using the originally reported standard deviations produced} *F*-statistics \textcolor{red}{that were more similar to the values reported in Article 1 than our analysis based on the updated numbers.
-Using the originally reported figures, we observed an} *F* = 18,193 \textcolor{red}{for the main effect of time.
-The authors reported} *F* = 16,055 \textcolor{red}{for this analysis.
-Our analysis using the updated statistics resulted in} *F* = 186.
-\textcolor{red}{Similarly, the Time X Group interaction was} *F* = 4242 \textcolor{red}{in Article 1,} *F* = 6208 \textcolor{red}{in our simulation of the original parameters, and} *F* = 54 \textcolor{red}{using the updated numbers.
-The main effect of group was} *F* = 7156 \textcolor{red}{in Article 1,} *F* = 3030 \textcolor{red}{in our simulation of the original parameters, and} *F* = 23 \textcolor{red}{using the updated numbers.
+\textcolor{red}{Our analysis of simulated reaction time data using the originally reported standard deviations produced $F$-statistics that were more similar to the values reported in} @lola2021b \textcolor{red}{than our analysis based on the updated numbers.
+Using the originally reported figures, we observed an $F$ = 18193 for the main effect of time.
+The authors reported $F$ = 16055 for this analysis.
+Our analysis using the updated statistics resulted in $F$ = 186.
+Similarly, the Time X Group interaction was $F$ = 4242 in} @lola2021b\textcolor{red}{, $F$ = 6208 in our simulation of the original parameters, and $F$ = 54 using the updated numbers.
+The main effect of group was $F$ = 7156 in} @lola2021b\textcolor{red}{, $F$ = 3030 in our simulation of the original parameters, and $F$ = 23 using the updated numbers.
 As is evident, although the updated standard deviations lead to more plausible effect size calculations than the originally reported values, they are not consistent with the analyses reported in the paper.}
 
-\textcolor{red}{We observed similarly discordant *F*-statistics with analyses of simulated accuracy data based on the updated statistics.
-Article 1 reported a main effect of time of} *F* = 3278,\textcolor{red}{ we observed} *F* = 2412 \textcolor{red}{when analyzing our simulation of the original parameters, and} *F* = 132\textcolor{red}{ when using the updated parameters.
-The authors reported a Group X Time interaction of} *F* = 657, \textcolor{red}{we found} *F* = 494 \textcolor{red}{with simulations of the original statistics, and} *F* = 27 \textcolor{red}{when using the updated values.
-Finally, the main effect of group was reported as} *F* = 922, \textcolor{red}{we found} *F* = 254 \textcolor{red}{with simulations of the original statistics, and} *F* = 21 \textcolor{red}{when analyzing simulations of the updated data.}
+\textcolor{red}{We observed similarly discordant $F$-statistics with analyses of simulated accuracy data based on the updated statistics.} @lola2021b \textcolor{red}{reported a main effect of time of $F$ = 3278, we observed $F$ = 2412 when analyzing our simulation of the original parameters, and $F$ = 132 when using the updated parameters.
+The authors reported a Group X Time interaction of $F$ = 657, we found $F$ = 494 with simulations of the original statistics, and $F$ = 27 when using the updated values.
+Finally, the main effect of group was reported as $F$ = 922, we found $F$ = 254 with simulations of the original statistics, and $F$ = 21 when analyzing simulations of the updated data.}
 
@@
 
-We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning [@lola2012; @lola2020; @lola2021;@lola2021b; @tzetzis2010; @tzetzis2015].
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning [@lola2021b; @lola2021; @lola2020; @tzetzis2015; @lola2012; @tzetzis2010].
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated $\eta^{2}$ values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-We discovered that the data reported in two articles are very highly correlated despite ostensibly coming from different experiments, samples, and situations [@lola2021; @lola2021b].
-\textcolor{red}{Finally, we observed that recently updated tables of summary statistics in Article 1 were incompatible with the analyses reported in the paper, while the original summary statistics, which indicate implausible effect sizes, were more compatible with the analyses.} Considering these findings, the conclusions from these articles are not reliable.
+We discovered that the data reported in @lola2021b and @lola2021 are very highly correlated despite ostensibly coming from different experiments, samples, and situations.
+\textcolor{red}{Finally, we observed that recently updated tables of summary statistics in} @lola2021b \textcolor{red}{were incompatible with the analyses reported in the paper, while the original summary statistics, which indicated implausible effect sizes, were more compatible with the analyses.} Considering these findings, the conclusions from these articles are not reliable.
+
+The data published in @lola2021b are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, the article was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we had shared our concerns about the previous five articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors published an additional article with results that \textcolor{red}{were} not only implausible, but highly correlated with the results reported in a previous article.
+\textcolor{red}{Subsequently, the authors published corrected tables with new standard deviation values.
+The means remained highly correlated with those reported in} @lola2021\textcolor{red}{, but the new standard deviations were substantially larger than the original values.
+The updated summary statistics are not consistent with the test statistics reported in} @lola2021b\textcolor{red}{.
+Without commenting further on the possible causes of this sequence of events, we note only that they do not inspire confidence in the validity of the results reported in the target articles.}
 
@@
 
-Other irregularities, such as a repeating *F*-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation.
+Other irregularities, such as a repeating *F*-statistic for all four analyses of explicit rules and the recurring age of participants potentially reflect sloppiness more than expectation.
 Indeed, the authors have already admitted that some values reported in their tables were in error, but failed to identify which values and which articles.
@@
 [^7]: \textcolor{red}{There is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
-However, as mentioned, the tables in Article 2 were updated and the authors offered corrections in response to the editors of Article 5.
+However, as mentioned, the tables in} @lola2021b \textcolor{red}{were updated and the authors offered some corrections in response to the editors of} @lola2012\textcolor{red}{.
 We do not know if additional corrections have been submitted.}
 
-## Comments on Article 1
-
-The data published in Article 1 are especially concerning.
-The article information indicates that it was submitted on June 17, 2021.
-Our email correspondence with the authors ended on April 22, 2021.
-Therefore, Article 1 was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
-Despite this correspondence, the authors published an additional article with results that \textcolor{red}{were} not only implausible, but highly correlated with the results reported in a previous article.
-\textcolor{red}{Subsequently, the authors published corrected tables with new standard deviation values.
-The means remained highly correlated with those reported in Article 2, but the new standard deviations were substantially larger than the original values.
-The updated summary statistics are not consistent with the test statistics reported in Article 1.
-Without commenting further on the possible causes of this sequence of events, we note only that they do not inspire confidence in the validity of the results reported in the target articles.}
+\newpage
 

### 2022-01-27 docs/manuscript/manuscript.Rmd

--- 2021-09-28 docs/manuscript/manuscript.Rmd
@@
 
+note: |
+  \vspace{10ex}
+  In Press at *Meta-Psychology*
+
 authornote: |
+  \vspace{-.5cm} 
   \addORCIDlink{Brad McKay}{0000-0002-7408-2323}
-
-  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
+  \newline \indent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
 
@@
 We found the pairwise effect sizes were implausible in all six articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000.
+In contrast, the largest effect size observed in a million simulated experiments with a true effect of $d$ = 3 was $d$ = 6.6.
 Impossible statistics were reported in four out of the six articles.
@@
 [^1]: One of the six papers had a third author and one had a third and fourth author.
-[^2]: We contacted the Editors of the journals that published Articles 1, 3, 4, and 5 on Sept 22 2021.
-The Editors have either indicated their intention to further investigate these issues and/or take corrective actions.
+[^2]: We contacted the journal editors for Articles 2-6 on Sept 22 2021 and for Article 1 on Jan 21 2022.
+All editors indicated their intention to further investigate these issues and/or take corrective actions.
 
@@
 
-We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague [@lola2012; @lola2020; @lola2021; @lola2021b; @tzetzis2010; @tzetzis2015].
-All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)).
-In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills.
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleagues.
+In all experiments, the authors investigated the effects of implicit and explicit instructions on perceptual and motor learning.
+All experiments sampled young females who were enrolled in a volleyball camp (see Table \@ref(tab:table1)).
 Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-We will refer to the six articles throughout this paper using the following numbering system:
+We will refer to the six articles throughout this paper using the following numbering system based on reverse chronological order:
 
 1.
+Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., & Tzetzis, G.C.
+(2021).
+The influence of analogies on the development of selective attention in novices in normal or stressful conditions.
+*Journal of Human Sport and Exercise*.
+https://doi.org/10.14198/jhse.2023.181.12
+
+2.
 Lola, A.C., & Tzetzis, G.C.
@@
 
-[^3]: This article is in a journal of a publishing group that has been identified as a potential predatory journal.
-Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS).
-In fact, the earliest available issue on the journal's webpage is from 2016.
+[^3]: This journal has been identified as a potential predatory journal.
+We were unable to find an online version of this article on the journal's webpage and interestingly, the earliest issue on the webpage is from 2016.
+We were only able to find an online version on ResearchGate (https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf#page=57).
 
-\vspace{6ex}
+\vspace{5ex}
 
@@
 table_1 <- tibble::tibble(
-  c1 = c("Lola \\& Tzetzis (2021)",
-         "Lola et al (2021)",
+  c1 = c("Lola et al. (2021)",
+         "Lola \\& Tzetzis (2021)",
          "Lola \\& Tzetzis (2020)",
          "Tzetzis \\& Lola (2015)",
-         "Lola et al (2012)",
+         "Lola et al. (2012)",
          "Tzetzis \\& Lola (2010)"),
-  c2 = c("60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
-         "60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)",
+  c2 = c("60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)",
+         "60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
          "80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\\textsuperscript{a}",
@@
   pack_rows("Article 6", 6, 6) %>%
-  footnote(alphabet = c("Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2."),
+  footnote(alphabet = c("Articles 2-4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 3 from Articles 2 and 4, and a different age range in Article 4 from Articles 2 and 3."),
            alphabet_title = "Note.",
@@
 Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test.
-The authors also included a high stress test in Articles 1, 2 and 6.
+A high stress test was also included in Articles 1, 2, and 6.
 
@@
 This advantage was also predicted to be greater when testing was conducted in a high stress situation.
-In @lola2021 for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team.
+In Article 2 for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team.
 Further, it was predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
-In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 3 had a measure of self-efficacy using a Likert scale.
-Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 6), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
+In addition, Articles 2 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 [@tsorbatzoudis1998], and Article 3 had a measure of self-efficacy using a Likert scale.
+The number of explicit rules recalled was assessed in Articles 2, 4, 5, and 6.
 
@@
 None of the six articles in question included a link to a public repository where the data could be accessed.
-We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment.
+We first wrote (email sent February 10, 2021) the corresponding author of Article 2 and asked if they would be willing to share the data for this experiment.
 The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A.
 Lola, personal communication, February 12 2021).
-We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent and presumably, all planned analyses had been completed.
-After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6.
+We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from any of Articles 3 to 6 as these were less recent, and presumably all planned analyses had been completed.
+After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from any of these articles.
 The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A.
@@
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns.
-Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles.
-The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
+The authors did address some specific concerns regarding Article 2, but for the most part only provided more general responses to our concerns.
+The authors admitted that some of the values reported in the other target articles were incorrect, but did not identify which values or articles.
 Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A.
@@
 
-[^4]: Excluding @lola2021b article as it had not yet been accepted for publication.
+[^4]: Excluding Article 1 [@lola2021b] because we were not aware of it at the time as it had not yet been accepted for publication.
 
@@
 
-Cohen's *d* is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
+Cohen's *d* is used to describe the standardized mean difference of an effect and values can range between 0 and infinity in both the negative and positive direction.
+We calculated absolute values so that all effects were positive.
 Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion].
@@
 Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].
+In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of *d* = .19 [@mckay2021b], *d* = .54 [@mckay2021a], and *d* = .71 [@lohse2016].
 
-To evaluate the maximum range of plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
+To evaluate the maximum plausible Cohen's *d* statistics one might encounter from experiments similar to those reported in the target articles, we conducted two simulations that each consisted of one million experiments (see Figure \@ref(fig:fig1)).
 We set the true effect size at *d* = .8, the conventional benchmark for a "large" treatment effect, in the first simulation.
@@
 
-(ref:fig1-caption) Absolute Cohen's $d$ estimates from Articles 1-5 plotted on a logarithmic scale.
+(ref:fig1-caption) Absolute Cohen's $d$ estimates from all articles except Article 6 plotted on a logarithmic scale.
+Only data from the original tables in Article 1 are included.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
+The original table of summary statistics in Article 1 indicated that the smallest post-intervention difference in reaction times was *d* = .64.
+However, all other effects were larger than *d* = 8.7 and the largest effect was *d* = 41.
+The accuracy data also reflected improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than *d* = 5 and a largest effect of *d* = 13.35.
+However, a correction to the tables of summary statistics was published that included substantially smaller standard deviations than the original tables.
+While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the reported analyses.
+
+In Article 2, the smallest pre-test difference for reaction time was *d* = 1.29 and the largest pre-test difference was *d* = 35.32---although none of the groups were reported as significantly different in the article.
 The smallest post-intervention effect at any of the three time points was *d* = 286.42, while the largest effect was *d* = 3504.86.
@@
 
-Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+In Articles 2, 5, and 6, the authors reported means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78).
-The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
-In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
-For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
+In Article 2, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups (Implicit: *M* = .73, *SD* = .35; Analogy: *M* = 1.03, *SD* = .25; Explicit: *M* = 4.8, *SD* = .78; Control: *M* = .67, *SD* = .48; *n* = 15).
+In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (*M* = 4.8, *SD* = 1.78) and the implicit group (*M* = 2.3, *SD* = 1.3).
+The mean and standard deviation pairs for the remaining two groups were GRIMMER inconsistent (Sequential: *M* = 4.2, *SD* = 1.07; Control: *M* = 1.8, *SD* = .3; *n* = 15).
+In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample (Sequential: *M* = 4.2, *SD* = 1.07; Implicit: *M* = 2.3, *SD* = 1.3; Control: *M* = 1.4, *SD* = .9; *n* = 12).
+For two of the groups, they were consistent regardless of which method of calculating the standard deviation was used.
 However, the results for the explicit group were GRIMMER inconsistent (*M* = 4.8, *SD* = 1.78).[^6]
 
-[^6]: You may have noticed that the same mean and standard deviation pairing (*M* = 4.8, *SD* = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences (*n* = 20 for the consistent result and *n* = 12 for the inconsistent one).
+[^6]: You may have noticed that two of the same mean and standard deviation pairings (*M* = 4.8, *SD* = 1.78 and *M* = 4.2, *SD* = 1.07) were classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences (*n* = 15 and *n* = 12).
 
@@
 With respect to response accuracy, the reported effects were $\eta^{2}$ = .98, $\eta^{2}$ = .94, $\eta^{2}$ = .93 for the Time, Group, and Time x Group analyses, respectively.
-Article 5 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.
+Article 6 reported $\eta^{2}$ = .66, $\eta^{2}$ = .52, $\eta^{2}$ = .72 for the Time, Group, and Time x Group analyses, respectively.
 
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
-The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 2, 4, 5, and 6.
+The reported test statistic in these four articles was *F* = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in the others).
+Articles 2-4 were published over a span of 6 years with reported samples sizes of 60 in Articles 2 and 4, and 80 in Article 3.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \@ref(tab:table1)).
@@
 
-Article 2 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
-We were unaware of Article 2 when posting the original preprint and it was not included in that version.
-However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
-Further, in comparing the reaction time and accuracy means reported in @lola2021b to those reported in @lola2021, it appeared the data shared a remarkably similar pattern.
+Article 1 was submitted to the *Journal of Human Sport and Exercise* following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted our preprint (Version 1).
+We were unaware of this article when posting the original preprint and it was not included in that version.
+However, when we became aware of this paper it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Further, in comparing the reaction time and accuracy means reported in Article 1 to those reported in Article 2, it appeared the data shared a remarkably similar pattern.
 To investigate this similarity further, we conducted a correlation analysis between the two data sets.
@@
 
+## New Developments Following September 28, 2021 Update
+
+After contacting the editors for Articles 2-5 on September 22 2021 and updating our preprint on September 28th, at least two important developments transpired.
+First, there was a response from all four editors indicating an intention to investigate the issues we raised.
+The *International Journal of Sport and Exercise Psychology* is so far the only journal that has taken observable action, issuing an Expression of Concern regarding Article 2 on October 11th, 2021 (see https://doi.org/10.1080/1612197X.2021.1991102).
+The current journal editor where Article 4 was published included us in an email to the authors.
+We were also included in the authors' reply, wherein they again insisted that their analyses and conclusions remained valid.
+They offered an updated manuscript to the journal, but we are unaware of any decisions or further actions.
+
+The second important development was that the tables in Article 1 were updated on October 8th, 2021.
+The new tables made changes to the standard deviation values for both the reaction time and accuracy measures.
+The standard deviations of the reaction time data were adjusted such that the decimal point was shifted one place to the right compared to the original version.
+For example, an original standard deviation of 10.25 is now 102.51.
+The adjustments to the accuracy data now show the original standard deviation values as standard errors and new standard deviations are reported.
+Although the adjustments to the tables reflect corrections to plausible mishaps in the publication process and correcting such errors should be applauded, the new data themselves are problematic when compared to the reported analyses.
+
+To illustrate the disconnect between the new values and the test statistics in Article 1, we used the `faux` package in `R` to simulate data from multivariate normal distributions with the same mean and standard deviation parameters as the original and updated tables.
+We then analyzed the data using the same 4 x 4 mixed ANOVA model reported by the authors and compared the test statistics we observed to those reported in Article 1.
+We tried various correlations between time points and chose the value that produced the closest agreement between our analyses and theirs $(r = .8)$.
+
+Our analysis of simulated reaction time data using the originally reported standard deviations produced $F$-statistics that were more similar to the values reported in Article 1 than our analysis based on the updated numbers.
+Using the originally reported figures, we observed an $F$ = 18193 for the main effect of time.
+The authors reported $F$ = 16055 for this analysis.
+Our analysis using the updated statistics resulted in $F$ = 186.
+Similarly, the Time x Group interaction was $F$ = 4242 in Article 1, $F$ = 6208 in our simulation of the original parameters, and $F$ = 54 using the updated numbers.
+The main effect of Group was $F$ = 7156 in Article 1, $F$ = 3030 in our simulation of the original parameters, and $F$ = 23 using the updated numbers.
+As is evident, although the updated standard deviations lead to more plausible effect size calculations than the originally reported values, they are not consistent with the analyses reported in the paper.
+
+We observed similarly discordant $F$-statistics with analyses of simulated accuracy data based on the updated statistics.
+Article 1 reported a main effect of Time of $F$ = 3278, we observed $F$ = 2412 when analyzing our simulation of the original parameters, and $F$ = 132 when using the updated parameters.
+The authors reported a Group x Time interaction of $F$ = 657, we found $F$ = 494 with simulations of the original statistics, and $F$ = 27 when using the updated values.
+Finally, the main effect of Group was reported as $F$ = 922, we found $F$ = 254 with simulations of the original statistics, and $F$ = 21 when analyzing simulations of the updated data.
+
 # Discussion
 
-We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning [@lola2012; @lola2020; @lola2021;@lola2021b; @tzetzis2010; @tzetzis2015].
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning [@lola2021b; @lola2021; @lola2020; @tzetzis2015; @lola2012; @tzetzis2010].
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated $\eta^{2}$ values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations [@lola2021; @lola2021b].
+We discovered that the data reported in Articles 1 and 2 are very highly correlated despite ostensibly coming from different experiments, samples, and situations [@lola2021b; @lola2021].
+Finally, we observed that recently updated tables of summary statistics in Article 1 were incompatible with the analyses reported in the paper, while the original summary statistics, which indicated implausible effect sizes, were more compatible with the analyses.
 Considering these findings, the conclusions from these articles are not reliable.
+
+The data published in Article 1 are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, the article was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we had shared our concerns about the previous five articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors published an additional article with results that were not only implausible, but highly correlated with the results reported in a previous article.
+Subsequently, the authors published corrected tables with new standard deviation values.
+The means remained highly correlated with those reported in Article 2, but the new standard deviations were substantially larger than the original values.
+The updated summary statistics are not consistent with the test statistics reported in Article 1.
+Without commenting further on the possible causes of this sequence of events, we note only that they do not inspire confidence in the validity of the results reported in the target articles.
 
@@
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do[^7], many in the research community may find it difficult to trust any of these results.
+Even if the authors offer additional corrections, which they have suggested they intend to do[^7], many in the research community may find it difficult to trust any of these results.
 
-[^7]: As of today's date (`r Sys.Date()`), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
+[^7]:There is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
+However, as mentioned, the tables in Article 1 were updated and the authors offered some corrections in response to the editors of Article 5.
+We do not know if additional corrections have been submitted.
 
-## Comments on Article 2
-
-The data published in Article 2 are especially concerning.
-The article information indicates that it was submitted on June 17, 2021.
-Our email correspondence with the authors ended on April 22, 2021.
-Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as *d* = 41.0 *after* we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
-Despite this correspondence, the authors have published an additional article with results that are not only implausible, but highly correlated with the results reported in a previous article.
-We cannot think of a benign explanation for this sequence of events.
+\newpage
 

### 2022-01-27 docs/manuscript/manuscript.tex

--- 2021-09-29 docs/manuscript/manuscript.tex
@@
 
+\note{
+
+\vspace{10ex}
+
+In Press at \emph{Meta-Psychology}
+
+}
+
 \abstract{
@@
 We found the pairwise effect sizes were implausible in all six articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000.
+In contrast, the largest effect size observed in a million simulated experiments with a true effect of \(d\) = 3 was \(d\) = 6.6.
 Impossible statistics were reported in four out of the six articles.
@@
 We first became aware of the Lola and Tzetzis (2021) paper when the paper was highlighted in a social media post (Gray, 2021).
-During an initial read through by one of us (BM), a number of reporting and/or statistical issues were noticed.
+During an initial read through by one of us (BM), a number of reporting and statistical issues were noticed.
 The paper also referenced past research published by these authors.
-Given our cause for concern over the issues found in the Lola and Tzetzis (2021) paper, we deemed it necessary to examine these other papers.
+Given our concerns over the issues found in the Lola and Tzetzis (2021) paper, we deemed it necessary to examine these other papers.
 We remain agnostic to the sources of error in each of these papers.
 Nevertheless, the data irregularities we found are similar across the target articles and at times even include repeated values (e.g., \(F\)-statistics) across multiple papers.
-Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions\footnote{We contacted the Editors of the journals that published Articles 1, 3, 4, and 5 on Sept 22 2021.
-The Editors have either indicated their intention to further investigate these issues and/or take corrective actions.}.
+Regardless of the conclusion one reaches with respect to the mechanism behind these errors, it is our contention that the results reported in these papers are unreliable and that the respective journals in which the papers are published should take corrective actions\footnote{We contacted the journal editors for Articles 2-6 on Sept 22 2021 and for Article 1 on Jan 21 2022.
+All editors indicated their intention to further investigate these issues and/or take corrective actions.}.
 Below, we outline our causes for concern and the overarching issues we found across the six articles in question.
@@
 
-We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola et al., In Press; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
-All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
-In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills.
+We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleagues.
+In all experiments, the authors investigated the effects of implicit and explicit instructions on perceptual and motor learning.
+All experiments sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}).
 Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics.
-We will refer to the six articles throughout this paper using the following numbering system:
+We will refer to the six articles throughout this paper using the following numbering system based on reverse chronological order:
 
@@
 The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions.
-\emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This article is in a journal of a publishing group that has been identified as a potential predatory journal.
-Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS}).
-In fact, the earliest available issue on the journal's webpage is from 2016.}
+\emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This journal has been identified as a potential predatory journal.
+We were unable to find an online version of this article on the journal's webpage and interestingly, the earliest issue on the webpage is from 2016.
+We were only able to find an online version on ResearchGate (\url{https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf\#page=57}).}
 \end{enumerate}
 
-\vspace{6ex}
+\vspace{5ex}
 
@@
 \multicolumn{2}{l}{\textbf{Article 1}}\\
-\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
+\hspace{1em}Lola et al. (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
 \addlinespace[0.3em]
 \multicolumn{2}{l}{\textbf{Article 2}}\\
-\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
+\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
 \addlinespace[0.3em]
@@
 \multicolumn{2}{l}{\textbf{Article 5}}\\
-\hspace{1em}Lola et al (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
+\hspace{1em}Lola et al. (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
 \addlinespace[0.3em]
@@
 \item \textit{Note.} 
-\item[a] Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2.
+\item[a] Articles 2-4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 3 from Articles 2 and 4, and a different age range in Article 4 from Articles 2 and 3.
 \end{tablenotes}
@@
 This advantage was also predicted to be greater when testing was conducted in a high stress situation.
-In Lola and Tzetzis (2021) for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team.
+In Article 2 for instance, high stress was induced by falsely telling participants that the best performers would be selected for a draft to the national team.
 Further, it was predicted that analogy or sequential instruction would offer improvements relative to implicit instruction.
 
-The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
-In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale.
-Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.
+The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 6), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3).
+In addition, Articles 2 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale.
+The number of explicit rules recalled was assessed in Articles 2, 4, 5, and 6.
 
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola et al.
-(In Press) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Article 1 (Lola et al., 2021) because we were not aware of it at the time as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
-The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns.
-Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles.
-The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles.
+The authors did address some specific concerns regarding Article 2, but for the most part only provided more general responses to our concerns.
+The authors admitted that some of the values reported in the other target articles were incorrect, but did not identify which values or articles.
 Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A.
@@
 
-Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity.
+Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity in both the negative and positive direction.
+We calculated absolute values so that all effects were positive.
 Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion).
@@
 Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).
+In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of \emph{d} = .19 (McKay et al., 2021), \emph{d} = .54 (McKay, Yantha, Hussien, Carter, \& Ste-Marie, in press), and \emph{d} = .71 (Lohse, Buchanan, \& Miller, 2016).
 
-To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
+To evaluate the maximum plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}).
 We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation.
@@
 
-\caption{Absolute Cohen's \(d\) estimates from Articles 1-5 plotted on a logarithmic scale.
+\caption{Absolute Cohen's \(d\) estimates from all articles except Article 6 plotted on a logarithmic scale.
+Only data from the original tables in Article 1 are included.
 All pairwise comparisons have been included for all dependent measures in each experiment.
@@
 In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes.
-In Article 1, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
+The original table of summary statistics in Article 1 indicated that the smallest post-intervention difference in reaction times was \emph{d} = .64.
+However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41.
+The accuracy data also reflected improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35.
+However, a correction to the tables of summary statistics was published that included substantially smaller standard deviations than the original tables.
+While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the reported analyses.
+
+In Article 2, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article.
 The smallest post-intervention effect at any of the three time points was \emph{d} = 286.42, while the largest effect was \emph{d} = 3504.86.
@@
 
-Articles 1, 5, and 6 reported the means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
+In Articles 2, 5, and 6, the authors reported means and standard deviations for the number of explicit rules recalled by participants following the intervention phase.
 As a single item analysis of integers these results were suitable for a GRIMMER analysis.
-In Article 1, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups.
-In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78).
-The mean and standard deviation pairs for the remaining three groups were GRIMMER inconsistent.
-In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample.
-For two of the groups, however, they were consistent regardless of which method of calculating the standard deviation was used.
-However, the results for the explicit group were GRIMMER inconsistent (\emph{M} = 4.8, \emph{SD} = 1.78).\footnote{You may have noticed that the same mean and standard deviation pairing (\emph{M} = 4.8, \emph{SD} = 1.78) was classified as GRIMMER inconsistent for one paper and consistent for the other.
-This is because of sample size differences (\emph{n} = 20 for the consistent result and \emph{n} = 12 for the inconsistent one).}
+In Article 2, the mean and standard deviation pairs were GRIMMER inconsistent for all four groups (Implicit: \emph{M} = .73, \emph{SD} = .35; Analogy: \emph{M} = 1.03, \emph{SD} = .25; Explicit: \emph{M} = 4.8, \emph{SD} = .78; Control: \emph{M} = .67, \emph{SD} = .48; \emph{n} = 15).
+In Article 5, the mean and standard deviation pair was GRIMMER consistent for the explicit rules group (\emph{M} = 4.8, \emph{SD} = 1.78) and the implicit group (\emph{M} = 2.3, \emph{SD} = 1.3).
+The mean and standard deviation pairs for the remaining two groups were GRIMMER inconsistent (Sequential: \emph{M} = 4.2, \emph{SD} = 1.07; Control: \emph{M} = 1.8, \emph{SD} = .3; \emph{n} = 15).
+In Article 6, the mean and standard deviation pairs were GRIMMER consistent for three of the four groups if the standard deviations were calculated for the population rather than the sample (Sequential: \emph{M} = 4.2, \emph{SD} = 1.07; Implicit: \emph{M} = 2.3, \emph{SD} = 1.3; Control: \emph{M} = 1.4, \emph{SD} = .9; \emph{n} = 12).
+For two of the groups, they were consistent regardless of which method of calculating the standard deviation was used.
+However, the results for the explicit group were GRIMMER inconsistent (\emph{M} = 4.8, \emph{SD} = 1.78).\footnote{You may have noticed that two of the same mean and standard deviation pairings (\emph{M} = 4.8, \emph{SD} = 1.78 and \emph{M} = 4.2, \emph{SD} = 1.07) were classified as GRIMMER inconsistent for one paper and consistent for the other.
+This is because of sample size differences (\emph{n} = 15 and \emph{n} = 12).}
 
@@
 With respect to response accuracy, the reported effects were \(\eta^{2}\) = .98, \(\eta^{2}\) = .94, \(\eta^{2}\) = .93 for the Time, Group, and Time x Group analyses, respectively.
-Article 5 reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses, respectively.
+Article 6 reported \(\eta^{2}\) = .66, \(\eta^{2}\) = .52, \(\eta^{2}\) = .72 for the Time, Group, and Time x Group analyses, respectively.
 
@@
 
-Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 1, 4, 5, and 6.
-The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in Articles 1, 3, and 4).
-Articles 1, 3, and 4 were published over a span of 6 years with reported samples sizes of 60 in Articles 1 and 4, and 80 in Article 3.
+Although the means and standard deviations for the explicit rules analysis were only reported in three of the articles in question, analyses were reported in Articles 2, 4, 5, and 6.
+The reported test statistic in these four articles was \emph{F} = 52.67, albeit with different degrees of freedom in Article 6 that reflected the different sample size in this experiment (48 versus 60 in the others).
+Articles 2-4 were published over a span of 6 years with reported samples sizes of 60 in Articles 2 and 4, and 80 in Article 3.
 Yet, the authors report identical means and standard deviations for the age of their participants in these three articles (see Table \ref{tab:table1}).
@@
 
-Article 2 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted the first version of this preprint (version 1 posted Sept 14 2021).
-We were unaware of Article 2 when posting the original preprint and it was not included in that version.
-However, when we became aware of Article 2 it was immediately apparent that data reported therein again reflected improbably large effect sizes.
-Further, in comparing the reaction time and accuracy means reported in Lola et al.
-(In Press) to those reported in Lola and Tzetzis (2021), it appeared the data shared a remarkably similar pattern.
+Article 1 was submitted to the \emph{Journal of Human Sport and Exercise} following our correspondence with the authors and published online (Sept 3 2021) 11 days before we posted our preprint (Version 1).
+We were unaware of this article when posting the original preprint and it was not included in that version.
+However, when we became aware of this paper it was immediately apparent that data reported therein again reflected improbably large effect sizes.
+Further, in comparing the reaction time and accuracy means reported in Article 1 to those reported in Article 2, it appeared the data shared a remarkably similar pattern.
 To investigate this similarity further, we conducted a correlation analysis between the two data sets.
 The reaction time means for each group and time point were highly correlated between the two papers, \emph{r} = .99, as were the accuracy means, \emph{r} = .99.
+
+\hypertarget{new-developments-following-september-28-2021-update}{%
+\subsection{New Developments Following September 28, 2021 Update}\label{new-developments-following-september-28-2021-update}}
+
+After contacting the editors for Articles 2-5 on September 22 2021 and updating our preprint on September 28th, at least two important developments transpired.
+First, there was a response from all four editors indicating an intention to investigate the issues we raised.
+The \emph{International Journal of Sport and Exercise Psychology} is so far the only journal that has taken observable action, issuing an Expression of Concern regarding Article 2 on October 11th, 2021 (see \url{https://doi.org/10.1080/1612197X.2021.1991102}).
+The current journal editor where Article 4 was published included us in an email to the authors.
+We were also included in the authors' reply, wherein they again insisted that their analyses and conclusions remained valid.
+They offered an updated manuscript to the journal, but we are unaware of any decisions or further actions.
+
+The second important development was that the tables in Article 1 were updated on October 8th, 2021.
+The new tables made changes to the standard deviation values for both the reaction time and accuracy measures.
+The standard deviations of the reaction time data were adjusted such that the decimal point was shifted one place to the right compared to the original version.
+For example, an original standard deviation of 10.25 is now 102.51.
+The adjustments to the accuracy data now show the original standard deviation values as standard errors and new standard deviations are reported.
+Although the adjustments to the tables reflect corrections to plausible mishaps in the publication process and correcting such errors should be applauded, the new data themselves are problematic when compared to the reported analyses.
+
+To illustrate the disconnect between the new values and the test statistics in Article 1, we used the \texttt{faux} package in \texttt{R} to simulate data from multivariate normal distributions with the same mean and standard deviation parameters as the original and updated tables.
+We then analyzed the data using the same 4 x 4 mixed ANOVA model reported by the authors and compared the test statistics we observed to those reported in Article 1.
+We tried various correlations between time points and chose the value that produced the closest agreement between our analyses and theirs \((r = .8)\).
+
+Our analysis of simulated reaction time data using the originally reported standard deviations produced \(F\)-statistics that were more similar to the values reported in Article 1 than our analysis based on the updated numbers.
+Using the originally reported figures, we observed an \(F\) = 18193 for the main effect of time.
+The authors reported \(F\) = 16055 for this analysis.
+Our analysis using the updated statistics resulted in \(F\) = 186.
+Similarly, the Time x Group interaction was \(F\) = 4242 in Article 1, \(F\) = 6208 in our simulation of the original parameters, and \(F\) = 54 using the updated numbers.
+The main effect of Group was \(F\) = 7156 in Article 1, \(F\) = 3030 in our simulation of the original parameters, and \(F\) = 23 using the updated numbers.
+As is evident, although the updated standard deviations lead to more plausible effect size calculations than the originally reported values, they are not consistent with the analyses reported in the paper.
+
+We observed similarly discordant \(F\)-statistics with analyses of simulated accuracy data based on the updated statistics.
+Article 1 reported a main effect of Time of \(F\) = 3278, we observed \(F\) = 2412 when analyzing our simulation of the original parameters, and \(F\) = 132 when using the updated parameters.
+The authors reported a Group x Time interaction of \(F\) = 657, we found \(F\) = 494 with simulations of the original statistics, and \(F\) = 27 when using the updated values.
+Finally, the main effect of Group was reported as \(F\) = 922, we found \(F\) = 254 with simulations of the original statistics, and \(F\) = 21 when analyzing simulations of the updated data.
 
@@
 Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-Finally, we discovered that the data reported in two articles are highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., In Press; Lola \& Tzetzis, 2021).
+We discovered that the data reported in Articles 1 and 2 are very highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., 2021; Lola \& Tzetzis, 2021).
+Finally, we observed that recently updated tables of summary statistics in Article 1 were incompatible with the analyses reported in the paper, while the original summary statistics, which indicated implausible effect sizes, were more compatible with the analyses.
 Considering these findings, the conclusions from these articles are not reliable.
+
+The data published in Article 1 are especially concerning.
+The article information indicates that it was submitted on June 17, 2021.
+Our email correspondence with the authors ended on April 22, 2021.
+Therefore, the article was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we had shared our concerns about the previous five articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
+Despite this correspondence, the authors published an additional article with results that were not only implausible, but highly correlated with the results reported in a previous article.
+Subsequently, the authors published corrected tables with new standard deviation values.
+The means remained highly correlated with those reported in Article 2, but the new standard deviations were substantially larger than the original values.
+The updated summary statistics are not consistent with the test statistics reported in Article 1.
+Without commenting further on the possible causes of this sequence of events, we note only that they do not inspire confidence in the validity of the results reported in the target articles.
 
@@
 At a minimum, the consistent reporting errors across these six articles seem to reflect excessive carelessness throughout the publication process.
-Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-28), there is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.}, many in the research community may find it difficult to trust any of these results.
+Even if the authors offer additional corrections, which they have suggested they intend to do\footnote{There is no indication that such corrective actions were taken by the authors prior to us contacting the Editors on Sept 22 2021.
+However, as mentioned, the tables in Article 1 were updated and the authors offered some corrections in response to the editors of Article 5.
+We do not know if additional corrections have been submitted.}, many in the research community may find it difficult to trust any of these results.
 
-\hypertarget{comments-on-article-2}{%
-\subsection{Comments on Article 2}\label{comments-on-article-2}}
-
-The data published in Article 2 are especially concerning.
-The article information indicates that it was submitted on June 17, 2021.
-Our email correspondence with the authors ended on April 22, 2021.
-Therefore, Article 2 was submitted with data that reflect implausible effect sizes as large as \emph{d} = 41.0 \emph{after} we shared our concerns about the previous 5 articles, and after the authors had suggested at least some of the implausible effect sizes were due to misprints.
-Despite this correspondence, the authors have published an additional article with results that are not only implausible, but highly correlated with the results reported in a previous article.
-We cannot think of a benign explanation for this sequence of events.
+\newpage
 

### 2022-02-04 docs/manuscript/manuscript.Rmd
update: fix wording

@@
 Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion].
-Conventional benchmarks for small, medium, and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions].
+Conventional benchmarks for small, medium, and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *mindless* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions].
 Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021].

### 2022-02-04 docs/manuscript/manuscript.tex
update: fix wording

@@
 \documentclass[
-  english,
   man, donotrepeattitle,floatsintext]{apa7}
-\title{Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
-\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
-\date{}
-
 \usepackage{amsmath,amssymb}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 \pagewiselinenumbers
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 \fi
+
+\title{Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
+\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
+\date{}
 
@@
 
-\abstract{
+\abstract{%
 We present a critical re-analysis of six implicit learning papers published by the same authors between 2010 and 2021.
@@
 Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion).
-Conventional benchmarks for small, medium, and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions).
+Conventional benchmarks for small, medium, and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{mindless} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions).
 Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).

### 2022-06-02 docs/manuscript/manuscript.Rmd
update - title change

@@
 ---
-title             : "Data irregularities across six implicit learning articles: Comments on @lola2021b, @lola2021, @lola2020, @tzetzis2015, @lola2012, and @tzetzis2010"
+title             : "A critical re-analysis of six implicit learning papers"
 
-shorttitle        : "Commentary on Lola & Tzetzis papers"
+shorttitle        : "Commentary on implicit learning papers"
 

### 2022-06-02 docs/manuscript/manuscript.tex
update - title change

--- 2022-01-27 docs/manuscript/manuscript.tex
@@
   man, donotrepeattitle,floatsintext]{apa7}
-\title{Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
-\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
-\date{}
-
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \hypersetup{
-  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
+  pdftitle={A critical re-analysis of six implicit learning papers},
   pdfauthor={Brad McKay1 \& Michael J. Carter1},
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{Commentary on implicit learning papers}
 \keywords{Metascience; GRIMMER; Effect sizes; Perceptual motor learning}
@@
 \fi
-\ifLuaTeX
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\shorttitle{Commentary on Lola \& Tzetzis papers}
+\title{A critical re-analysis of six implicit learning papers}
+\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
+\date{}
+
+\note{
+
+\vspace{10ex}
+
+In Press at \emph{Meta-Psychology}
+
+}
 
@@
 \affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Kinesiology, McMaster University}
-
-\note{
-
-\vspace{10ex}
-
-In Press at \emph{Meta-Psychology}
-
-}
 
@@
 Our first two requests did not include any indication about our concerns regarding the data irregularities.
-Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Article 1 (Lola et al., 2021) because we were not aware of it at the time as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
+Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Article 1 (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021) because we were not aware of it at the time as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles.
 These requests were once again refused.
@@
 
-We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola et al., 2021; Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015).
+We have reviewed concerning data irregularities spanning six articles investigating implicit motor and perceptual learning (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015).
 These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A.
@@
 Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables.
-We discovered that the data reported in Articles 1 and 2 are very highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola et al., 2021; Lola \& Tzetzis, 2021).
+We discovered that the data reported in Articles 1 and 2 are very highly correlated despite ostensibly coming from different experiments, samples, and situations (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2021).
 Finally, we observed that recently updated tables of summary statistics in Article 1 were incompatible with the analyses reported in the paper, while the original summary statistics, which indicated implausible effect sizes, were more compatible with the analyses.
@@
 
-R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{faux} (Version 1.1.0; DeBruine, 2021), \emph{gridGraphics} (Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Edwards, 2020), \emph{lsr} (Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.2; Neuwirth, 2014), \emph{scales} (Version 1.1.1; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019).
+R (Version 4.0.4; R Core Team, 2021) and the R-packages \emph{compute.es} (Version 0.2.5; Re, 2013), \emph{daff} (Version 0.3.5; Fitzpatrick, de Jonge, \& Warnes, 2019), \emph{faux} (Version 1.1.0; DeBruine, 2021), \emph{gridGraphics} (Version 0.5.1; Murrell \& Wen, 2020), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{lemon} (Version 0.4.5; Edwards, 2020), \emph{lsr} (Version 0.5; Navarro, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{RColorBrewer} (Version 1.1.3; Neuwirth, 2014), \emph{scales} (Version 1.2.0; Wickham \& Seidel, 2020), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-faux}{}}%
+\leavevmode\hypertarget{ref-R-faux}{}%
 DeBruine, L. (2021). \emph{Faux: Simulation for factorial designs}. Zenodo. \url{https://doi.org/10.5281/zenodo.2669586}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lemon}{}}%
+\leavevmode\hypertarget{ref-R-lemon}{}%
 Edwards, S. M. (2020). \emph{Lemon: Freshing up your 'ggplot2' plots}. Retrieved from \url{https://CRAN.R-project.org/package=lemon}
 
-\leavevmode\vadjust pre{\hypertarget{ref-field2016}{}}%
+\leavevmode\hypertarget{ref-field2016}{}%
 Field, A. P. (2016). \emph{An adventure in statistics: The reality enigma}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-fischman2015}{}}%
+\leavevmode\hypertarget{ref-fischman2015}{}%
 Fischman, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lohse2016}{}}%
+\leavevmode\hypertarget{ref-lohse2016}{}%
 Lohse, K., Buchanan, T., \& Miller, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mckay2021b}{}}%
+\leavevmode\hypertarget{ref-mckay2021b}{}%
 McKay, B., Hussien, J., Vinh, M.-A., Mir-Orefice, A., Brooks, H., \& Ste-Marie, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mckay2021a}{}}%
+\leavevmode\hypertarget{ref-mckay2021a}{}%
 McKay, B., Yantha, Z.
